### 2018-04-19 resistingrhythm/analysis/ca_analysis.Rmd
Added Ca analysis Rmd

---
title: "Ca exp analysis -- 4/18/2018"
output: html_notebook
---

```{r}
library(tidyverse)
library(gridExtra)

data_path <- "~/Code/resistingrhythm/data/"
```

```{r, message=FALSE}
exp_code <- 1
osc_codes <- c(1, 3, 5)
osc_rates <- c(1, 3, 5)
stim_codes <- c(0)

# Load exp 1 results for comparison
results <- NULL
for(i in 1:length(osc_codes)){
  for(s_c in stim_codes){
    o_c <- osc_codes[i]
    o_r <- osc_rates[i]

    # Load the csv
    df <- read_csv(paste(data_path, 
                         "exp", as.character(exp_code), 
                         "_stim", as.character(s_c), 
                         "_osc", as.character(o_c),
                         ".csv", sep=""))

    # Add metadata
    df$osc_code <- rep(o_c, nrow(df))
    df$osc_rate <- rep(o_r, nrow(df))
    df$stim_code <- rep(ca, nrow(df))
    df$ca_targets <- rep("0.030", nrow(df))

    results <- rbind(results, df)
  }
}

# the load exp2, for Ca 
exp_code <- 2
ca_values <- c("0.032", "0.034", "0.036", "0.038")
for(i in 1:length(osc_codes)){
  for(s_c in stim_codes){
    for(ca in ca_values){
      o_c <- osc_codes[i]
      o_r <- osc_rates[i]

      # Load the csv
      df <- read_csv(paste(data_path, 
                           "exp", as.character(exp_code), 
                           "_stim", as.character(s_c), 
                           "_osc", as.character(o_c),
                           "_Ca", ca,
                           ".csv", sep=""))

      # Add metadata
      df$osc_code <- rep(o_c, nrow(df))
      df$osc_rate <- rep(o_r, nrow(df))
      df$stim_code <- rep(s_c, nrow(df))
      df$ca_targets <- rep(ca, nrow(df))

      results <- rbind(results, df)
    }
  }
}
```

# Osc rate 
## By variance

```{r, fig.width=2.0, fig.height=1}
results %>% 
  ggplot(aes(x=osc_rate, y=kappa_coord, 
             group=interaction(osc_rate,ca_targets),
             color=ca_targets)) +
  geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
  labs(y="Kappa", x="Osc. rate (Hz)") +
  theme_classic() 
```

```{r, fig.width=2.0, fig.height=1}
results %>% 
  ggplot(aes(x=osc_rate, y=mse_var, 
             group=interaction(osc_rate, ca_targets),
             color=ca_targets)) +
  geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
  labs(y="Variance", x="Osc. rate (Hz)") +
  theme_classic() 
```

## By error

```{r, fig.width=2.0, fig.height=1.0}
results %>% 
  ggplot(aes(x=osc_rate, y=mse_error, 
             group=interaction(osc_rate,ca_targets),
             color=ca_targets)) +
  geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
  labs(y="Error", x="Osc. rate (Hz)") +
  theme_classic() 
```

## By rate

```{r, fig.width=2.0, fig.height=1.0}
results %>% 
  ggplot(aes(x=osc_rate, y=rate_k, 
             group=interaction(osc_rate,ca_targets),
             color=ca_targets)) +
  geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
  labs(y="Mod. rate (Hz)", x="Osc. rate (Hz)") +
  theme_classic() 
```

```{r, fig.width=2.0, fig.height=1.0}
results %>% 
  ggplot(aes(x=osc_rate, y=rate_ref - rate_k, 
             group=interaction(osc_rate,ca_targets),
             color=ca_targets)) +
  geom_jitter(alpha=0.1, size=0.1) +
  geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
  geom_hline(yintercept=0, size=0.5) +
  labs(y="Rate diff. (Hz)", x="Osc. rate (Hz)") +
  theme_classic() 
```

# Error versus var

```{r, fig.width=2.2, fig.height=0.8}
results %>% 
  ggplot(aes(x=mse_error, y=kappa_coord, color=ca_targets)) +
  geom_point(alpha=0.5, size=0.2) + 
  theme_classic() + 
  labs(y="Kappa", x="Error") +
  facet_grid(.~osc_rate)
```

```{r, fig.width=1.8, fig.height=0.8}
results %>% 
  ggplot(aes(x=mse_error, y=mse_var, color=ca_targets)) +
  geom_point(alpha=0.5, size=0.2) + 
  theme_classic() + 
  labs(y="Variance", x="Error") +
  facet_grid(.~osc_rate)
```

### 2018-04-19 resistingrhythm/exp/homeostasis_experiments.py
Added exp4,5,6; updated exp2 to match new Ca API....
Added --CA_ref to h_exp, so the Ca for the ref and target are independent.

@@ -22,12 +22,14 @@ def run(run_name,
         burn_t=10,
         N=10,
         Ca_target=0.03,
+        Ca_ref=0.03,
         tau_h=1,
         w_min=5e-6,
         w_max=50e-6,
         sigma=0,
         num_trials=2,
         seed_value=42,
+        no_homeostasis=True,
         verbose=False):
     """Run a HHH experiment"""
 
@@ -48,8 +50,10 @@ def run(run_name,
     w_min = float(w_min)
     w_max = float(w_max)
     tau_h = float(tau_h)
-    Ca_target = float(Ca_target)
     burn_t = float(burn_t)
+
+    Ca_target = float(Ca_target)
+    Ca_ref = float(Ca_ref)
 
     if w_min > w_max:
         raise ValueError("w_min must be smaller than w_max")
@@ -95,7 +99,7 @@ def run(run_name,
             np.asarray([]),  # no osc mod
             np.asarray([]),
             N=N,
-            Ca_target=Ca_target,
+            Ca_target=Ca_ref,
             bias_in=bias_in,
             sigma=sigma,
             w_in=w,
@@ -105,7 +109,7 @@ def run(run_name,
             burn_time=burn_t,
             seed_value=seed_value + k,
             record_traces=True,
-            homeostasis=True)
+            homeostasis=no_homeostasis)
 
         ns_ref, ts_ref = filter_spikes(results_ref["ns"], results_ref["ts"],
                                        a_window)
@@ -129,7 +133,7 @@ def run(run_name,
                         burn_time=burn_t,
                         seed_value=seed_value + k,
                         record_traces=True,
-                        homeostasis=True)
+                        homeostasis=no_homeostasis)
 
         # -
         if verbose:
@@ -154,16 +158,17 @@ def run(run_name,
 
         # Get final avg. calcium
         # over a window? Just grab last?
-        Ca_k = results_k['calcium'][:, -50].mean()
-        Ca_ref = results_ref['calcium'][:, -50].mean()
+        Ca_obs_k = results_k['calcium'][:, -50].mean()
+        Ca_obs_ref = results_ref['calcium'][:, -50].mean()
 
         # Get final avg V_m
         V_k = results_k['v_m'][:, -50].mean()
         V_ref = results_ref['v_m'][:, -50].mean()
 
         # save row
[…]

### 2018-04-19 resistingrhythm/exp/homeostasis_experiments.py
Tweaks to results col names in h_exp

@@ -176,9 +176,9 @@ def run(run_name,
         print(">>> Saving results")
 
     head = [
-        "k", "V_ref", "V_k", "Ca_target", "Ca_ref", "Ca_obs_k", "Ca_obs_ref",
-        "kappa_error", "kappa_coord", "abs_error", "abs_var", "mse_error",
-        "mse_var", "rate_k", "rate_ref"
+        "k", "V_ref", "V_k", "Ca_target", "Ca_ref", "Ca_obs_target",
+        "Ca_obs_ref", "kappa_error", "kappa_coord", "abs_error", "abs_var",
+        "mse_error", "mse_var", "rate_k", "rate_ref"
     ]
     with open("{}.csv".format(run_name), "w") as fi:
         writer = csv.writer(fi, delimiter=",")

### 2018-04-19 resistingrhythm/util.py
Removed unneeded deps

@@ -1,8 +1,6 @@
 from __future__ import division
 import csv
 import os
-import json
-import voltagebudget
 import numpy as np
 
 from scipy.signal import square

### 2018-04-20 resistingrhythm/exp/homeostasis_experiments.py
osc_name and stim_name are no optional, as intended.

@@ -78,11 +78,21 @@ def run(run_name,
 
     # ---------------------------------------------------
     # load spikes
-    ns_stim, ts_stim = load_spikes(stim_name)
-    ns_osc, ts_osc = load_spikes(osc_name)
-    if verbose:
-        print(">>> Loaded {}".format(stim_name))
-        print(">>> Loaded {}".format(osc_name))
+    if stim_name is not None:
+        ns_stim, ts_stim = load_spikes(stim_name)
+        if verbose:
+            print(">>> Loaded {}".format(stim_name))
+    else:
+        ns_stim = np.asarray([])
+        ts_stim = np.asarray([])
+
+    if osc_name is not None:
+        ns_osc, ts_osc = load_spikes(osc_name)
+        if verbose:
+            print(">>> Loaded {}".format(osc_name))
+    else:
+        ns_osc = np.asarray([])
+        ts_osc = np.asarray([])
 
     # ---------------------------------------------------
     results = []

### 2018-04-20 resistingrhythm/analysis/ca_analysis_v2.Rmd
Added new Ca analysis Rmd, adj col names to match the new format

---
title: "Ca exp analysis -- 4/18/2018"
output: html_notebook
---

```{r}
library(tidyverse)
library(gridExtra)

data_path <- "~/Code/resistingrhythm/data/"
```

```{r, message=FALSE}
exp_code <- 1
osc_codes <- c(1, 3, 5)
osc_rates <- c(1, 3, 5)
stim_codes <- c(0)

# Load exp 1 results for comparison

results <- NULL
for(i in 1:length(osc_codes)){
  for(s_c in stim_codes){
    o_c <- osc_codes[i]
    o_r <- osc_rates[i]

    # Load the csv
    df <- read_csv(paste(data_path, 
                         "exp", as.character(exp_code), 
                         "_stim", as.character(s_c), 
                         "_osc", as.character(o_c),
                         ".csv", sep=""))

    # Add metadata
    df$osc_code <- rep(o_c, nrow(df))
    df$osc_rate <- rep(o_r, nrow(df))
    df$stim_code <- rep(s_c, nrow(df))
    df$Ca_target <- rep("0.030", nrow(df))

    results <- rbind(results, df)
  }
}

# Rename Ca to match new format
results %>% 
  rename(Ca_obs_target = Ca_k) %>% 
  mutate(Ca_obs_ref = Ca_obs_target) -> results

# ------------------------------------------------------------------
# exp_code <- 2
# ca_values <- c("0.032", "0.034", "0.036", "0.038")

exp_code <- 7
ca_values <- c("0.032", "0.034", "0.036")
for(i in 1:length(osc_codes)){
  for(s_c in stim_codes){
    for(ca in ca_values){
      o_c <- osc_codes[i]
      o_r <- osc_rates[i]

      # Generate name
      file_name <- paste(data_path, 
                         "exp", as.character(exp_code), 
                         "_stim", as.character(s_c), 
                         "_osc", as.character(o_c),
                         "_Ca", ca,
                         ".csv", sep="")

      if (file.exists(file_name)){
        # Load
        df <- read_csv(file_name)

        # Add metadata
        df$osc_code <- rep(o_c, nrow(df))
        df$osc_rate <- rep(o_r, nrow(df))
        df$stim_code <- rep(s_c, nrow(df))

        results <- rbind(results, df)  
      }
    }
  }
}

rm(df, exp_code, ca_values, osc_codes, osc_rates, file_name, i, o_c, o_r, s_c, stim_codes, ca)
```

# Osc rate 
## By variance

```{r, fig.width=2.0, fig.height=1}
results %>% 
  ggplot(aes(x=osc_rate, y=kappa_coord, 
             group=interaction(osc_rate, Ca_target),
             color=factor(Ca_target))) +
  geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
  labs(y="Kappa", x="Osc. rate (Hz)") +
  theme_classic() 
```
```{r, fig.width=2.0, fig.height=1}
results %>% 
  ggplot(aes(x=osc_rate, y=mse_var, 
             group=interaction(osc_rate, Ca_target),
             color=factor(Ca_target))) +
  geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
  labs(y="Variance", x="Osc. rate (Hz)") +
  theme_classic() 
```

## By error

```{r, fig.width=2.0, fig.height=1}
results %>% 
  ggplot(aes(x=osc_rate, y=mse_error, 
             group=interaction(osc_rate, Ca_target),
             color=factor(Ca_target))) +
  geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
  labs(y="Error", x="Osc. rate (Hz)") +
  theme_classic() 
```

## By rate

```{r, fig.width=2.0, fig.height=1}
results %>% 
  ggplot(aes(x=osc_rate, y=rate_k, 
             group=interaction(osc_rate, Ca_target),
             color=factor(Ca_target))) +
  geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
  labs(y="Firing rate (Hz)", x="Rate (Hz") +
  theme_classic() 
```

```{r, fig.width=2.0, fig.height=1.0}
results %>% 
  ggplot(aes(x=osc_rate, y=rate_ref - rate_k, 
             group=interaction(osc_rate, Ca_target),
             color=factor(Ca_target))) +
  geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
  geom_hline(yintercept=0, size=0.5) +
  labs(y="Rate diff. (Hz)", x="Osc. rate (Hz)") +
  theme_classic() 
```

# Error versus var

```{r, fig.width=2.2, fig.height=0.8}
results %>% 
  ggplot(aes(x=mse_error, y=kappa_coord, color=Ca_target)) +
  geom_point(alpha=0.5, size=0.2) + 
  theme_classic() + 
  labs(y="Kappa", x="Error") +
  facet_grid(.~osc_rate)
```

```{r, fig.width=1.8, fig.height=0.8}
results %>% 
  ggplot(aes(x=mse_error, y=mse_var, color=Ca_target)) +
  geom_point(alpha=0.5, size=0.2) + 
  theme_classic() + 
  labs(y="Variance", x="Error") +
  facet_grid(.~osc_rate)
```

### 2018-04-20 resistingrhythm/analysis/burst_analysis.Rmd
Adding control_analysis and burst_analysis

---
title: "General burst analysis -- 4/18/2018"
output: html_notebook
---

```{r}
library(tidyverse)
library(gridExtra)

data_path <- "~/Code/resistingrhythm/data/"
```

```{r, message=FALSE}
exp_code <- 3
osc_codes <- c(0, 1, 3, 5)
osc_rates <- c(0.5, 1, 3, 5)
stim_codes <- c(0, 1, 2)

results <- NULL
for(i in 1:length(osc_codes)){
  for(s_c in stim_codes){
    o_c <- osc_codes[i]
    o_r <- osc_rates[i]

    # Load the csv
    df <- read_csv(paste(data_path, 
                         "exp", as.character(exp_code), 
                         "_stim", as.character(s_c), 
                         "_burst", as.character(o_c),
                         ".csv", sep=""))

    # Add metadata
    df$osc_code <- rep(o_c, nrow(df))
    df$osc_rate <- rep(o_r, nrow(df))
    df$stim_code <- rep(s_c, nrow(df))

    results <- rbind(results, df)
  }
}
```

# Osc rate 
## By variance

```{r, fig.width=1.0, fig.height=0.8}
results %>% 
  ggplot(aes(x=osc_rate, y=kappa_coord, group=osc_rate)) +
  geom_jitter(alpha=0.1, size=0.1) +
  geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
  labs(y="Kappa", x="Osc. rate (Hz)") +
  theme_classic() 
```

```{r, fig.width=1.0, fig.height=0.8}
results %>% 
  ggplot(aes(x=osc_rate, y=mse_var, group=osc_rate)) +
  geom_jitter(alpha=0.1, size=0.1) +
  geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
  labs(y="Variance", x="Osc. rate (Hz)") +
  theme_classic() 
```

## By error

```{r, fig.width=1.0, fig.height=0.8}
results %>% 
  ggplot(aes(x=osc_rate, y=mse_error, group=osc_rate)) +
  geom_jitter(alpha=0.1, size=0.1) +
  geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
  labs(y="Error", x="Osc. rate (Hz)") +
  theme_classic() 
```

## By rate

```{r, fig.width=1.0, fig.height=0.8}
results %>% 
  ggplot(aes(x=osc_rate, y=rate_k, group=osc_rate)) +
  geom_jitter(alpha=0.1, size=0.1) +
  geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
  labs(y="Mod. rate (Hz)", x="Osc. rate (Hz)") +
  theme_classic() 
```

```{r, fig.width=1.0, fig.height=0.8}
results %>% 
  ggplot(aes(x=osc_rate, y=rate_k - rate_ref, group=osc_rate)) +
  geom_jitter(alpha=0.1, size=0.1) +
  geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
  geom_hline(yintercept=0, size=0.5) +
  labs(y="Rate diff. (Hz)", x="Osc. rate (Hz)") +
  theme_classic() 
```

# Error versus var

```{r, fig.width=1.8, fig.height=0.8}
results %>% 
  ggplot(aes(x=mse_error, y=kappa_coord)) +
  geom_point(size=0.4, alpha=0.2) + 
  theme_classic() + 
  labs(y="Kappa", x="Error") +
  facet_grid(.~osc_rate)
```

```{r, fig.width=1.8, fig.height=0.8}
results %>% 
  ggplot(aes(x=mse_error, y=mse_var)) +
  geom_point(size=0.4, alpha=0.2) + 
  theme_classic() + 
  labs(y="Variance", x="Error") +
  facet_grid(.~osc_rate)
```

### 2018-04-20 resistingrhythm/exp/homeostasis_experiments.py
Clarfied use/docs of the homeostatsis flag in h_exp

@@ -29,7 +29,7 @@ def run(run_name,
         sigma=0,
         num_trials=2,
         seed_value=42,
-        no_homeostasis=True,
+        homeostasis=True,
         verbose=False):
     """Run a HHH experiment"""
 
@@ -38,10 +38,15 @@ def run(run_name,
     bias_in = 0
     time_step = 1e-5
 
+    if homeostasis:
+        print(">>> Homeostasis is on")
+    else:
+        print(">>> Homeostasis is off")
+
     # ---------------------------------------------------
     if verbose:
         print(">>> Running {}".format(run_name))
-        print(">>> Checking args.")
+        print(">>> Checking args")
 
     N = int(N)
     num_trials = int(num_trials)
@@ -119,7 +124,7 @@ def run(run_name,
             burn_time=burn_t,
             seed_value=seed_value + k,
             record_traces=True,
-            homeostasis=no_homeostasis)
+            homeostasis=homeostasis)
 
         ns_ref, ts_ref = filter_spikes(results_ref["ns"], results_ref["ts"],
                                        a_window)
@@ -143,7 +148,7 @@ def run(run_name,
                         burn_time=burn_t,
                         seed_value=seed_value + k,
                         record_traces=True,
-                        homeostasis=no_homeostasis)
+                        homeostasis=homeostasis)
 
         # -
         if verbose:

### 2018-04-23 resistingrhythm/exp/homeostasis_experiments.py
Exposed bias_in in h_exp

@@ -26,6 +26,7 @@ def run(run_name,
         tau_h=1,
         w_min=5e-6,
         w_max=50e-6,
+        bias_in=0,
         sigma=0,
         num_trials=2,
         seed_value=42,
@@ -35,7 +36,6 @@ def run(run_name,
 
     # ---------------------------------------------------
     # Fixed params
-    bias_in = 0
     time_step = 1e-5
 
     if homeostasis:

### 2018-04-28 resistingrhythm/analysis/paper_figures.Rmd
Draft one of paper figures

---
title: "General exp analysis -- 4/18/2018"
output: html_notebook
---

```{r, message=FALSE}
library(tidyverse)
library(gridExtra)
library(grid)
library(ggpubr)
library(cowplot)

data_path <- "~/Code/resistingrhythm/data/"
```

# Load all data

```{r, message=FALSE}
# 16: Burst E, with H
exp_code <- 16
osc_codes <- c(100, 101, 102, 103, 104, 105, 110, 115, 120, 125, 130, 135, 140, 145, 150, 155, 160)
osc_rates <- c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0, 3.5, 4.0, 4.5, 5.0, 5.5, 6.0)
stim_codes <- c(0, 1)

results16 <- NULL
for(i in 1:length(osc_codes)){
  for(s_c in stim_codes){
    o_c <- osc_codes[i]
    o_r <- osc_rates[i]

    # Load the csv
    df <- read_csv(paste(data_path, 
                         "exp", as.character(exp_code), 
                         "_stim", as.character(s_c), 
                         "_burst", as.character(o_c),
                         ".csv", sep=""))

    # Add metadata
    df$osc_code <- rep(o_c, nrow(df))
    df$osc_rate <- rep(o_r, nrow(df))
    df$stim_code <- rep(s_c, nrow(df))

    results16 <- rbind(results16, df)
  }
}

results16 %>%
  filter(rate_k > 0) -> results15

# -
# 15: Sustained E, with H
exp_code <- 15
osc_codes <- c(100, 101, 102, 103, 104, 105, 110, 115, 120, 125, 130, 135, 140, 145, 150, 155, 160)
osc_rates <- c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0, 3.5, 4.0, 4.5, 5.0, 5.5, 6.0)
stim_codes <- c(0, 1)

results15 <- NULL
for(i in 1:length(osc_codes)){
  for(s_c in stim_codes){
    o_c <- osc_codes[i]
    o_r <- osc_rates[i]

    # Load the csv
    df <- read_csv(paste(data_path, 
                         "exp", as.character(exp_code), 
                         "_stim", as.character(s_c), 
                         "_osc", as.character(o_c),
                         ".csv", sep=""))

    # Add metadata
    df$osc_code <- rep(o_c, nrow(df))
    df$osc_rate <- rep(o_r, nrow(df))
    df$stim_code <- rep(s_c, nrow(df))

    results15 <- rbind(results15, df)
  }
}

results15 %>%
  filter(rate_k > 0) -> results15

# 22: Sustained E, with NO H
exp_code <- 22
osc_codes <- c(100, 101, 102, 103, 104, 105, 110, 115, 120, 125, 130, 135, 140, 145, 150, 155, 160)
osc_rates <- c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0, 3.5, 4.0, 4.5, 5.0, 5.5, 6.0)
stim_codes <- c(0, 1)

results22 <- NULL
for(i in 1:length(osc_codes)){
  for(s_c in stim_codes){
    o_c <- osc_codes[i]
    o_r <- osc_rates[i]

    # Load the csv
    df <- read_csv(paste(data_path, 
                         "exp", as.character(exp_code), 
                         "_stim", as.character(s_c), 
                         "_osc", as.character(o_c),
                         ".csv", sep=""))

    # Add metadata
    df$osc_code <- rep(o_c, nrow(df))
    df$osc_rate <- rep(o_r, nrow(df))
    df$stim_code <- rep(s_c, nrow(df))

    results22 <- rbind(results22, df)
  }
}

results22 %>%
  filter(rate_k > 0) -> results22

# -
# 21: Sustained I, with H
exp_code <- 21
osc_codes <- c(100, 101, 102, 103, 104, 105, 110, 115, 120, 125, 130, 135, 140, 145, 150, 155, 160)
osc_rates <- c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0, 3.5, 4.0, 4.5, 5.0, 5.5, 6.0)
stim_codes <- c(0, 1)

results21 <- NULL
for(i in 1:length(osc_codes)){
  for(s_c in stim_codes){
    o_c <- osc_codes[i]
    o_r <- osc_rates[i]

    # Load the csv
    df <- read_csv(paste(data_path, 
                         "exp", as.character(exp_code), 
                         "_stim", as.character(s_c), 
                         "_osc", as.character(o_c),
                         ".csv", sep=""))

    # Add metadata
    df$osc_code <- rep(o_c, nrow(df))
    df$osc_rate <- rep(o_r, nrow(df))
    df$stim_code <- rep(s_c, nrow(df))

    results21 <- rbind(results21, df)
  }
}

results21 %>%
  filter(rate_k > 0) -> results21

# -
# 23: Sustained I, with NO H
exp_code <- 23
osc_codes <- c(100, 101, 102, 103, 104, 105, 110, 115, 120, 125, 130, 135, 140, 145, 150, 155, 160)
osc_rates <- c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0, 3.5, 4.0, 4.5, 5.0, 5.5, 6.0)
stim_codes <- c(0, 1)

results23 <- NULL
for(i in 1:length(osc_codes)){
  for(s_c in stim_codes){
    o_c <- osc_codes[i]
    o_r <- osc_rates[i]

    # Load the csv
    df <- read_csv(paste(data_path, 
                         "exp", as.character(exp_code), 
                         "_stim", as.character(s_c), 
                         "_osc", as.character(o_c),
                         ".csv", sep=""))

    # Add metadata
    df$osc_code <- rep(o_c, nrow(df))
    df$osc_rate <- rep(o_r, nrow(df))
    df$stim_code <- rep(s_c, nrow(df))

    results23 <- rbind(results23, df)
  }
}

results23 %>%
  filter(rate_k > 0) -> results23

# Calcium exp, E, sustained
exp_code <- 19
osc_codes <- c(105, 115, 125, 135, 145, 155)
osc_rates <- c(0.5, 1.5, 2.5, 3.5, 4.5, 5.5)
stim_codes <- c(0, 1)

ca_targets <- c(0.026, 0.028, 0.032, 0.034)

results19 <- NULL
for(i in 1:length(osc_codes)){
  for(s_c in stim_codes){
    for(ca in ca_targets){
      o_c <- osc_codes[i]
      o_r <- osc_rates[i]

      # Load the csv
      df <- read_csv(paste(data_path,
                           "exp", as.character(exp_code),
                           "_stim", as.character(s_c),
                           "_osc", as.character(o_c),
                           "_ca", as.character(ca),
                           ".csv", sep=""))

      # Add metadata
      df$osc_code <- rep(o_c, nrow(df))
      df$osc_rate <- rep(o_r, nrow(df))
      df$stim_code <- rep(s_c, nrow(df))
      df$Ca_target <- rep(ca, nrow(df))

      results19 <- rbind(results19, df)
    }
  }
}

# Add default Ca value, from exp
exp_code <- 15
osc_codes <- c(105, 115, 125, 135, 145, 155)
osc_rates <- c(0.5, 1.5, 2.5, 3.5, 4.5, 5.5)
stim_codes <- c(0, 1)
ca_targets <- c(0.03, 0.03, 0.03, 0.03)

for(i in 1:length(osc_codes)){
  for(s_c in stim_codes){
    for(ca in ca_targets){

      o_c <- osc_codes[i]
      o_r <- osc_rates[i]

      # Load the csv
      df <- read_csv(paste(data_path,
                           "exp", as.character(exp_code),
                           "_stim", as.character(s_c),
                           "_osc", as.character(o_c),
                           ".csv", sep=""))

      # Add metadata
      df$osc_code <- rep(o_c, nrow(df))
      df$osc_rate <- rep(o_r, nrow(df))
      df$stim_code <- rep(s_c, nrow(df))
      df$Ca_target <- rep(ca, nrow(df))

      results19 <- rbind(results19, df)
    }
  }
}

# Clean up
rm(df, exp_code, i, o_c, o_r, osc_codes, osc_rates, s_c, stim_codes)
```

# Figure 2. Sustained E

```{r, fig.width=3.0, fig.height=2.0}
shift <- -0.15

# --------------------------------------------------------
# No H, E
results22 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) -> tmp1

results22 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  group_by(osc_rate) %>% 
  mutate(M=mean(mse_var), SD=sd(mse_var)) -> tmp2

ggplot(data=tmp1, mapping=aes(x=osc_rate, y=mse_var, group=osc_rate)) +
  geom_jitter(alpha=0.2, size=0.2, position = position_jitter(width = .05)) +
  geom_point(data=tmp2, mapping=aes(x=osc_rate - shift, y=M), size=0.8) +
  geom_errorbar(data=tmp2, mapping=aes(x=osc_rate - shift, ymin=M - SD, ymax=M + SD), width=.15, size=0.2) +
  # geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
  labs(title="a.", y="Variance (s)", x="Osc. rate (Hz)") +
  lims(y=c(0, .15)) +
  theme_classic() +
  theme(plot.title = element_text(hjust = -.35, size=18, face="bold")) -> p1

rm(tmp1, tmp2)

# -
# With H, E
results15 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) -> tmp1

results15 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  group_by(osc_rate) %>% 
  mutate(M=mean(mse_var), SD=sd(mse_var)) -> tmp2

ggplot(data=tmp1, mapping=aes(x=osc_rate, y=mse_var, group=osc_rate)) +
  geom_jitter(alpha=0.2, size=0.2, position = position_jitter(width = .05)) +
  geom_point(data=tmp2, mapping=aes(x=osc_rate - shift, y=M), size=0.8) +
  geom_errorbar(data=tmp2, mapping=aes(x=osc_rate - shift, ymin=M - SD, ymax=M + SD), width=.15, size=0.2) +
  # geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
  labs(title="b.", y="Variance (s)", x="Osc. rate (Hz)") +
  lims(y=c(0, .01)) +
  theme_classic() +
  theme(plot.title = element_text(hjust = -.5, size=18, face="bold")) -> p2

rm(tmp1, tmp2)

# -
# Rate, no H, E
results22 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) -> tmp1

results22 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  group_by(osc_rate) %>% 
  mutate(M=mean(rate_k - rate_ref), SD=sd(rate_k - rate_ref)) -> tmp2

ggplot(data=tmp1, mapping=aes(x=osc_rate, y=rate_k - rate_ref, group=osc_rate)) +
  geom_jitter(alpha=0.2, size=0.2, position = position_jitter(width = .05)) +
  geom_point(data=tmp2, mapping=aes(x=osc_rate - shift, y=M), size=0.8) +
  geom_errorbar(data=tmp2, mapping=aes(x=osc_rate - shift, ymin=M - SD, ymax=M + SD), width=.15, size=0.2) +
  # geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
  labs(title="c.", y=expression(Delta*" rate (Hz)"), x="Osc. rate (Hz)") +
  lims(y=c(0, 70)) +
  geom_hline(yintercept=0, size=0.2) +
  theme_classic() + 
  theme(plot.title = element_text(hjust = -.25, size=18, face="bold")) -> p3

rm(tmp1, tmp2)

# -
# Rate, with H, E
results15 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) -> tmp1

results15 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  group_by(osc_rate) %>% 
  mutate(M=mean(rate_k - rate_ref), SD=sd(rate_k - rate_ref)) -> tmp2

ggplot(data=tmp1, mapping=aes(x=osc_rate, y=rate_k - rate_ref, group=osc_rate)) +
  geom_jitter(alpha=0.2, size=0.2, position = position_jitter(width = .05)) +
  geom_point(data=tmp2, mapping=aes(x=osc_rate - shift, y=M), size=0.8) +
  geom_errorbar(data=tmp2, mapping=aes(x=osc_rate - shift, ymin=M - SD, ymax=M + SD), width=.15, size=0.2) +
  # geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
  labs(title="d.", y=expression(Delta*" rate (Hz)"), x="Osc. rate (Hz)") +
  lims(y=c(-4, 4)) +
  geom_hline(yintercept=0, size=0.2) +
  theme_classic() +
  theme(plot.title = element_text(hjust = -.3, size=18, face="bold")) -> p4

rm(tmp1, tmp2)

# -
layout_matrix <- rbind(
  c(NA, 7, 7, 8, 8),
  c(5, 1, 1, 2, 2), 
  c(5, 1, 1, 2, 2), 
  c(5, 1, 1, 2, 2), 
  c(5, 1, 1, 2, 2), 
  c(6, 3, 3, 4, 4),
  c(6, 3, 3, 4, 4),
  c(6, 3, 3, 4, 4),
  c(6, 3, 3, 4, 4)
)

p7 <- textGrob("No homeostatsis")
p8 <- textGrob("Homeostatsis")
p5 <- textGrob("Synchrony")
p6 <- textGrob("Excitability")

# -
png(file="fig2.png", bg="white", width=6.0, height=4.0, unit="in", res=300)
grid.arrange(p1, p2, p3, p4, p5, p6, p7, p8, layout_matrix=layout_matrix)
dev.off()

rm(p1, p2, p3, p4, p5, p6, p7, p8)
```

# Figure 3. Burst E

```{r, fig.width=2.25, fig.height=2}
shift <- -0.15

# --------------------------------------------------------
# Var
results16 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) -> tmp1

results16 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  group_by(osc_rate) %>% 
  mutate(M=mean(mse_var), SD=sd(mse_var)) -> tmp2

ggplot(data=tmp1, mapping=aes(x=osc_rate, y=mse_var, group=osc_rate)) +
  geom_jitter(alpha=0.2, size=0.2, position = position_jitter(width = .05), color="dodgerblue3") +
  geom_point(data=tmp2, mapping=aes(x=osc_rate - shift, y=M), size=0.8, color="dodgerblue3") +
  geom_errorbar(data=tmp2, mapping=aes(x=osc_rate - shift, ymin=M - SD, ymax=M + SD), 
                width=.15, size=0.2, color="dodgerblue3") +
  labs(title="a.", y="Variance (s)", x="Osc. rate (Hz)") +
  theme_classic() + 
  theme(plot.title = element_text(hjust = -.6, size=18, face="bold")) -> p1

rm(tmp1, tmp2)

# -
# Rate
results16 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) -> tmp1

results16 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  group_by(osc_rate) %>% 
  mutate(M=mean(rate_k - rate_ref), SD=sd(rate_k - rate_ref)) -> tmp2

ggplot(data=tmp1, mapping=aes(x=osc_rate, y=rate_k - rate_ref, group=osc_rate)) +
  geom_jitter(alpha=0.2, size=0.2, position = position_jitter(width = .05), color="dodgerblue3") +
  geom_point(data=tmp2, mapping=aes(x=osc_rate - shift, y=M), size=0.6, color="dodgerblue3") +
  geom_errorbar(data=tmp2, mapping=aes(x=osc_rate - shift, ymin=M - SD, ymax=M + SD), 
                width=.15, size=0.2, color="dodgerblue3") +
  geom_hline(yintercept=0, size=0.2) +
  labs(title="b.", y=expression(Delta*" rate (Hz)"), x="Osc. rate (Hz)") +
  lims(y=c(-3, 3)) +
  theme_classic() +
  theme(plot.title = element_text(hjust = -.4, size=18, face="bold")) -> p2

# -
# Rate: burst v sustained
tmp3 <- results15
tmp3$osc_mode <- rep("Sustained", nrow(results15))

tmp4 <- results16
tmp4$osc_mode <- rep("Burst", nrow(results16))

tmp5 <- rbind(tmp3, tmp4)
tmp5 %>% 
  ggplot(aes(x=osc_mode, y=rate_k - rate_ref, color=osc_mode)) +
  geom_boxplot(notch = TRUE, width=0.4,  outlier.size=0.05, outlier.alpha=0.5) +
  labs(title="c.", y=expression(Delta*" rate (Hz)"), x="") +
  theme_classic() +
  geom_hline(yintercept=0, size=0.2) +
  lims(y=c(-3, 3)) +
  scale_color_manual(values=c("dodgerblue3", "black"), guide=FALSE) +
  stat_compare_means(method="wilcox.test", label="p.signif", label.x=1.3, size=3) +
  theme(
    axis.text.x = element_text(angle = 70, hjust = 1),
    plot.title = element_text(hjust = -1.6, size=18, face="bold")) -> p5

p3 <- textGrob("Synchrony")
p4 <- textGrob("Excitability")

layout_matrix <- rbind(
  c(3, 1, 1, NA), 
  c(3, 1, 1, NA), 
  c(4, 2, 2, 5),
  c(4, 2, 2, 5),
  c(NA, NA, NA, 5))

# -
png(file="fig3.png", bg="white", width=4.5, height=4.0, unit="in", res=300)
grid.arrange(p1, p2, p3, p4, p5, layout_matrix=layout_matrix)
dev.off()

rm(p1, p2, p3, p4, p5)

# -
print(wilcox.test(x=(tmp3$rate_k - tmp3$rate_ref), y=(tmp4$rate_k - tmp4$rate_ref)))
```

# Figure 4. Weak E oscillations, variance, and error.

```{r, fig.width=2.4, fig.height=1.7}
# --------------------------------------------------------
# Burst
results16 %>% 
  filter(osc_rate >= 0 & osc_rate <= 0.5) %>% 
  group_by(osc_rate) %>% 
  summarise(M_var=mean(mse_var), 
         SD_var=sd(mse_var),
         M_error=mean(mse_error)/1e3,
         SD_error=sd(mse_error)/1e3) -> tmp1

# Sustained
results15 %>% 
  filter(osc_rate >= 0 & osc_rate <= 0.5) %>% 
  group_by(osc_rate) %>% 
  summarise(M_var=mean(mse_var), 
         SD_var=sd(mse_var),
         M_error=mean(mse_error)/1e3,
         SD_error=sd(mse_error)/1e3) -> tmp2

tmp1$osc_mode <- rep("Burst", nrow(tmp1))
tmp2$osc_mode <- rep("Sustained", nrow(tmp2))
tmp3 <- rbind(tmp1, tmp2)

tmp3 %>% 
  ggplot(aes(x=osc_rate, y=M_var, color=osc_mode)) +
  geom_line(size=0.8) +
  geom_point(size=1.5) +
  geom_errorbar(aes(x=osc_rate, ymin=M_var - SD_var, ymax=M_var + SD_var), 
                alpha=0.5, width=.02, size=0.4) +
  scale_color_manual(values=c("dodgerblue3", "black"), name="Oscillation") +
  labs(title="a.", y="Variance (s)", x="Osc. rate (Hz)") +
  theme_classic() + 
  lims(y=c(0, 0.004)) +
  theme(
    legend.position = c(1.4, -0.3),
    legend.background = element_rect(colour ="black"),
    legend.key.size = unit(.5, "cm"),
    plot.title = element_text(hjust = -.45, size=18, face="bold")) -> p1

tmp3 %>% 
  ggplot(aes(x=osc_rate, y=M_error, color=osc_mode)) +
  geom_line(size=0.8) +
  geom_point(size=1.5) +
  geom_errorbar(aes(x=osc_rate, ymin=M_error - SD_error, ymax=M_error + SD_error), 
                alpha=0.5, width=.02, size=0.4) +
  scale_color_manual(values=c("dodgerblue3", "black"), guide=FALSE) +
  labs(title="b.", y="RMSE (s)", x="Osc. rate (Hz)") +
  theme_classic() + 
  theme(plot.title = element_text(hjust = -.5, size=18, face="bold")) -> p2

# p3 <- textGrob("Homeostatsis")
p3 <- textGrob("Synchrony")
p4 <- textGrob("Error")

layout_matrix <- rbind(
  c(3, 1, 1, 5), 
  c(3, 1, 1, 5), 
  c(4, 2, 2, 5),
  c(4, 2, 2, 5))

p5 <- nullGrob()

# -
png(file="fig4.png", bg="white", width=4.8, height=3.3, unit="in", res=300)
grid.arrange(p1, p2, p3, p4, p5, layout_matrix=layout_matrix)
dev.off()

rm(p1, p2, p3, p4, tmp1, tmp2, tmp3)
```

# Figure 5. Sustained I

```{r, fig.width=3.0, fig.height=2.2}
shift <- -0.15

# --------------------------------------------------------
# No H, I
results23 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) -> tmp1

results23 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  group_by(osc_rate) %>% 
  mutate(M=mean(mse_var), SD=sd(mse_var)) -> tmp2

ggplot(data=tmp1, mapping=aes(x=osc_rate, y=mse_var, group=osc_rate)) +
  geom_jitter(alpha=0.2, size=0.2, position = position_jitter(width = .05)) +
  geom_point(data=tmp2, mapping=aes(x=osc_rate - shift, y=M), size=0.8) +
  geom_errorbar(data=tmp2, mapping=aes(x=osc_rate - shift, ymin=M - SD, ymax=M + SD), width=.15, size=0.2) +
  labs(title="a.", y="Variance (s)", x="Osc. rate (Hz)") +
  theme_classic() +
  theme(plot.title = element_text(hjust = -.4, size=18, face="bold")) -> p1

rm(tmp1, tmp2)

# With H
results21 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) -> tmp1

results21 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  group_by(osc_rate) %>% 
  mutate(M=mean(mse_var), SD=sd(mse_var)) -> tmp2

ggplot(data=tmp1, mapping=aes(x=osc_rate, y=mse_var, group=osc_rate)) +
  geom_jitter(alpha=0.2, size=0.2, position = position_jitter(width = .05)) +
  geom_point(data=tmp2, mapping=aes(x=osc_rate - shift, y=M), size=0.8) +
  geom_errorbar(data=tmp2, mapping=aes(x=osc_rate - shift, ymin=M - SD, ymax=M + SD), width=.15, size=0.2) +
  labs(title="b.", y="Variance (s)", x="Osc. rate (Hz)") +
  theme_classic() + 
  theme(plot.title = element_text(hjust = -.5, size=18, face="bold")) -> p2

rm(tmp1, tmp2)

# -
# Rate, no H, E
results23 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) -> tmp1

results23 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  group_by(osc_rate) %>% 
  mutate(M=mean(rate_k - rate_ref), SD=sd(rate_k - rate_ref)) -> tmp2

ggplot(data=tmp1, mapping=aes(x=osc_rate, y=rate_k - rate_ref, group=osc_rate)) +
  geom_jitter(alpha=0.2, size=0.2, position = position_jitter(width = .05)) +
  geom_point(data=tmp2, mapping=aes(x=osc_rate - shift, y=M), size=0.8) +
  geom_errorbar(data=tmp2, mapping=aes(x=osc_rate - shift, ymin=M - SD, ymax=M + SD), width=.15, size=0.2) +
  # geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
  labs(title="c.", y=expression(Delta*" rate (Hz)"), x="Osc. rate (Hz)") +
  geom_hline(yintercept=0, size=0.2) +
  theme_classic() +
  theme(plot.title = element_text(hjust = -.35, size=18, face="bold")) -> p3

rm(tmp1, tmp2)

# -
# Rate, with H, E
results21 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) -> tmp1

results21 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  group_by(osc_rate) %>% 
  mutate(M=mean(rate_k - rate_ref), SD=sd(rate_k - rate_ref)) -> tmp2

ggplot(data=tmp1, mapping=aes(x=osc_rate, y=rate_k - rate_ref, group=osc_rate)) +
  geom_jitter(alpha=0.2, size=0.2, position = position_jitter(width = .05)) +
  geom_point(data=tmp2, mapping=aes(x=osc_rate - shift, y=M), size=0.8) +
  geom_errorbar(data=tmp2, mapping=aes(x=osc_rate - shift, ymin=M - SD, ymax=M + SD), width=.15, size=0.2) +
  # geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
  labs(title="d.", y=expression(Delta*" rate (Hz)"), x="Osc. rate (Hz)") +
  # lims(y=c(-4, 4)) +
  geom_hline(yintercept=0, size=0.2) +
  theme_classic() +
  theme(plot.title = element_text(hjust = -.3, size=18, face="bold")) -> p4

rm(tmp1, tmp2)

# -
layout_matrix <- rbind(
  c(NA, 7, 7, 8, 8),
  c(5, 1, 1, 2, 2), 
  c(5, 1, 1, 2, 2), 
  c(5, 1, 1, 2, 2), 
  c(6, 3, 3, 4, 4),
  c(6, 3, 3, 4, 4),
  c(6, 3, 3, 4, 4)
)

p7 <- textGrob("No homeostatsis")
p8 <- textGrob("Homeostatsis")
p5 <- textGrob("Synchrony")
p6 <- textGrob("Excitability")

# -
png(file="fig5.png", bg="white", width=6, height=4.4, unit="in", res=300)
grid.arrange(p1, p2, p3, p4, p5, p6, p7, p8, layout_matrix=layout_matrix)
dev.off()

rm(p1, p2, p3, p4, p5, p6, p7, p8)
```

# Figure 6. Variable Calcium targets and sustained E

```{r, fig.width=2.4, fig.height=1.7}
# -
# With H, E
# Var
results19 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  group_by(osc_rate, Ca_target) %>% 
  summarise(M=mean(mse_var), SD=sd(mse_var)) -> tmp1

tmp1 %>% 
ggplot(aes(x=osc_rate, y=M, color=factor(Ca_target, levels = c(0.026, 0.028, 0.03, 0.032, 0.034)))) +
  geom_line(size=0.8) +
  geom_point(size=1.5) +
  geom_errorbar(aes(ymin=M - SD, ymax=M + SD), alpha=0.5, width=.1, size=0.4)  +
  labs(title="a", y="Variance (s)", x="Osc. rate (Hz)") +
  scale_color_manual(
    values=c("paleturquoise3", "paleturquoise4", "black", "indianred4", "indianred1"), 
    guide=FALSE) +
  theme_classic() +
  theme(plot.title = element_text(hjust = -.5, size=18, face="bold")) -> p1

# Rate
results19 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  group_by(osc_rate, Ca_target) %>% 
  summarise(M=mean(rate_k - rate_ref), SD=sd(rate_k - rate_ref)) -> tmp2

tmp2 %>% 
ggplot(aes(x=osc_rate, y=M, color=factor(Ca_target, levels = c(0.026, 0.028, 0.03, 0.032, 0.034)))) +
  geom_line(size=0.8) +
  geom_point(size=1.5) +
  geom_errorbar(aes(ymin=M - SD, ymax=M + SD), alpha=0.5, width=.1, size=0.4)  +
  labs(title="b", y=expression(Delta*" rate (Hz)"), x="Osc. rate (Hz)") +
  geom_hline(yintercept=0, size=0.2) +
  scale_color_manual(
    values=c("paleturquoise3", "paleturquoise4", "black", "indianred4", "indianred1"), 
    name="Target [Ca]\n(mmolar)") +
  # lims(y=c(0, .01)) 
  # guides(col = guide_legend(ncol = 2)) +
  theme_classic() +
  theme(
    plot.title = element_text(hjust = -.34, size=18, face="bold"),
    legend.position = c(1.35, 1.5),
    legend.background = element_rect(colour ="black"),
    legend.key.size = unit(.4, "cm")) -> p2

# p3 <- textGrob("Homeostatsis")
p3 <- textGrob("Synchrony")
p4 <- textGrob("Excitability    ")

layout_matrix <- rbind(
  c(3, 1, 1, 5), 
  c(3, 1, 1, 5), 
  c(4, 2, 2, 5),
  c(4, 2, 2, 5))

p5 <- nullGrob()

# -
png(file="fig6.png", bg="white", width=4.8, height=3.2, unit="in", res=300)
grid.arrange(p1, p2, p3, p4, p5, layout_matrix=layout_matrix)
dev.off()

rm(p1, p2, p3, p4, p5, tmp1, tmp2)
```

### 2018-04-28 resistingrhythm/analysis/burst_analysis.Rmd
Rmd vis - tweaks to nearly everything

@@
 ```{r, message=FALSE}
-exp_code <- 3
-osc_codes <- c(0, 1, 3, 5)
-osc_rates <- c(0.5, 1, 3, 5)
-stim_codes <- c(0, 1, 2)
+
+exp_code <- 16
+osc_codes <- c(100, 101, 102, 103, 104, 105, 110, 115, 120, 125, 130, 135, 140, 145, 150, 155, 160)
+osc_rates <- c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0, 3.5, 4.0, 4.5, 5.0, 5.5, 6.0)
+stim_codes <- c(0, 1)
 
@@
 }
+
+# exp_code <- 3
+# osc_codes <- c(0, 1, 3, 5)
+# osc_rates <- c(0.5, 1, 3, 5)
+# stim_codes <- c(0, 1, 2)
+# 
+# results0 <- NULL
+# for(i in 1:length(osc_codes)){
+#   for(s_c in stim_codes){
+#     o_c <- osc_codes[i]
+#     o_r <- osc_rates[i]
+#     
+#     # Load the csv
+#     df <- read_csv(paste(data_path, 
+#                          "exp", as.character(exp_code), 
+#                          "_stim", as.character(s_c), 
+#                          "_burst", as.character(o_c),
+#                          ".csv", sep=""))
+#     
+#     # Add metadata
+#     df$osc_code <- rep(o_c, nrow(df))
+#     df$osc_rate <- rep(o_r, nrow(df))
+#     df$stim_code <- rep(s_c, nrow(df))
+#     
+#     results0 <- rbind(results0, df)
+#   }
+# }
+# 
+# 
+# exp_code <- 14
+# osc_codes <- c(7, 8, 9, 10, 11, 12, 13, 14, 15)
+# osc_rates <- c(0.05, 0.1, 0.15, 0.2, 0.25, 0.3, 0.35, 0.4, 0.45)
+# stim_codes <- c(0, 1, 2)
+# 
+# results1 <- NULL
+# for(i in 1:length(osc_codes)){
+#   for(s_c in stim_codes){
+#     o_c <- osc_codes[i]
+#     o_r <- osc_rates[i]
+#     
+#     # Load the csv
+#     df <- read_csv(paste(data_path, 
+#                          "exp", as.character(exp_code), 
+#                          "_stim", as.character(s_c), 
+#                          "_burst", as.character(o_c),
+#                          ".csv", sep=""))
+#     
+#     # Add metadata
+#     df$osc_code <- rep(o_c, nrow(df))
+#     df$osc_rate <- rep(o_r, nrow(df))
+#     df$stim_code <- rep(s_c, nrow(df))
+#     
+#     results1 <- rbind(results1, df)
+#   }
+# }
+# 
+# results0 %>% 
+#   select(k, osc_rate, osc_code, kappa_error, kappa_coord, mse_error, 
+#          mse_var, abs_error, abs_var, rate_k, rate_ref, stim_code) -> results0
+# results1 %>% 
+#   select(k, osc_rate, osc_code, kappa_error, kappa_coord, mse_error, mse_var, abs_error, abs_var, rate_k, rate_ref, stim_code) -> results1
+# results <- rbind(results0, results1)
+
+results %>% 
+  filter(kappa_coord > 0) -> results
 ```
@@
 
-```{r, fig.width=1.0, fig.height=0.8}
+```{r, fig.width=2.0, fig.height=0.8}
 results %>% 
@@
   geom_jitter(alpha=0.1, size=0.1) +
-  geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
+  # geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
   labs(y="Kappa", x="Osc. rate (Hz)") +
@@
 
-```{r, fig.width=1.0, fig.height=0.8}
+```{r, fig.width=3.0, fig.height=0.8}
 results %>% 
   ggplot(aes(x=osc_rate, y=mse_error, group=osc_rate)) +
-  geom_jitter(alpha=0.1, size=0.1) +
+  # geom_jitter(alpha=0.1, size=0.1) +
   geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
@@
 
-```{r, fig.width=1.8, fig.height=0.8}
+```{r, fig.width=2.8, fig.height=0.8}
 results %>% 
@@
   geom_point(size=0.4, alpha=0.2) + 
+  geom_smooth(method='lm', color="red", alpha=0.4, se=FALSE, size=0.1) +
   theme_classic() + 

### 2018-04-28 resistingrhythm/analysis/ca_analysis_v2.Rmd
Rmd vis - tweaks to nearly everything

@@
 ```{r, message=FALSE}
-exp_code <- 1
-osc_codes <- c(1, 3, 5)
-osc_rates <- c(1, 3, 5)
-stim_codes <- c(0)
+exp_code <- 19
+osc_codes <- c(101, 103, 105, 115, 125, 135, 145, 155)
+osc_rates <- c(0.1, 0.3, 0.5, 1.5, 2.5, 3.5, 4.5, 5.5)
+stim_codes <- c(0, 1)
 
-# Load exp 1 results for comparison
+ca_targets <- c(0.026, 0.028, 0.032, 0.034)
 
@@
   for(s_c in stim_codes){
+    for(ca in ca_targets){
       o_c <- osc_codes[i]
@@
                            "_osc", as.character(o_c),
+                           "_ca", as.character(ca),
                            ".csv", sep=""))
@@
       df$stim_code <- rep(s_c, nrow(df))
-    df$Ca_target <- rep("0.030", nrow(df))
-
-    results <- rbind(results, df)
-  }
-}
-
-# Rename Ca to match new format
-results %>% 
-  rename(Ca_obs_target = Ca_k) %>% 
-  mutate(Ca_obs_ref = Ca_obs_target) -> results
-
-# ------------------------------------------------------------------
-# exp_code <- 2
-# ca_values <- c("0.032", "0.034", "0.036", "0.038")
-
-exp_code <- 7
-ca_values <- c("0.032", "0.034", "0.036")
-for(i in 1:length(osc_codes)){
-  for(s_c in stim_codes){
-    for(ca in ca_values){
-      o_c <- osc_codes[i]
-      o_r <- osc_rates[i]
-
-      # Generate name
-      file_name <- paste(data_path, 
-                         "exp", as.character(exp_code), 
-                         "_stim", as.character(s_c), 
-                         "_osc", as.character(o_c),
-                         "_Ca", ca,
-                         ".csv", sep="")
-
-      if (file.exists(file_name)){
-        # Load
-        df <- read_csv(file_name)
-
-        # Add metadata
-        df$osc_code <- rep(o_c, nrow(df))
-        df$osc_rate <- rep(o_r, nrow(df))
-        df$stim_code <- rep(s_c, nrow(df))
+      df$Ca_target <- rep(ca, nrow(df))
 
@@
 }
-}
+
+# exp_code <- 1
+# osc_codes <- c(1, 3, 5)
+# osc_rates <- c(1, 3, 5)
+# stim_codes <- c(0)
+# 
+# # Load exp 1 results for comparison
+# 
+# results <- NULL
+# for(i in 1:length(osc_codes)){
+#   for(s_c in stim_codes){
+#     o_c <- osc_codes[i]
+#     o_r <- osc_rates[i]
+#     
+#     # Load the csv
+#     df <- read_csv(paste(data_path, 
+#                          "exp", as.character(exp_code), 
+#                          "_stim", as.character(s_c), 
+#                          "_osc", as.character(o_c),
+#                          ".csv", sep=""))
+#     
+#     # Add metadata
+#     df$osc_code <- rep(o_c, nrow(df))
+#     df$osc_rate <- rep(o_r, nrow(df))
+#     df$stim_code <- rep(s_c, nrow(df))
+#     df$Ca_target <- rep("0.030", nrow(df))
+#     
+#     results <- rbind(results, df)
+#   }
+# }
+# 
+# # Rename Ca to match new format
+# results %>% 
+#   rename(Ca_obs_target = Ca_k) %>% 
+#   mutate(Ca_obs_ref = Ca_obs_target) -> results
+# 
+# # ------------------------------------------------------------------
+# # exp_code <- 2
+# # ca_values <- c("0.032", "0.034", "0.036", "0.038")
+# 
+# exp_code <- 7
+# ca_values <- c("0.032", "0.034", "0.036")
+# for(i in 1:length(osc_codes)){
+#   for(s_c in stim_codes){
+#     for(ca in ca_values){
+#       o_c <- osc_codes[i]
+#       o_r <- osc_rates[i]
+#       
+#       # Generate name
+#       file_name <- paste(data_path, 
+#                          "exp", as.character(exp_code), 
+#                          "_stim", as.character(s_c), 
+#                          "_osc", as.character(o_c),
+#                          "_Ca", ca,
+#                          ".csv", sep="")
+#     
+#       if (file.exists(file_name)){
+#         # Load
+#         df <- read_csv(file_name)
+# 
+#         # Add metadata
+#         df$osc_code <- rep(o_c, nrow(df))
+#         df$osc_rate <- rep(o_r, nrow(df))
+#         df$stim_code <- rep(s_c, nrow(df))
+#         
+#         results <- rbind(results, df)  
+#       }
+#     }
+#   }
+# }
 
@@
              color=factor(Ca_target))) +
-  geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
+  # geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
+  geom_jitter(size=.1) +
+  facet_grid(.~Ca_target) +
   labs(y="Kappa", x="Osc. rate (Hz)") +
@@
              color=factor(Ca_target))) +
-  geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
+  # geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
+  geom_jitter(size=.1) +
+  facet_grid(.~Ca_target) +
   labs(y="Variance", x="Osc. rate (Hz)") +
@@
 results %>% 
-  ggplot(aes(x=osc_rate, y=mse_error, 
+  ggplot(aes(x=osc_rate, y=mse_error/1e3, 
              group=interaction(osc_rate, Ca_target),
              color=factor(Ca_target))) +
-  geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
+  # geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
+  geom_jitter(size=.1) +
+  facet_grid(.~Ca_target) +
   labs(y="Error", x="Osc. rate (Hz)") +
@@
              color=factor(Ca_target))) +
-  geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
-  labs(y="Firing rate (Hz)", x="Rate (Hz") +
+  # geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
+  geom_jitter(size=.1) +
+  facet_grid(.~Ca_target) +
+  labs(y="Mod. rate (Hz)", x="Rate (Hz") +
   theme_classic() 
@@
 results %>% 
-  ggplot(aes(x=osc_rate, y=rate_ref - rate_k, 
+  ggplot(aes(x=osc_rate, y=rate_k - rate_ref, 
              group=interaction(osc_rate, Ca_target),
              color=factor(Ca_target))) +
-  geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
-  geom_hline(yintercept=0, size=0.5) +
-  labs(y="Rate diff. (Hz)", x="Osc. rate (Hz)") +
+  # geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
+  geom_jitter(size=.1) +
+  facet_grid(.~Ca_target) +
+  labs(y="Delta rate (Hz)", x="Rate (Hz)") +
   theme_classic() 
@@
 
-```{r, fig.width=2.2, fig.height=0.8}
+```{r, fig.width=2, fig.height=2}
 results %>% 
-  ggplot(aes(x=mse_error, y=kappa_coord, color=Ca_target)) +
-  geom_point(alpha=0.5, size=0.2) + 
-  theme_classic() + 
-  labs(y="Kappa", x="Error") +
-  facet_grid(.~osc_rate)
+  ggplot(aes(x=mse_error/1e3, y=mse_var, 
+             group=interaction(osc_rate, Ca_target),
+             color=factor(Ca_target))) +
+  # geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
+  geom_jitter(size=.1) +
+  facet_grid(Ca_target~.) +
+  labs(y="Variance", x="Error") +
+  theme_classic() 
 ```
-
-```{r, fig.width=1.8, fig.height=0.8}
-results %>% 
-  ggplot(aes(x=mse_error, y=mse_var, color=Ca_target)) +
-  geom_point(alpha=0.5, size=0.2) + 
-  theme_classic() + 
-  labs(y="Variance", x="Error") +
-  facet_grid(.~osc_rate)
-```

### 2018-04-28 resistingrhythm/analysis/step_analysis.Rmd
Rmd vis - tweaks to nearly everything

---
title: "Ca exp analysis -- 4/18/2018"
output: html_notebook
---

```{r}
library(tidyverse)
library(gridExtra)

data_path <- "~/Code/resistingrhythm/data/"
```

```{r, message=FALSE}
exp_code <- 17
osc_codes <- c(200, 201, 202, 203, 204, 205)
osc_rates <- c(0.0, 0.1, 0.2, 0.3, 0.4, 0.5)

step_codes <- c(0, 1, 2, 3)
step_currents <- c(0.0, -0.5e-6, -0.75e-6, -1.0e-6)

stim_codes <- c(0, 1)

results <- NULL
for(i in 1:length(osc_codes)){
  for(j in 1:length(step_codes)){

    for(s_c in stim_codes){
      o_c <- osc_codes[i]
      o_r <- osc_rates[i]

      stp <- step_codes[j]
      I <- step_currents[j]

      # Load the csv
      df <- read_csv(paste(data_path, 
                           "exp", as.character(exp_code), 
                           "_stim", as.character(s_c), 
                           "_burst", as.character(o_c),
                           "_step", as.character(stp),
                           ".csv", sep=""))

      # Add metadata
      df$osc_code <- rep(o_c, nrow(df))
      df$osc_rate <- rep(o_r, nrow(df))
      df$stim_code <- rep(s_c, nrow(df))

      df$step_code <- rep(stp, nrow(df))
      df$step_current <- rep(I, nrow(df))

      results <- rbind(results, df)
    }
  }
}

results %>% 
  filter(kappa_coord > 0) -> results

rm(df, exp_code, step_codes, step_currents, osc_codes, osc_rates, stp, I, j, i, o_c, o_r, s_c, stim_codes)
```

# Osc rate 
## By variance

```{r, fig.width=2.0, fig.height=1}
results %>% 
  ggplot(aes(x=osc_rate, y=kappa_coord, 
             group=interaction(osc_rate, step_current),
             color=factor(step_current))) +
  geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
  labs(y="Kappa", x="Osc. rate (Hz)") +
  theme_classic() 
```
```{r, fig.width=2.0, fig.height=1}
results %>% 
  ggplot(aes(x=osc_rate, y=mse_var, 
             group=interaction(osc_rate, step_current),
             color=factor(step_current))) +
  geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
  labs(y="Variance", x="Osc. rate (Hz)") +
  theme_classic() 
```

## By error

```{r, fig.width=2.0, fig.height=1}
results %>% 
  ggplot(aes(x=osc_rate, y=mse_error, 
             group=interaction(osc_rate, step_current),
             color=factor(step_current))) +
  geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
  labs(y="Error", x="Osc. rate (Hz)") +
  theme_classic() 
```

# Var vesus error

```{r, fig.width=3.0, fig.height=0.8}
results %>% 
  ggplot(aes(x=mse_error, y=mse_var, 
             color=factor(step_current))) +
  geom_point(size=0.1) +
  labs(y="Variance", x="Error") +
  facet_grid(.~step_current) +
  theme_classic() 
```

### 2018-04-28 resistingrhythm/analysis/tonic_analysis.Rmd
Rmd vis - tweaks to nearly everything

---
title: "Ca exp analysis -- 4/18/2018"
output: html_notebook
---

```{r}
library(tidyverse)
library(gridExtra)

data_path <- "~/Code/resistingrhythm/data/"
```

```{r, message=FALSE}
exp_code <- 18
osc_codes <- c(101, 103, 105, 115, 125, 135, 145, 155)
osc_rates <- c(0.1, 0.3, 0.5, 1.5, 2.5, 3.5, 4.5, 5.5)

tonic_codes <- c(1, 2, 3)
tonic_currents <- c(-0.5e-6, -0.75e-6, -1.0e-6)

stim_codes <- c(0, 1)

results <- NULL
for(i in 1:length(osc_codes)){
  for(j in 1:length(tonic_codes)){

    for(s_c in stim_codes){
      o_c <- osc_codes[i]
      o_r <- osc_rates[i]

      stp <- tonic_codes[j]
      I <- tonic_currents[j]

      # Load the csv
      df <- read_csv(paste(data_path, 
                           "exp", as.character(exp_code), 
                           "_stim", as.character(s_c), 
                           "_osc", as.character(o_c),
                           "_tonic", as.character(stp),
                           ".csv", sep=""))

      # Add metadata
      df$osc_code <- rep(o_c, nrow(df))
      df$osc_rate <- rep(o_r, nrow(df))
      df$stim_code <- rep(s_c, nrow(df))

      df$tonic_code <- rep(stp, nrow(df))
      df$tonic_current <- rep(I, nrow(df))

      results <- rbind(results, df)
    }
  }
}

results %>% 
  filter(kappa_coord > 0) -> results

rm(df, exp_code, tonic_codes, tonic_currents, osc_codes, osc_rates, stp, I, j, i, o_c, o_r, s_c, stim_codes)
```

# Osc rate 
## By variance

```{r, fig.width=2.0, fig.height=1}
results %>% 
  ggplot(aes(x=osc_rate, y=kappa_coord, 
             group=interaction(osc_rate, tonic_current),
             color=factor(tonic_current))) +
  # geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
  geom_jitter(size=.1) +
  labs(y="Kappa", x="Osc. rate (Hz)") +
  theme_classic() 
```
```{r, fig.width=2.0, fig.height=1}
results %>% 
  ggplot(aes(x=osc_rate, y=mse_var, 
             group=interaction(osc_rate, tonic_current),
             color=factor(tonic_current))) +
  # geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
  geom_jitter(size=.1) +
  labs(y="Variance", x="Osc. rate (Hz)") +
  theme_classic() 
```

## By error

```{r, fig.width=2.0, fig.height=1}
results %>% 
  ggplot(aes(x=osc_rate, y=mse_error, 
             group=interaction(osc_rate, tonic_current),
             color=factor(tonic_current))) +
  # geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
  geom_jitter(size=.1) +
  labs(y="Error", x="Osc. rate (Hz)") +
  theme_classic() 
```

# Var vesus error

```{r, fig.width=3.0, fig.height=0.8}
results %>% 
  ggplot(aes(x=mse_error, y=mse_var, 
             color=factor(tonic_current))) +
  geom_point(size=0.1) +
  labs(y="Variance", x="Error") +
  facet_grid(.~tonic_current) +
  theme_classic() 
```

### 2018-04-29 resistingrhythm/analysis/paper_figures.Rmd
Merged burst and sustained E figures

@@
 
-# Figure 2. Sustained E
+# Figure 2. Sustained and burst E
 
-```{r, fig.width=3.0, fig.height=2.0}
+```{r, fig.width=4.5, fig.height=2.0}
 shift <- -0.15
@@
   # geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
-  labs(title="c.", y=expression(Delta*" rate (Hz)"), x="Osc. rate (Hz)") +
+  labs(title="d.", y=expression(Delta*" rate (Hz)"), x="Osc. rate (Hz)") +
   lims(y=c(0, 70)) +
@@
   # geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
-  labs(title="d.", y=expression(Delta*" rate (Hz)"), x="Osc. rate (Hz)") +
+  labs(title="e.", y=expression(Delta*" rate (Hz)"), x="Osc. rate (Hz)") +
   lims(y=c(-4, 4)) +
@@
 
-# -
-layout_matrix <- rbind(
-  c(NA, 7, 7, 8, 8),
-  c(5, 1, 1, 2, 2), 
-  c(5, 1, 1, 2, 2), 
-  c(5, 1, 1, 2, 2), 
-  c(5, 1, 1, 2, 2), 
-  c(6, 3, 3, 4, 4),
-  c(6, 3, 3, 4, 4),
-  c(6, 3, 3, 4, 4),
-  c(6, 3, 3, 4, 4)
-)
+# --------------------------------------------------------
+# Bursts
 
-p7 <- textGrob("No homeostatsis")
-p8 <- textGrob("Homeostatsis")
-p5 <- textGrob("Synchrony")
-p6 <- textGrob("Excitability")
-
-# -
-png(file="fig2.png", bg="white", width=6.0, height=4.0, unit="in", res=300)
-grid.arrange(p1, p2, p3, p4, p5, p6, p7, p8, layout_matrix=layout_matrix)
-dev.off()
-
-rm(p1, p2, p3, p4, p5, p6, p7, p8)
-```
-
-# Figure 3. Burst E
-
-```{r, fig.width=2.25, fig.height=2}
-shift <- -0.15
-
-# --------------------------------------------------------
 # Var
@@
                 width=.15, size=0.2, color="dodgerblue3") +
-  labs(title="a.", y="Variance (s)", x="Osc. rate (Hz)") +
+  labs(title="c.", y="Variance (s)", x="Osc. rate (Hz)") +
   theme_classic() + 
-  theme(plot.title = element_text(hjust = -.6, size=18, face="bold")) -> p1
+  lims(y=c(0, .01)) +
+  theme(plot.title = element_text(hjust = -.6, size=18, face="bold")) -> p5
 
@@
   geom_hline(yintercept=0, size=0.2) +
-  labs(title="b.", y=expression(Delta*" rate (Hz)"), x="Osc. rate (Hz)") +
+  labs(title="d.", y=expression(Delta*" rate (Hz)"), x="Osc. rate (Hz)") +
   lims(y=c(-3, 3)) +
   theme_classic() +
-  theme(plot.title = element_text(hjust = -.4, size=18, face="bold")) -> p2
+  theme(plot.title = element_text(hjust = -.4, size=18, face="bold")) -> p6
 
@@
   ggplot(aes(x=osc_mode, y=rate_k - rate_ref, color=osc_mode)) +
-  geom_boxplot(notch = TRUE, width=0.4,  outlier.size=0.05, outlier.alpha=0.5) +
-  labs(title="c.", y=expression(Delta*" rate (Hz)"), x="") +
+  geom_point(size=-1, aes(fill=osc_mode)) +
+  geom_boxplot(notch = TRUE, width=0.4,  outlier.size=0.05, outlier.alpha=0.5, show.legend=FALSE) +
+  labs(title="f.", y=expression(Delta*" rate (Hz)"), x="") +
   theme_classic() +
@@
   lims(y=c(-3, 3)) +
-  scale_color_manual(values=c("dodgerblue3", "black"), guide=FALSE) +
-  stat_compare_means(method="wilcox.test", label="p.signif", label.x=1.3, size=3) +
+  scale_fill_manual(values=c("dodgerblue3", "black"), name="Oscillation") +
+  scale_color_manual(values=c("dodgerblue3", "black"), name="Oscillation") +
+  stat_compare_means(method="wilcox.test", label="p.signif", 
+                     label.x=1.3, size=3, show.legend=FALSE) +
+  guides(fill = guide_legend(override.aes = list(shape = 15, size = 7, alpha=0.8))) +
   theme(
+    legend.position = c(0.1, 2),
+    legend.background = element_rect(colour ="black"),
+    legend.key.size = unit(.5, "cm"),
     axis.text.x = element_text(angle = 70, hjust = 1),
-    plot.title = element_text(hjust = -1.6, size=18, face="bold")) -> p5
+    plot.title = element_text(hjust = -1.2, size=18, face="bold")) -> p7
 
-p3 <- textGrob("Synchrony")
-p4 <- textGrob("Excitability")
-
-layout_matrix <- rbind(
-  c(3, 1, 1, NA), 
-  c(3, 1, 1, NA), 
-  c(4, 2, 2, 5),
-  c(4, 2, 2, 5),
-  c(NA, NA, NA, 5))
+# NEW
 
 # -
-png(file="fig3.png", bg="white", width=4.5, height=4.0, unit="in", res=300)
-grid.arrange(p1, p2, p3, p4, p5, layout_matrix=layout_matrix)
-dev.off()
+layout_matrix <- rbind(
+  c(NA, 8, 8, 9, 9, 9, 9, NA),
+  c(10, 1, 1, 2, 2, 5, 5, NA), 
+  c(10, 1, 1, 2, 2, 5, 5, NA), 
+  c(10, 1, 1, 2, 2, 5, 5, NA), 
+  c(10, 1, 1, 2, 2, 5, 5, 7), 
+  c(11, 3, 3, 4, 4, 6, 6, 7),
+  c(11, 3, 3, 4, 4, 6, 6, 7),
+  c(11, 3, 3, 4, 4, 6, 6, 7),
+  c(11, 3, 3, 4, 4, 6, 6, 7)
+)
 
-rm(p1, p2, p3, p4, p5)
+p8 <- textGrob("No homeostatsis")
+p9 <- textGrob("Homeostatsis")
+p10 <- textGrob("Synchrony")
+p11 <- textGrob("Excitability")
+
+grid.arrange(p1, p2, p3, p4, p5, p6, p7, p8, p9, p10, p11, layout_matrix=layout_matrix)
 
 # -
+png(file="fig2.png", bg="white", width=9.0, height=4.0, unit="in", res=300)
+grid.arrange(p1, p2, p3, p4, p5, p6, p7, p8, p9, p10, p11, layout_matrix=layout_matrix)
+dev.off()
+```
+
+```{r}
 print(wilcox.test(x=(tmp3$rate_k - tmp3$rate_ref), y=(tmp4$rate_k - tmp4$rate_ref)))
@@
 
-# Figure 4. Weak E oscillations, variance, and error.
+# Figure 3. Weak E oscillations, variance, and error.
 
@@
 # -
-png(file="fig4.png", bg="white", width=4.8, height=3.3, unit="in", res=300)
+png(file="fig3.png", bg="white", width=4.8, height=3.3, unit="in", res=300)
 grid.arrange(p1, p2, p3, p4, p5, layout_matrix=layout_matrix)
@@
 
-# Figure 5. Sustained I
+# Figure 4. Sustained I
 
@@
 # -
-png(file="fig5.png", bg="white", width=6, height=4.4, unit="in", res=300)
+png(file="fig4.png", bg="white", width=6, height=4.4, unit="in", res=300)
 grid.arrange(p1, p2, p3, p4, p5, p6, p7, p8, layout_matrix=layout_matrix)
@@
 
-# Figure 6. Variable Calcium targets and sustained E
+# Figure 5. Variable Calcium targets and sustained E
 
@@
 p3 <- textGrob("Synchrony")
-p4 <- textGrob("Excitability    ")
+p4 <- textGrob("Excitability")
 
@@
 # -
-png(file="fig6.png", bg="white", width=4.8, height=3.2, unit="in", res=300)
+png(file="fig5.png", bg="white", width=4.8, height=3.2, unit="in", res=300)
 grid.arrange(p1, p2, p3, p4, p5, layout_matrix=layout_matrix)

### 2018-04-30 resistingrhythm/neurons.py
Added burst500 (4 cycle) and exp31 and 32

@@ -90,7 +90,7 @@ def HHH(time,
 
     g_Na = 100 * msiemens
     g_K = 80 * msiemens
-    g_KCa = 80 * msiemens
+    g_KCa = 40 * msiemens
     g_Ca = 0.01 * msiemens
     g_l = 1.0 * msiemens
 
@@ -110,6 +110,7 @@ def HHH(time,
     G_Ca = 3 * msiemens
     G_Na = 360 * msiemens
     G_K = 180 * msiemens
+    G_KCa = 90 * msiemens
 
     # ----------------------------------------------------
     eqs = """
@@ -146,7 +147,7 @@ def HHH(time,
     dg_osc/dt = -g_osc / tau_osc : siemens
     """ + """
     Ca_target : mmolar
-    g_KCa : siemens
+    # g_KCa : siemens
     """
 
     if homeostasis:
@@ -154,12 +155,14 @@ def HHH(time,
         dg_Na/dt = (1 / tau_h) * (G_Na / (1 + exp(1 * (Ca - Ca_target)/delta)) - g_Na) : siemens 
         dg_Ca/dt = (1 / tau_h) * (G_Ca / (1 + exp(1 * (Ca - Ca_target)/delta)) - g_Ca) : siemens 
         dg_K/dt = (1 / tau_h) * (G_K / (1 + exp(-1 * (Ca - Ca_target)/delta)) - g_K) : siemens 
+        dg_KCa/dt = (1 / tau_h) * (G_KCa / (1 + exp(-1 * (Ca - Ca_target)/delta)) - g_KCa) : siemens 
         """
     else:
         eqs += """
         g_Na : siemens
         g_K : siemens
         g_Ca : siemens
+        g_KCa : siemens
         """
 
     # Setup the current
@@ -172,6 +175,10 @@ def HHH(time,
     # ----------------------------------------------------
     # Def the net by hand....
     net = Network()
+    to_monitor = [
+        'V', 'g_total', 'g_Na', 'g_Ca', 'g_K', 'g_KCa', 'Ca', 'I_Ca', 'I_Na',
+        'I_K'
+    ]
 
     # -
     # The target pop....
@@ -204,6 +211,7 @@ def HHH(time,
         C_in.w_in = w_in * siemens
 
         net.add([P_in, C_in])
+        to_monitor.append('I_in')
 
     # -
     # Connect osc
@@ -223,15 +231,12 @@ def HHH(time,
         C_osc.w_osc = w_osc * siemens
 
         net.add([P_osc, C_osc])
[…]

### 2018-04-30 resistingrhythm/analysis/paper_figures.Rmd
Tweaks to paper figures

@@
 ```{r, message=FALSE}
+# -----------------------------------------------------------------------
 # 16: Burst E, with H
@@
 
-# -
+# -----------------------------------------------------------------------
 # 15: Sustained E, with H
@@
 
+# -----------------------------------------------------------------------
 # 22: Sustained E, with NO H
@@
 
-# -
+# -----------------------------------------------------------------------
 # 21: Sustained I, with H
@@
 
-# -
+# -----------------------------------------------------------------------
 # 23: Sustained I, with NO H
@@
 
+# -----------------------------------------------------------------------
+# 30: Burst I, with H
+exp_code <- 30
+osc_codes <- c(100, 101, 102, 103, 104, 105, 110, 115, 120, 125, 130, 135, 140, 145, 150, 155, 160)
+osc_rates <- c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0, 3.5, 4.0, 4.5, 5.0, 5.5, 6.0)
+stim_codes <- c(0, 1)
+
+results30 <- NULL
+for(i in 1:length(osc_codes)){
+  for(s_c in stim_codes){
+    o_c <- osc_codes[i]
+    o_r <- osc_rates[i]
+
+    # Load the csv
+    df <- read_csv(paste(data_path, 
+                         "exp", as.character(exp_code), 
+                         "_stim", as.character(s_c), 
+                         "_burst", as.character(o_c),
+                         ".csv", sep=""))
+
+    # Add metadata
+    df$osc_code <- rep(o_c, nrow(df))
+    df$osc_rate <- rep(o_r, nrow(df))
+    df$stim_code <- rep(s_c, nrow(df))
+
+    results30 <- rbind(results30, df)
+  }
+}
+
+results30 %>%
+  filter(rate_k > 0) -> results30
+
+# -----------------------------------------------------------------------
 # Calcium exp, E, sustained
@@
 
+# -----------------------------------------------------------------------
 # Add default Ca value, from exp
@@
 
-# Figure 2. Sustained and burst E
+# Figure 2. Excitatory oscillations, sustained and burst
 
-```{r, fig.width=4.5, fig.height=2.0}
+```{r, fig.width=4.5, fig.height=2.25}
 shift <- -0.15
@@
 layout_matrix <- rbind(
+  c(12, 12, 12, 12, 12, 12, 12, 12),
   c(NA, 8, 8, 9, 9, 9, 9, NA),
@@
 p11 <- textGrob("Excitability")
+p12 <- textGrob("Excitatory modulation")
 
-grid.arrange(p1, p2, p3, p4, p5, p6, p7, p8, p9, p10, p11, layout_matrix=layout_matrix)
+grid.arrange(p1, p2, p3, p4, p5, p6, p7, p8, p9, p10, p11, p12, layout_matrix=layout_matrix)
 
 # -
-png(file="fig2.png", bg="white", width=9.0, height=4.0, unit="in", res=300)
-grid.arrange(p1, p2, p3, p4, p5, p6, p7, p8, p9, p10, p11, layout_matrix=layout_matrix)
+png(file="fig2.png", bg="white", width=9.0, height=4.5, unit="in", res=300)
+grid.arrange(p1, p2, p3, p4, p5, p6, p7, p8, p9, p10, p11, p12, layout_matrix=layout_matrix)
 dev.off()
@@
 layout_matrix <- rbind(
+  c(6, 6, 6, 6), 
   c(3, 1, 1, 5), 
   c(3, 1, 1, 5),
+  c(3, 1, 1, 5),
+  c(3, 1, 1, 5), 
+  c(4, 2, 2, 5),
+  c(4, 2, 2, 5),
   c(4, 2, 2, 5),
@@
 p5 <- nullGrob()
+p6 <- textGrob("Weak excitatory modulation")
 
 # -
-png(file="fig3.png", bg="white", width=4.8, height=3.3, unit="in", res=300)
-grid.arrange(p1, p2, p3, p4, p5, layout_matrix=layout_matrix)
+png(file="fig3.png", bg="white", width=4.4, height=3.8, unit="in", res=300)
+grid.arrange(p1, p2, p3, p4, p5, p6, layout_matrix=layout_matrix)
 dev.off()
@@
 
-# Figure 4. Sustained I
+# Figure 2. Inhibitory oscillations, sustained and burst
 
-```{r, fig.width=3.0, fig.height=2.2}
+```{r, fig.width=4.5, fig.height=2.0}
 shift <- -0.15
+# 23 No H
+# 21 w H
+# 30 burst
 
 # --------------------------------------------------------
-# No H, I
+# No H, E
 results23 %>% 
@@
   geom_errorbar(data=tmp2, mapping=aes(x=osc_rate - shift, ymin=M - SD, ymax=M + SD), width=.15, size=0.2) +
+  # geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
   labs(title="a.", y="Variance (s)", x="Osc. rate (Hz)") +
+  lims(y=c(0, .15)) +
   theme_classic() +
-  theme(plot.title = element_text(hjust = -.4, size=18, face="bold")) -> p1
+  theme(plot.title = element_text(hjust = -.35, size=18, face="bold")) -> p1
 
@@
 
-# With H
+# -
+# With H, E
 results21 %>% 
@@
   geom_errorbar(data=tmp2, mapping=aes(x=osc_rate - shift, ymin=M - SD, ymax=M + SD), width=.15, size=0.2) +
+  # geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
   labs(title="b.", y="Variance (s)", x="Osc. rate (Hz)") +
+  # lims(y=c(0, .01)) +
   theme_classic() +
@@
   # geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
-  labs(title="c.", y=expression(Delta*" rate (Hz)"), x="Osc. rate (Hz)") +
+  labs(title="d.", y=expression(Delta*" rate (Hz)"), x="Osc. rate (Hz)") +
+  # lims(y=c(0, 70)) +
   geom_hline(yintercept=0, size=0.2) +
   theme_classic() + 
-  theme(plot.title = element_text(hjust = -.35, size=18, face="bold")) -> p3
+  theme(plot.title = element_text(hjust = -.25, size=18, face="bold")) -> p3
 
@@
   # geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
-  labs(title="d.", y=expression(Delta*" rate (Hz)"), x="Osc. rate (Hz)") +
+  labs(title="e.", y=expression(Delta*" rate (Hz)"), x="Osc. rate (Hz)") +
   # lims(y=c(-4, 4)) +
@@
 
+# --------------------------------------------------------
+# Bursts
+
+# Var
+results30 %>% 
+  filter(osc_rate < 0.1 | osc_rate > 0.4) -> tmp1
+
+results30 %>% 
+  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
+  group_by(osc_rate) %>% 
+  mutate(M=mean(mse_var), SD=sd(mse_var)) -> tmp2
+
+ggplot(data=tmp1, mapping=aes(x=osc_rate, y=mse_var, group=osc_rate)) +
+  geom_jitter(alpha=0.2, size=0.2, position = position_jitter(width = .05), color="dodgerblue3") +
+  geom_point(data=tmp2, mapping=aes(x=osc_rate - shift, y=M), size=0.8, color="dodgerblue3") +
+  geom_errorbar(data=tmp2, mapping=aes(x=osc_rate - shift, ymin=M - SD, ymax=M + SD), 
+                width=.15, size=0.2, color="dodgerblue3") +
+  labs(title="c.", y="Variance (s)", x="Osc. rate (Hz)") +
+  theme_classic() + 
+  # lims(y=c(0, .01)) +
+  theme(plot.title = element_text(hjust = -.6, size=18, face="bold")) -> p5
+
+rm(tmp1, tmp2)
+
+# -
+# Rate
+results30 %>% 
+  filter(osc_rate < 0.1 | osc_rate > 0.4) -> tmp1
+
+results30 %>% 
+  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
+  group_by(osc_rate) %>% 
+  mutate(M=mean(rate_k - rate_ref), SD=sd(rate_k - rate_ref)) -> tmp2
+
+ggplot(data=tmp1, mapping=aes(x=osc_rate, y=rate_k - rate_ref, group=osc_rate)) +
+  geom_jitter(alpha=0.2, size=0.2, position = position_jitter(width = .05), color="dodgerblue3") +
+  geom_point(data=tmp2, mapping=aes(x=osc_rate - shift, y=M), size=0.6, color="dodgerblue3") +
+  geom_errorbar(data=tmp2, mapping=aes(x=osc_rate - shift, ymin=M - SD, ymax=M + SD), 
+                width=.15, size=0.2, color="dodgerblue3") +
+  geom_hline(yintercept=0, size=0.2) +
+  labs(title="d.", y=expression(Delta*" rate (Hz)"), x="Osc. rate (Hz)") +
+  # lims(y=c(-3, 3)) +
+  theme_classic() +
+  theme(plot.title = element_text(hjust = -.4, size=18, face="bold")) -> p6
+
+# -
+# Rate: burst v sustained
+tmp3 <- results21
+tmp3$osc_mode <- rep("Sustained", nrow(results21))
+
+tmp4 <- results30
+tmp4$osc_mode <- rep("Burst", nrow(results30))
+
+tmp5 <- rbind(tmp3, tmp4)
+tmp5 %>% 
+  ggplot(aes(x=osc_mode, y=rate_k - rate_ref, color=osc_mode)) +
+  geom_point(size=-1, aes(fill=osc_mode)) +
+  geom_boxplot(notch = TRUE, width=0.4,  outlier.size=0.05, outlier.alpha=0.5, show.legend=FALSE) +
+  labs(title="f.", y=expression(Delta*" rate (Hz)"), x="") +
+  theme_classic() +
+  geom_hline(yintercept=0, size=0.2) +
+  # lims(y=c(-3, 3)) +
+  scale_fill_manual(values=c("dodgerblue3", "black"), name="Oscillation") +
+  scale_color_manual(values=c("dodgerblue3", "black"), name="Oscillation") +
+  stat_compare_means(method="wilcox.test", label="p.signif", 
+                     label.x=1.3, size=3, show.legend=FALSE) +
+  guides(fill = guide_legend(override.aes = list(shape = 15, size = 7, alpha=0.8))) +
+  theme(
+    legend.position = c(0.1, 2),
+    legend.background = element_rect(colour ="black"),
+    legend.key.size = unit(.5, "cm"),
+    axis.text.x = element_text(angle = 70, hjust = 1),
+    plot.title = element_text(hjust = -1.2, size=18, face="bold")) -> p7
+
+# NEW
+
 # -
 layout_matrix <- rbind(
-  c(NA, 7, 7, 8, 8),
-  c(5, 1, 1, 2, 2), 
-  c(5, 1, 1, 2, 2), 
-  c(5, 1, 1, 2, 2), 
-  c(6, 3, 3, 4, 4),
-  c(6, 3, 3, 4, 4),
-  c(6, 3, 3, 4, 4)
+  c(12, 12, 12, 12, 12, 12, 12, 12),
+  c(NA, 8, 8, 9, 9, 9, 9, NA),
+  c(10, 1, 1, 2, 2, 5, 5, NA), 
+  c(10, 1, 1, 2, 2, 5, 5, NA), 
+  c(10, 1, 1, 2, 2, 5, 5, NA), 
+  c(10, 1, 1, 2, 2, 5, 5, 7), 
+  c(11, 3, 3, 4, 4, 6, 6, 7),
+  c(11, 3, 3, 4, 4, 6, 6, 7),
+  c(11, 3, 3, 4, 4, 6, 6, 7),
+  c(11, 3, 3, 4, 4, 6, 6, 7)
 )
 
-p7 <- textGrob("No homeostatsis")
-p8 <- textGrob("Homeostatsis")
-p5 <- textGrob("Synchrony")
-p6 <- textGrob("Excitability")
+p8 <- textGrob("No homeostatsis")
+p9 <- textGrob("Homeostatsis")
+p10 <- textGrob("Synchrony")
+p11 <- textGrob("Excitability")
+p12 <- textGrob("Inhibitory modulation")
+
+grid.arrange(p1, p2, p3, p4, p5, p6, p7, p8, p9, p10, p11, p12, layout_matrix=layout_matrix)
 
 # -
-png(file="fig4.png", bg="white", width=6, height=4.4, unit="in", res=300)
-grid.arrange(p1, p2, p3, p4, p5, p6, p7, p8, layout_matrix=layout_matrix)
+png(file="fig4.png", bg="white", width=9.0, height=4.5, unit="in", res=300)
+grid.arrange(p1, p2, p3, p4, p5, p6, p7, p8, p9, p10, p11, p12, layout_matrix=layout_matrix)
 dev.off()
-
-rm(p1, p2, p3, p4, p5, p6, p7, p8)
 ```
 
-# Figure 5. Variable Calcium targets and sustained E
+# Figure 4. Variable Calcium targets and sustained E
 
@@
 layout_matrix <- rbind(
+  c(6, 6, 6, 6), 
   c(3, 1, 1, 5),
   c(3, 1, 1, 5),
+  c(3, 1, 1, 5), 
+  c(3, 1, 1, 5), 
+  c(4, 2, 2, 5),
+  c(4, 2, 2, 5),
   c(4, 2, 2, 5),
@@
 p5 <- nullGrob()
+p6 <- textGrob("Excitatory modulation")
 
 # -
-png(file="fig5.png", bg="white", width=4.8, height=3.2, unit="in", res=300)
-grid.arrange(p1, p2, p3, p4, p5, layout_matrix=layout_matrix)
+png(file="fig5.png", bg="white", width=4.2, height=3.8, unit="in", res=300)
+grid.arrange(p1, p2, p3, p4, p5, p6,layout_matrix=layout_matrix)
 dev.off()

### 2018-04-30 resistingrhythm/analysis/paper_figures.Rmd
Update data for figs

@@
 # 16: Burst E, with H
-exp_code <- 16
-osc_codes <- c(100, 101, 102, 103, 104, 105, 110, 115, 120, 125, 130, 135, 140, 145, 150, 155, 160)
+exp_code <- 31
+osc_codes <- c(500, 501, 502, 503, 504, 505, 510, 515, 520, 525, 530, 535, 540, 545, 550, 555, 560)
 osc_rates <- c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0, 3.5, 4.0, 4.5, 5.0, 5.5, 6.0)
@@
 
-results16 <- NULL
+results31 <- NULL
 for(i in 1:length(osc_codes)){
@@
 
-    results16 <- rbind(results16, df)
+    results31 <- rbind(results31, df)
   }
@@
 
-results16 %>%
+results31 %>%
   filter(rate_k > 0) -> results15
@@
 # 30: Burst I, with H
-exp_code <- 30
-osc_codes <- c(100, 101, 102, 103, 104, 105, 110, 115, 120, 125, 130, 135, 140, 145, 150, 155, 160)
+exp_code <- 32
+osc_codes <- c(500, 501, 502, 503, 504, 505, 510, 515, 520, 525, 530, 535, 540, 545, 550, 555, 560)
 osc_rates <- c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0, 3.5, 4.0, 4.5, 5.0, 5.5, 6.0)
@@
 
-results30 <- NULL
+results32 <- NULL
 for(i in 1:length(osc_codes)){
@@
 
-    results30 <- rbind(results30, df)
+    results32 <- rbind(results32, df)
   }
@@
 
-results30 %>%
-  filter(rate_k > 0) -> results30
+results32 %>%
+  filter(rate_k > 0) -> results32
 
@@
 # Var
-results16 %>% 
+results31 %>% 
   filter(osc_rate < 0.1 | osc_rate > 0.4) -> tmp1
 
-results16 %>% 
+results31 %>% 
   filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
@@
 # Rate
-results16 %>% 
+results31 %>% 
   filter(osc_rate < 0.1 | osc_rate > 0.4) -> tmp1
 
-results16 %>% 
+results31 %>% 
   filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
@@
 
-tmp4 <- results16
-tmp4$osc_mode <- rep("Burst", nrow(results16))
+tmp4 <- results31
+tmp4$osc_mode <- rep("Burst", nrow(results31))
 
@@
 # Burst
-results16 %>% 
+results31 %>% 
   filter(osc_rate >= 0 & osc_rate <= 0.5) %>% 
@@
 # Var
-results30 %>% 
+results32 %>% 
   filter(osc_rate < 0.1 | osc_rate > 0.4) -> tmp1
 
-results30 %>% 
+results32 %>% 
   filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
@@
 # Rate
-results30 %>% 
+results32 %>% 
   filter(osc_rate < 0.1 | osc_rate > 0.4) -> tmp1
 
-results30 %>% 
+results32 %>% 
   filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
@@
 
-tmp4 <- results30
-tmp4$osc_mode <- rep("Burst", nrow(results30))
+tmp4 <- results32
+tmp4$osc_mode <- rep("Burst", nrow(results32))
 
@@
 
-# Figure 4. Variable Calcium targets and sustained E
+# Figure 4. Calcium targets
 
@@
 p5 <- nullGrob()
-p6 <- textGrob("Excitatory modulation")
+p6 <- textGrob("Calcium level")
 

### 2018-05-05 resistingrhythm/exp/homeostasis_experiments.py
Added exp37-40

@@ -201,6 +201,7 @@ def run(run_name,
         row = (k, V_ref, V_k, Ca_target, Ca_ref, Ca_obs_k, Ca_obs_ref, k_error,
                k_coord, abs_error, abs_var, mse_error, mse_var, rate_k,
                rate_ref)
+
         results.append(row)
 
     # ---------------------------------------------------

### 2018-05-05 resistingrhythm/ipynb/testing_HHH.py
Added HHH testing script; moving to #%% based jupyter

@@ -1,0 +1,163 @@
+#%%
+from bokeh.plotting import figure
+from bokeh.io import show, output_notebook
+from bokeh.layouts import column, row
+from bokeh.models import Range1d
+output_notebook()
+
+import numpy as np
+
+from resistingrhythm.util import poisson_impulse
+from resistingrhythm.util import poisson_oscillation
+from resistingrhythm.util import current_pulse
+from resistingrhythm.util import load_spikes
+
+from resistingrhythm.neurons import HHH
+
+#%%
+# Shared Params
+time = 1
+N = 1
+
+V_e = 0
+V_i = -80e-3
+
+tau_e = 5e-3
+tau_i = 10e-3
+
+tau_h = 4
+
+w = (5e-6, 50e-6)
+
+#%%
+# Load data
+osc_name = "/Users/type/Code/resistingrhythm/data/osc160.csv"
+stim_name = "/Users/type/Code/resistingrhythm/data/stim3.csv"
+
+ns_osc, ts_osc = load_spikes(osc_name)
+ns_in, ts_in = load_spikes(stim_name)
+
+#%%
+# Plot inputs/osc
+p = figure(plot_width=400, plot_height=200)
+p.circle(ts_osc, ns_osc, color="grey")
+p.xaxis.axis_label = 'Time (s)'
+p.yaxis.axis_label = 'N'
+p.x_range = Range1d(18, 20)
+p.xgrid.grid_line_color = None
+p.ygrid.grid_line_color = None
+show(p)
+
+#%%
+# External currents?
+# external_current = current_pulse(time, t_onset=2, t_offset=2.5, I=0.5e-6)
+
+#%%
+# Run HHH
+results = HHH(
+    time,
+    ns_in,
+    ts_in,
+    ns_osc,
+    ts_osc,
+    #     np.asarray([]), # stim
+    #     np.asarray([]),
+    #     np.asarray([]), # osc
+    #     np.asarray([]),
+    external_current=None,
+    N=N,
+    Ca_target=0.03,
+    tau_h=tau_h,
+    w_in=w,
+    tau_in=tau_e,
+    V_in=V_e,
+    bias_in=0.0e-9,
+    w_osc=w,
+    tau_osc=tau_e,
+    V_osc=V_e,
+    sigma=0,
+    homeostasis=True,
+    time_step=1e-5,
+    seed_value=42)
+
+#%%
+# Plot HHH
+p = figure(plot_width=400, plot_height=200)
[…]

### 2018-05-05 resistingrhythm/analysis/paper_figures.Rmd
Figure tweaks for PNAS submission

@@
   scale_color_manual(values=c("dodgerblue3", "black"), guide=FALSE) +
-  labs(title="b.", y="RMSE (s)", x="Osc. rate (Hz)") +
+  labs(title="b.", y="MSE (s)", x="Osc. rate (Hz)") +
   theme_classic() + 
@@
 ```
+```{r}
+print(wilcox.test(x=(tmp3$rate_k - tmp3$rate_ref), y=(tmp4$rate_k - tmp4$rate_ref)))
+```
 

### 2018-05-08 resistingrhythm/ipynb/testing_HHH.py
Improved cell markers in testing_HHH

@@ -1,4 +1,4 @@
-#%%
+#%% -------------------------------------------------------------------
 from bokeh.plotting import figure
 from bokeh.io import show, output_notebook
 from bokeh.layouts import column, row
@@ -14,7 +14,7 @@ from resistingrhythm.util import load_spikes
 
 from resistingrhythm.neurons import HHH
 
-#%%
+#%% -------------------------------------------------------------------
 # Shared Params
 time = 1
 N = 1
@@ -29,15 +29,14 @@ tau_h = 4
 
 w = (5e-6, 50e-6)
 
-#%%
+#%% -------------------------------------------------------------------
 # Load data
 osc_name = "/Users/type/Code/resistingrhythm/data/osc160.csv"
-stim_name = "/Users/type/Code/resistingrhythm/data/stim3.csv"
+stim_name = "/Users/type/Code/resistingrhythm/data/stim0.csv"
 
 ns_osc, ts_osc = load_spikes(osc_name)
 ns_in, ts_in = load_spikes(stim_name)
 
-#%%
 # Plot inputs/osc
 p = figure(plot_width=400, plot_height=200)
 p.circle(ts_osc, ns_osc, color="grey")
@@ -52,18 +51,18 @@ show(p)
 # External currents?
 # external_current = current_pulse(time, t_onset=2, t_offset=2.5, I=0.5e-6)
 
-#%%
+#%% -------------------------------------------------------------------
 # Run HHH
 results = HHH(
     time,
-    ns_in,
-    ts_in,
-    ns_osc,
-    ts_osc,
-    #     np.asarray([]), # stim
-    #     np.asarray([]),
-    #     np.asarray([]), # osc
-    #     np.asarray([]),
+    # ns_in,
+    # ts_in,
+    # ns_osc,
+    # ts_osc,
+    np.asarray([]),  # stim
+    np.asarray([]),
+    np.asarray([]),  # osc
+    np.asarray([]),
     external_current=None,
     N=N,
     Ca_target=0.03,
@@ -75,14 +74,14 @@ results = HHH(
     w_osc=w,
     tau_osc=tau_e,
     V_osc=V_e,
-    sigma=0,
-    homeostasis=True,
+    noise_rate=1,
+    homeostasis=False,
     time_step=1e-5,
     seed_value=42)
 
 #%%
 # Plot HHH
-p = figure(plot_width=400, plot_height=200)
+p = figure(plot_width=600, plot_height=300)
 p.circle(results['ts'], results['ns'], color="black")
[…]

### 2018-06-22 resistingrhythm/analysis/paper_figures_v2.Rmd
Adde paper fig v2

--- 2018-05-05 resistingrhythm/analysis/paper_figures.Rmd
@@
 # 16: Burst E, with H
-exp_code <- 31
-osc_codes <- c(500, 501, 502, 503, 504, 505, 510, 515, 520, 525, 530, 535, 540, 545, 550, 555, 560)
-osc_rates <- c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0, 3.5, 4.0, 4.5, 5.0, 5.5, 6.0)
-stim_codes <- c(0, 1)
+# exp_code <- 31
+# osc_codes <- c(500, 501, 502, 503, 504, 505, 510, 515, 520, 525, 530, 535, 540, 545, 550, 555, 560)
+# osc_rates <- c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0, 3.5, 4.0, 4.5, 5.0, 5.5, 6.0)
+# stim_codes <- c(0, 1)
+
+exp_code <- "102e"
+osc_codes <- c(500, 501, 502, 503, 504, 505, 510, 515, 520, 525, 530)
+osc_rates <- c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0)
+stim_codes <- c(3, 4)
 
@@
 # 15: Sustained E, with H
-exp_code <- 15
-osc_codes <- c(100, 101, 102, 103, 104, 105, 110, 115, 120, 125, 130, 135, 140, 145, 150, 155, 160)
-osc_rates <- c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0, 3.5, 4.0, 4.5, 5.0, 5.5, 6.0)
-stim_codes <- c(0, 1)
+# exp_code <- 15
+# osc_codes <- c(100, 101, 102, 103, 104, 105, 110, 115, 120, 125, 130, 135, 140, 145, 150, 155, 160)
+# osc_rates <- c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0, 3.5, 4.0, 4.5, 5.0, 5.5, 6.0)
+# stim_codes <- c(0, 1)
 
+exp_code <- "104e"
+osc_codes <- c(100, 101, 102, 103, 104, 105, 110, 115, 120, 125, 130)
+osc_rates <- c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0)
+stim_codes <- c(3, 4)
 results15 <- NULL
@@
 # 22: Sustained E, with NO H
-exp_code <- 22
-osc_codes <- c(100, 101, 102, 103, 104, 105, 110, 115, 120, 125, 130, 135, 140, 145, 150, 155, 160)
-osc_rates <- c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0, 3.5, 4.0, 4.5, 5.0, 5.5, 6.0)
-stim_codes <- c(0, 1)
+# exp_code <- 22
+# osc_codes <- c(100, 101, 102, 103, 104, 105, 110, 115, 120, 125, 130, 135, 140, 145, 150, 155, 160)
+# osc_rates <- c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0, 3.5, 4.0, 4.5, 5.0, 5.5, 6.0)
+# stim_codes <- c(0, 1)
+
+exp_code <- "105e"
+osc_codes <- c(100, 101, 102, 103, 104, 105, 110, 115, 120, 125, 130)
+osc_rates <- c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0)
+stim_codes <- c(3, 4)
 
@@
 # 21: Sustained I, with H
-exp_code <- 21
-osc_codes <- c(100, 101, 102, 103, 104, 105, 110, 115, 120, 125, 130, 135, 140, 145, 150, 155, 160)
-osc_rates <- c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0, 3.5, 4.0, 4.5, 5.0, 5.5, 6.0)
-stim_codes <- c(0, 1)
+# exp_code <- 21
+# osc_codes <- c(100, 101, 102, 103, 104, 105, 110, 115, 120, 125, 130, 135, 140, 145, 150, 155, 160)
+# osc_rates <- c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0, 3.5, 4.0, 4.5, 5.0, 5.5, 6.0)
+# stim_codes <- c(0, 1)
+
+exp_code <- "104i"
+osc_codes <- c(100, 101, 102, 103, 104, 105, 110, 115, 120, 125, 130)
+osc_rates <- c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0)
+stim_codes <- c(3, 4)
 
@@
 # 23: Sustained I, with NO H
-exp_code <- 23
-osc_codes <- c(100, 101, 102, 103, 104, 105, 110, 115, 120, 125, 130, 135, 140, 145, 150, 155, 160)
-osc_rates <- c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0, 3.5, 4.0, 4.5, 5.0, 5.5, 6.0)
-stim_codes <- c(0, 1)
+# exp_code <- 23
+# osc_codes <- c(100, 101, 102, 103, 104, 105, 110, 115, 120, 125, 130, 135, 140, 145, 150, 155, 160)
+# osc_rates <- c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0, 3.5, 4.0, 4.5, 5.0, 5.5, 6.0)
+# stim_codes <- c(0, 1)
+
+exp_code <- "105i"
+osc_codes <- c(100, 101, 102, 103, 104, 105, 110, 115, 120, 125, 130)
+osc_rates <- c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0)
+stim_codes <- c(3, 4)
 
@@
 # 30: Burst I, with H
-exp_code <- 32
-osc_codes <- c(500, 501, 502, 503, 504, 505, 510, 515, 520, 525, 530, 535, 540, 545, 550, 555, 560)
-osc_rates <- c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0, 3.5, 4.0, 4.5, 5.0, 5.5, 6.0)
-stim_codes <- c(0, 1)
+# exp_code <- 32
+# osc_codes <- c(500, 501, 502, 503, 504, 505, 510, 515, 520, 525, 530, 535, 540, 545, 550, 555, 560)
+# osc_rates <- c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0, 3.5, 4.0, 4.5, 5.0, 5.5, 6.0)
+# stim_codes <- c(0, 1)
+
+exp_code <- "102i"
+osc_codes <- c(500, 501, 502, 503, 504, 505, 510, 515, 520, 525, 530)
+osc_rates <- c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0)
+stim_codes <- c(3, 4)
 
@@
 # -
-png(file="fig2.png", bg="white", width=9.0, height=4.5, unit="in", res=300)
+png(file="fig2_v2.png", bg="white", width=9.0, height=4.5, unit="in", res=300)
 grid.arrange(p1, p2, p3, p4, p5, p6, p7, p8, p9, p10, p11, p12, layout_matrix=layout_matrix)
@@
 # -
-png(file="fig3.png", bg="white", width=4.4, height=3.8, unit="in", res=300)
+png(file="fig3_v2.png", bg="white", width=4.4, height=3.8, unit="in", res=300)
 grid.arrange(p1, p2, p3, p4, p5, p6, layout_matrix=layout_matrix)
@@
 # -
-png(file="fig4.png", bg="white", width=9.0, height=4.5, unit="in", res=300)
+png(file="fig4_v2.png", bg="white", width=9.0, height=4.5, unit="in", res=300)
 grid.arrange(p1, p2, p3, p4, p5, p6, p7, p8, p9, p10, p11, p12, layout_matrix=layout_matrix)
@@
 # -
-png(file="fig5.png", bg="white", width=4.2, height=3.8, unit="in", res=300)
+png(file="fig5_v2.png", bg="white", width=4.2, height=3.8, unit="in", res=300)
 grid.arrange(p1, p2, p3, p4, p5, p6,layout_matrix=layout_matrix)

### 2018-10-29 resistingrhythm/analysis/burst_analysis.Rmd
Update misc analysis notebooks

@@
 
-exp_code <- 16
-osc_codes <- c(100, 101, 102, 103, 104, 105, 110, 115, 120, 125, 130, 135, 140, 145, 150, 155, 160)
-osc_rates <- c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0, 3.5, 4.0, 4.5, 5.0, 5.5, 6.0)
-stim_codes <- c(0, 1)
+# exp_code <- 16
+# osc_codes <- c(100, 101, 102, 103, 104, 105, 110, 115, 120, 125, 130, 135, 140, 145, 150, 155, 160)
+# osc_rates <- c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0, 3.5, 4.0, 4.5, 5.0, 5.5, 6.0)
+# stim_codes <- c(0, 1)
+
+# exp_code <- 32
+# osc_codes <- c(500, 501, 502, 503, 504, 505, 510, 515, 520, 525, 530, 535, 540, 545, 550, 555, 560)
+# osc_rates <- c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0, 3.5, 4.0, 4.5, 5.0, 5.5, 6.0)
+# stim_codes <- c(0, 1)
+
+exp_code <- "103e"
+osc_codes <- c(500, 501, 502, 503, 504, 505, 510, 515, 520, 525, 530)
+osc_rates <- c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0)
+stim_codes <- c(3, 4)
 

### 2018-10-29 resistingrhythm/analysis/paper_figures_v2.Rmd
Update misc

@@
 stim_codes <- c(3, 4)
+
 results15 <- NULL
+for(i in 1:length(osc_codes)){
+  for(s_c in stim_codes){
+    o_c <- osc_codes[i]
+    o_r <- osc_rates[i]
+
+    # Load the csv
+    df <- read_csv(paste(data_path, 
+                         "exp", as.character(exp_code), 
+                         "_stim", as.character(s_c), 
+                         "_osc", as.character(o_c),
+                         ".csv", sep=""))
+
+    # Add metadata
+    df$osc_code <- rep(o_c, nrow(df))
+    df$osc_rate <- rep(o_r, nrow(df))
+    df$stim_code <- rep(s_c, nrow(df))
+
+    results15 <- rbind(results15, df)
+  }
+}
+
+# Add higher
+exp_code <- "106e"
+osc_codes <- c(135, 140, 145, 150, 155, 160, 165, 170, 175, 180, 185, 190)
+osc_rates <- c(3.5, 4.0, 4.5, 5.0, 5.5, 6.0, 6.5, 7.0, 7.5, 8.0, 8.5, 9.0)
+stim_codes <- c(3, 4)
+
 for(i in 1:length(osc_codes)){
@@
 stim_codes <- c(3, 4)
+results22 <- NULL
+for(i in 1:length(osc_codes)){
+  for(s_c in stim_codes){
+    o_c <- osc_codes[i]
+    o_r <- osc_rates[i]
 
-results22 <- NULL
+    # Load the csv
+    df <- read_csv(paste(data_path, 
+                         "exp", as.character(exp_code), 
+                         "_stim", as.character(s_c), 
+                         "_osc", as.character(o_c),
+                         ".csv", sep=""))
+
+    # Add metadata
+    df$osc_code <- rep(o_c, nrow(df))
+    df$osc_rate <- rep(o_r, nrow(df))
+    df$stim_code <- rep(s_c, nrow(df))
+
+    results22 <- rbind(results22, df)
+  }
+}
+
+exp_code <- "107e"
+osc_codes <- c(135, 140, 145, 150, 155, 160, 165, 170, 175, 180, 185, 190)
+osc_rates <- c(3.5, 4.0, 4.5, 5.0, 5.5, 6.0, 6.5, 7.0, 7.5, 8.0, 8.5, 9.0)
+stim_codes <- c(3, 4)
 for(i in 1:length(osc_codes)){
@@
   labs(title="a.", y="Variance (s)", x="Osc. rate (Hz)") +
-  lims(y=c(0, .15)) +
+  # lims(y=c(0, .15)) +
   theme_classic() +
@@
   labs(title="b.", y="Variance (s)", x="Osc. rate (Hz)") +
-  lims(y=c(0, .01)) +
+  # lims(y=c(0, .01)) +
   theme_classic() +
@@
   labs(title="d.", y=expression(Delta*" rate (Hz)"), x="Osc. rate (Hz)") +
-  lims(y=c(0, 70)) +
+  # lims(y=c(0, 70)) +
   geom_hline(yintercept=0, size=0.2) +
@@
   labs(title="e.", y=expression(Delta*" rate (Hz)"), x="Osc. rate (Hz)") +
-  lims(y=c(-4, 4)) +
+  # lims(y=c(-4, 4)) +
   geom_hline(yintercept=0, size=0.2) +
@@
   theme_classic() + 
-  lims(y=c(0, .01)) +
+  # lims(y=c(0, .01)) +
   theme(plot.title = element_text(hjust = -.6, size=18, face="bold")) -> p5
@@
   labs(title="d.", y=expression(Delta*" rate (Hz)"), x="Osc. rate (Hz)") +
-  lims(y=c(-3, 3)) +
+  # lims(y=c(-3, 3)) +
   theme_classic() +
@@
   geom_hline(yintercept=0, size=0.2) +
-  lims(y=c(-3, 3)) +
+  # lims(y=c(-3, 3)) +
   scale_fill_manual(values=c("dodgerblue3", "black"), name="Oscillation") +
@@
   theme_classic() + 
-  lims(y=c(0, 0.004)) +
+  # lims(y=c(0, 0.004)) +
   theme(
@@
 
+grid.arrange(p1, p2, p3, p4, p5, p6, layout_matrix=layout_matrix)
+
 # -

### 2018-10-29 resistingrhythm/exp/examples.py

@@ -1,0 +1,24 @@
+#%%
+from bokeh.plotting import figure
+from bokeh.io import show, output_notebook
+from bokeh.layouts import column, row
+from bokeh.models import Range1d
+output_notebook()
+
+from resistingrhythm.util import poisson_impulse
+
+#%%
+time = 1
+ns, ts = poisson_impulse(time)
+
+p = figure(plot_width=500, plot_height=300)
+p.circle(ts, ns, color="grey")
+p.xaxis.axis_label = 'Time (s)'
+p.yaxis.axis_label = 'N'
+p.x_range = Range1d(0, time)
+p.xgrid.grid_line_color = None
+p.ygrid.grid_line_color = None
+show(p)
+
+#%%
+print(1)

### 2018-10-29 resistingrhythm/util.py
min_rate is not additive for oscillations

@@ -253,7 +253,7 @@ def poisson_oscillation(t=1,
     times = fsutil.create_times(t, dt=dt)
 
     # Create rate wave, over times
-    osc = rate / 2 * (1 + np.sin((times * f * 2 * np.pi) + phi))
+    osc = (rate / 2 * (1 + np.sin((times * f * 2 * np.pi) + phi))) + min_rate
 
     # Truncate it to a n_cycle burst, starting at t_onset
     if np.isclose(f, 0.0):

### 2018-10-30 resistingrhythm/exp/homeostasis_experiments.py
Decrease kappa dt

@@ -175,8 +175,8 @@ def run(run_name,
         ns_k, ts_k = filter_spikes(results_k['ns'], results_k['ts'], a_window)
 
         # Analysis of error and network corr, in a_window
-        k_error = kappa(ns_ref, ts_ref, ns_k, ts_k, a_window, dt=time_step)
-        k_coord = kappa(ns_k, ts_k, ns_k, ts_k, a_window, dt=time_step)
+        k_error = kappa(ns_ref, ts_ref, ns_k, ts_k, a_window, dt=1e-3)
+        k_coord = kappa(ns_k, ts_k, ns_k, ts_k, a_window, dt=1e-3)
 
         # l1 scores
         abs_var, abs_error = l1_by_n(N, ns_ref, ts_ref, ns_k, ts_k)

### 2018-10-30 resistingrhythm/analysis/paper_figures_v3.Rmd
add figures v3 (exps200)

--- 2018-05-05 resistingrhythm/analysis/paper_figures.Rmd
@@
 # 16: Burst E, with H
-exp_code <- 31
-osc_codes <- c(500, 501, 502, 503, 504, 505, 510, 515, 520, 525, 530, 535, 540, 545, 550, 555, 560)
+exp_code <- 204
+osc_codes <- c(100, 101, 102, 103, 104, 105, 110, 115, 120, 125, 130, 135, 140, 145, 150, 155, 160)
 osc_rates <- c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0, 3.5, 4.0, 4.5, 5.0, 5.5, 6.0)
-stim_codes <- c(0, 1)
+stim_codes <- c(3, 4) # 4
 
-results31 <- NULL
+results204 <- NULL
 for(i in 1:length(osc_codes)){
@@
 
-    results31 <- rbind(results31, df)
+    results204 <- rbind(results204, df)
   }
@@
 
-results31 %>%
-  filter(rate_k > 0) -> results15
+results204 %>%
+  filter(rate_k > 0) -> results204
 
@@
 # 15: Sustained E, with H
-exp_code <- 15
+exp_code <- 201
 osc_codes <- c(100, 101, 102, 103, 104, 105, 110, 115, 120, 125, 130, 135, 140, 145, 150, 155, 160)
 osc_rates <- c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0, 3.5, 4.0, 4.5, 5.0, 5.5, 6.0)
-stim_codes <- c(0, 1)
+stim_codes <- c(3)#, 4)
 
-results15 <- NULL
+results201 <- NULL
 for(i in 1:length(osc_codes)){
@@
 
-    results15 <- rbind(results15, df)
+    results201 <- rbind(results201, df)
   }
@@
 
-results15 %>%
-  filter(rate_k > 0) -> results15
+results201 %>%
+  filter(rate_k > 0) -> results201
 
@@
 # 22: Sustained E, with NO H
-exp_code <- 22
+exp_code <- 200
 osc_codes <- c(100, 101, 102, 103, 104, 105, 110, 115, 120, 125, 130, 135, 140, 145, 150, 155, 160)
 osc_rates <- c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0, 3.5, 4.0, 4.5, 5.0, 5.5, 6.0)
-stim_codes <- c(0, 1)
+stim_codes <- c(3) #, 3)
 
-results22 <- NULL
+results200 <- NULL
 for(i in 1:length(osc_codes)){
@@
 
-    results22 <- rbind(results22, df)
+    results200 <- rbind(results200, df)
   }
@@
 
-results22 %>%
-  filter(rate_k > 0) -> results22
+results200 %>%
+  filter(rate_k > 0) -> results200
 
@@
 
-```{r, fig.width=4.5, fig.height=2.25}
+```{r, fig.width=5, fig.height=2.25}
 shift <- -0.15
@@
 # No H, E
-results22 %>% 
+results200 %>% 
   filter(osc_rate < 0.1 | osc_rate > 0.4) -> tmp1
 
-results22 %>% 
+results200 %>% 
   filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
@@
 # With H, E
-results15 %>% 
+results201 %>% 
   filter(osc_rate < 0.1 | osc_rate > 0.4) -> tmp1
 
-results15 %>% 
+results201 %>% 
   filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
@@
 # Rate, no H, E
-results22 %>% 
+results200 %>% 
   filter(osc_rate < 0.1 | osc_rate > 0.4) -> tmp1
 
-results22 %>% 
+results200 %>% 
   filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
@@
 # Rate, with H, E
-results15 %>% 
+results201 %>% 
   filter(osc_rate < 0.1 | osc_rate > 0.4) -> tmp1
 
-results15 %>% 
+results201 %>% 
   filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
@@
 # Var
-results31 %>% 
+results204 %>% 
   filter(osc_rate < 0.1 | osc_rate > 0.4) -> tmp1
 
-results31 %>% 
+results204 %>% 
   filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
@@
 # Rate
-results31 %>% 
+results204 %>% 
   filter(osc_rate < 0.1 | osc_rate > 0.4) -> tmp1
 
-results31 %>% 
+results204 %>% 
   filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
@@
 # Rate: burst v sustained
-tmp3 <- results15
-tmp3$osc_mode <- rep("Sustained", nrow(results15))
+tmp3 <- results201
+tmp3$osc_mode <- rep("Sustained", nrow(results201))
 
-tmp4 <- results31
-tmp4$osc_mode <- rep("Burst", nrow(results31))
+tmp4 <- results204
+tmp4$osc_mode <- rep("Burst", nrow(results204))
 
@@
 print(wilcox.test(x=(tmp3$rate_k - tmp3$rate_ref), y=(tmp4$rate_k - tmp4$rate_ref)))
-```
-
-# Figure 3. Weak E oscillations, variance, and error.
-
-```{r, fig.width=2.4, fig.height=1.7}
-# --------------------------------------------------------
-# Burst
-results31 %>% 
-  filter(osc_rate >= 0 & osc_rate <= 0.5) %>% 
-  group_by(osc_rate) %>% 
-  summarise(M_var=mean(mse_var), 
-         SD_var=sd(mse_var),
-         M_error=mean(mse_error)/1e3,
-         SD_error=sd(mse_error)/1e3) -> tmp1
-
-# Sustained
-results15 %>% 
-  filter(osc_rate >= 0 & osc_rate <= 0.5) %>% 
-  group_by(osc_rate) %>% 
-  summarise(M_var=mean(mse_var), 
-         SD_var=sd(mse_var),
-         M_error=mean(mse_error)/1e3,
-         SD_error=sd(mse_error)/1e3) -> tmp2
-
-tmp1$osc_mode <- rep("Burst", nrow(tmp1))
-tmp2$osc_mode <- rep("Sustained", nrow(tmp2))
-tmp3 <- rbind(tmp1, tmp2)
-
-tmp3 %>% 
-  ggplot(aes(x=osc_rate, y=M_var, color=osc_mode)) +
-  geom_line(size=0.8) +
-  geom_point(size=1.5) +
-  geom_errorbar(aes(x=osc_rate, ymin=M_var - SD_var, ymax=M_var + SD_var), 
-                alpha=0.5, width=.02, size=0.4) +
-  scale_color_manual(values=c("dodgerblue3", "black"), name="Oscillation") +
-  labs(title="a.", y="Variance (s)", x="Osc. rate (Hz)") +
-  theme_classic() + 
-  lims(y=c(0, 0.004)) +
-  theme(
-    legend.position = c(1.4, -0.3),
-    legend.background = element_rect(colour ="black"),
-    legend.key.size = unit(.5, "cm"),
-    plot.title = element_text(hjust = -.45, size=18, face="bold")) -> p1
-
-tmp3 %>% 
-  ggplot(aes(x=osc_rate, y=M_error, color=osc_mode)) +
-  geom_line(size=0.8) +
-  geom_point(size=1.5) +
-  geom_errorbar(aes(x=osc_rate, ymin=M_error - SD_error, ymax=M_error + SD_error), 
-                alpha=0.5, width=.02, size=0.4) +
-  scale_color_manual(values=c("dodgerblue3", "black"), guide=FALSE) +
-  labs(title="b.", y="MSE (s)", x="Osc. rate (Hz)") +
-  theme_classic() + 
-  theme(plot.title = element_text(hjust = -.5, size=18, face="bold")) -> p2
-
-# p3 <- textGrob("Homeostatsis")
-p3 <- textGrob("Synchrony")
-p4 <- textGrob("Error")
-
-layout_matrix <- rbind(
-  c(6, 6, 6, 6), 
-  c(3, 1, 1, 5), 
-  c(3, 1, 1, 5),
-  c(3, 1, 1, 5),
-  c(3, 1, 1, 5), 
-  c(4, 2, 2, 5),
-  c(4, 2, 2, 5),
-  c(4, 2, 2, 5),
-  c(4, 2, 2, 5))
-
-p5 <- nullGrob()
-p6 <- textGrob("Weak excitatory modulation")
-
-# -
-png(file="fig3.png", bg="white", width=4.4, height=3.8, unit="in", res=300)
-grid.arrange(p1, p2, p3, p4, p5, p6, layout_matrix=layout_matrix)
-dev.off()
-
-rm(p1, p2, p3, p4, tmp1, tmp2, tmp3)
 ```

### 2018-10-31 resistingrhythm/exp/homeostasis_experiments.py
Update stats output
- Now includes ref var, mad, kappa

@@ -177,12 +177,13 @@ def run(run_name,
         # Analysis of error and network corr, in a_window
         k_error = kappa(ns_ref, ts_ref, ns_k, ts_k, a_window, dt=1e-3)
         k_coord = kappa(ns_k, ts_k, ns_k, ts_k, a_window, dt=1e-3)
+        k_ref = kappa(ns_ref, ts_ref, ns_ref, ts_ref, a_window, dt=1e-3)
 
         # l1 scores
-        abs_var, abs_error = l1_by_n(N, ns_ref, ts_ref, ns_k, ts_k)
+        abs_var, abs_ref, abs_error = l1_by_n(N, ns_ref, ts_ref, ns_k, ts_k)
 
         # l2 scores
-        mse_var, mse_error = l2_by_n(N, ns_ref, ts_ref, ns_k, ts_k)
+        mse_var, mse_ref, mse_error = l2_by_n(N, ns_ref, ts_ref, ns_k, ts_k)
 
         # Get rate
         rate_k = float(ns_k.size) / float(N) / (t - burn_t)
@@ -200,7 +201,9 @@ def run(run_name,
         # save row
         row = (k, V_ref, V_k, Ca_target, Ca_ref, Ca_obs_k, Ca_obs_ref, k_error,
                k_coord, abs_error, abs_var, mse_error, mse_var, rate_k,
-               rate_ref)
+               rate_ref, abs_ref, mse_ref, k_ref)
+
+        print(row)
 
         results.append(row)
 
@@ -211,7 +214,8 @@ def run(run_name,
     head = [
         "k", "V_ref", "V_k", "Ca_target", "Ca_ref", "Ca_obs_target",
         "Ca_obs_ref", "kappa_error", "kappa_coord", "abs_error", "abs_var",
-        "mse_error", "mse_var", "rate_k", "rate_ref"
+        "mse_error", "mse_var", "rate_k", "rate_ref", "abs_ref", "mse_ref",
+        "k_ref"
     ]
     with open("{}.csv".format(run_name), "w") as fi:
         writer = csv.writer(fi, delimiter=",")

### 2018-10-31 resistingrhythm/util.py

@@ -23,6 +23,7 @@ def select_n(n, ns, ts):
 
 def l1_by_n(N, ns_ref, ts_ref, ns_n, ts_n):
     v_i = []
+    v_r = []
     e_i = []
     for i in range(N):
         ns_ref_i, ts_ref_i = select_n(i, ns_ref, ts_ref)
@@ -35,24 +36,31 @@ def l1_by_n(N, ns_ref, ts_ref, ns_n, ts_n):
             var = 0
         v_i.append(var)
 
+        if ts_ref_i.size > 0:
+            var = mad(ts_ref_i) / ts_ref_i.size
+        else:
+            var = 0
+        v_r.append(var)
+
         # Error
         e_i.append(mae(ts_i, ts_ref_i))
 
     # Expectation of all neurons.
     var = np.mean(v_i)
+    var_ref = np.mean(v_r)
     error = np.mean(e_i)
 
-    return var, error
+    return var, var_ref, error
 
 
 def l2_by_n(N, ns_ref, ts_ref, ns_n, ts_n):
     v_i = []
+    v_r = []
     e_i = []
     for i in range(N):
         ns_ref_i, ts_ref_i = select_n(i, ns_ref, ts_ref)
         ns_i, ts_i = select_n(i, ns_n, ts_n)
 
-        # Variance
         # Variance
         if ts_i.size > 0:
             var = np.std(ts_i)
@@ -60,14 +68,21 @@ def l2_by_n(N, ns_ref, ts_ref, ns_n, ts_n):
             var = 0
         v_i.append(var)
 
+        if ts_ref_i.size > 0:
+            var = np.std(ts_ref_i)
+        else:
+            var = 0
+        v_r.append(var)
+
         # Error
         e_i.append(mse(ts_i, ts_ref_i))
 
     # Expectation of all neurons.
     var = np.mean(v_i)
+    var_ref = np.mean(v_r)
     error = np.mean(e_i)
 
-    return var, error
+    return var, var_ref, error
 
 
 def mad(x, M=None, axis=None):

### 2018-10-31 resistingrhythm/exp/homeostasis_experiments.py
Added row printing w/ --verbose

@@ -203,7 +203,9 @@ def run(run_name,
                k_coord, abs_error, abs_var, mse_error, mse_var, rate_k,
                rate_ref, abs_ref, mse_ref, k_ref)
 
-        print(row)
+        if verbose:
+            print(">>> Analysis results:")
+            print(row)
 
         results.append(row)
 

### 2018-10-31 resistingrhythm/analysis/paper_figures_v3.Rmd
WIP

@@
 # 21: Sustained I, with H
-exp_code <- 21
+exp_code <- 203
 osc_codes <- c(100, 101, 102, 103, 104, 105, 110, 115, 120, 125, 130, 135, 140, 145, 150, 155, 160)
 osc_rates <- c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0, 3.5, 4.0, 4.5, 5.0, 5.5, 6.0)
-stim_codes <- c(0, 1)
+stim_codes <- c(3, 4)
 
-results21 <- NULL
+results203 <- NULL
 for(i in 1:length(osc_codes)){
@@
 
-    results21 <- rbind(results21, df)
+    results203 <- rbind(results203, df)
   }
@@
 
-results21 %>%
-  filter(rate_k > 0) -> results21
+results203 %>%
+  filter(rate_k > 0) -> results203
 
@@
 # 23: Sustained I, with NO H
-exp_code <- 23
+exp_code <- 202
 osc_codes <- c(100, 101, 102, 103, 104, 105, 110, 115, 120, 125, 130, 135, 140, 145, 150, 155, 160)
 osc_rates <- c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0, 3.5, 4.0, 4.5, 5.0, 5.5, 6.0)
-stim_codes <- c(0, 1)
+stim_codes <- c(3)#, 4)
 
-results23 <- NULL
+results202 <- NULL
 for(i in 1:length(osc_codes)){
@@
 
-    results23 <- rbind(results23, df)
+    results202 <- rbind(results202, df)
   }
@@
 
-results23 %>%
-  filter(rate_k > 0) -> results23
+results202 %>%
+  filter(rate_k > 0) -> results202
 
@@
 # 30: Burst I, with H
-exp_code <- 32
-osc_codes <- c(500, 501, 502, 503, 504, 505, 510, 515, 520, 525, 530, 535, 540, 545, 550, 555, 560)
+exp_code <- 207
+osc_codes <- c(100, 101, 102, 103, 104, 105, 110, 115, 120, 125, 130, 135, 140, 145, 150, 155, 160)
 osc_rates <- c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0, 3.5, 4.0, 4.5, 5.0, 5.5, 6.0)
-stim_codes <- c(0, 1)
+stim_codes <- c(3, 4)
 
-results32 <- NULL
+results207 <- NULL
 for(i in 1:length(osc_codes)){
@@
 
-    results32 <- rbind(results32, df)
+    results207 <- rbind(results207, df)
   }
@@
 
-results32 %>%
-  filter(rate_k > 0) -> results32
+results207 %>%
+  filter(rate_k > 0) -> results207
 
@@
   group_by(osc_rate) %>% 
-  mutate(M=mean(mse_var), SD=sd(mse_var)) -> tmp2
+  mutate(M=mean(mse_error), SD=sd(mse_error)) -> tmp2
 
-ggplot(data=tmp1, mapping=aes(x=osc_rate, y=mse_var, group=osc_rate)) +
+ggplot(data=tmp1, mapping=aes(x=osc_rate, y=mse_error, group=osc_rate)) +
   geom_jitter(alpha=0.2, size=0.2, position = position_jitter(width = .05)) +
@@
   labs(title="a.", y="Variance (s)", x="Osc. rate (Hz)") +
-  # lims(y=c(0, .15)) +
+  # # lims(y=c(0, .15)) +
   theme_classic() +
@@
   group_by(osc_rate) %>% 
-  mutate(M=mean(mse_var), SD=sd(mse_var)) -> tmp2
+  mutate(M=mean(mse_error), SD=sd(mse_error)) -> tmp2
 
-ggplot(data=tmp1, mapping=aes(x=osc_rate, y=mse_var, group=osc_rate)) +
+ggplot(data=tmp1, mapping=aes(x=osc_rate, y=mse_error, group=osc_rate)) +
   geom_jitter(alpha=0.2, size=0.2, position = position_jitter(width = .05), color="dodgerblue3") +
@@
 # No H, E
-results23 %>% 
+results202 %>% 
   filter(osc_rate < 0.1 | osc_rate > 0.4) -> tmp1
 
-results23 %>% 
+results202 %>% 
   filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
   group_by(osc_rate) %>% 
-  mutate(M=mean(mse_var), SD=sd(mse_var)) -> tmp2
+  mutate(M=mean(mse_error), SD=sd(mse_error)) -> tmp2
 
-ggplot(data=tmp1, mapping=aes(x=osc_rate, y=mse_var, group=osc_rate)) +
+ggplot(data=tmp1, mapping=aes(x=osc_rate, y=mse_error, group=osc_rate)) +
   geom_jitter(alpha=0.2, size=0.2, position = position_jitter(width = .05)) +
@@
 # With H, E
-results21 %>% 
+results203 %>% 
   filter(osc_rate < 0.1 | osc_rate > 0.4) -> tmp1
 
-results21 %>% 
+results203 %>% 
   filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
   group_by(osc_rate) %>% 
-  mutate(M=mean(mse_var), SD=sd(mse_var)) -> tmp2
+  mutate(M=mean(mse_error), SD=sd(mse_error)) -> tmp2
 
-ggplot(data=tmp1, mapping=aes(x=osc_rate, y=mse_var, group=osc_rate)) +
+ggplot(data=tmp1, mapping=aes(x=osc_rate, y=mse_error, group=osc_rate)) +
   geom_jitter(alpha=0.2, size=0.2, position = position_jitter(width = .05)) +
@@
   labs(title="b.", y="Variance (s)", x="Osc. rate (Hz)") +
-  # lims(y=c(0, .01)) +
+  # lims(y=c(0, .15)) +
   theme_classic() +
@@
 # Rate, no H, E
-results23 %>% 
+results202 %>% 
   filter(osc_rate < 0.1 | osc_rate > 0.4) -> tmp1
 
-results23 %>% 
+results202 %>% 
   filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
@@
 # Rate, with H, E
-results21 %>% 
+results203 %>% 
   filter(osc_rate < 0.1 | osc_rate > 0.4) -> tmp1
 
-results21 %>% 
+results203 %>% 
   filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
@@
 # Var
-results32 %>% 
+results207 %>% 
   filter(osc_rate < 0.1 | osc_rate > 0.4) -> tmp1
 
-results32 %>% 
+results207 %>% 
   filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
   group_by(osc_rate) %>% 
-  mutate(M=mean(mse_var), SD=sd(mse_var)) -> tmp2
+  mutate(M=mean(mse_error), SD=sd(mse_error)) -> tmp2
 
-ggplot(data=tmp1, mapping=aes(x=osc_rate, y=mse_var, group=osc_rate)) +
+ggplot(data=tmp1, mapping=aes(x=osc_rate, y=mse_error, group=osc_rate)) +
   geom_jitter(alpha=0.2, size=0.2, position = position_jitter(width = .05), color="dodgerblue3") +
@@
   theme_classic() + 
-  # lims(y=c(0, .01)) +
+  # lims(y=c(0, .15)) +
   theme(plot.title = element_text(hjust = -.6, size=18, face="bold")) -> p5
@@
 # Rate
-results32 %>% 
+results207 %>% 
   filter(osc_rate < 0.1 | osc_rate > 0.4) -> tmp1
 
-results32 %>% 
+results207 %>% 
   filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
@@
 # Rate: burst v sustained
-tmp3 <- results21
-tmp3$osc_mode <- rep("Sustained", nrow(results21))
+tmp3 <- results203
+tmp3$osc_mode <- rep("Sustained", nrow(results203))
 
-tmp4 <- results32
-tmp4$osc_mode <- rep("Burst", nrow(results32))
+tmp4 <- results207
+tmp4$osc_mode <- rep("Burst", nrow(results207))
 
@@
   group_by(osc_rate, Ca_target) %>% 
-  summarise(M=mean(mse_var), SD=sd(mse_var)) -> tmp1
+  summarise(M=mean(mse_error), SD=sd(mse_error)) -> tmp1
 
@@
 p6 <- textGrob("Calcium level")
+grid.arrange(p1, p2, p3, p4, p5, p6,layout_matrix=layout_matrix)
 

### 2018-11-01 resistingrhythm/neurons.py
Ca conc is not initialized at ca_target

@@ -191,6 +191,7 @@ def HHH(time,
     P_target.g_KCa = g_KCa
     P_target.g_Ca = g_Ca
     P_target.Ca_target = Ca_target
+    P_target.Ca = Ca_target
 
     net.add(P_target)
 

### 2018-11-01 resistingrhythm/analysis/paper_figures_v3.Rmd
Tweak v3

@@
 osc_rates <- c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0, 3.5, 4.0, 4.5, 5.0, 5.5, 6.0)
-stim_codes <- c(3)#, 4)
+stim_codes <- c(3)# , 4)
 
@@
 osc_rates <- c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0, 3.5, 4.0, 4.5, 5.0, 5.5, 6.0)
-stim_codes <- c(3) #, 3)
+stim_codes <- c(3)#, 4)
 
@@
 # Calcium exp, E, sustained
-exp_code <- 19
+exp_code <- 218
 osc_codes <- c(105, 115, 125, 135, 145, 155)
 osc_rates <- c(0.5, 1.5, 2.5, 3.5, 4.5, 5.5)
-stim_codes <- c(0, 1)
+stim_codes <- c(3)
 
@@
 
-results19 <- NULL
+results218 <- NULL
 for(i in 1:length(osc_codes)){
@@
 
-      results19 <- rbind(results19, df)
+      results218 <- rbind(results218, df)
     }
@@
 # -----------------------------------------------------------------------
-# Add default Ca value, from exp
-exp_code <- 15
+# # Add default Ca value, from exp
+exp_code <- 211
 osc_codes <- c(105, 115, 125, 135, 145, 155)
 osc_rates <- c(0.5, 1.5, 2.5, 3.5, 4.5, 5.5)
-stim_codes <- c(0, 1)
+stim_codes <- c(3)
 ca_targets <- c(0.03, 0.03, 0.03, 0.03)
 
+df <- NULL
 for(i in 1:length(osc_codes)){
@@
   group_by(osc_rate) %>% 
-  mutate(M=mean(mse_error), SD=sd(mse_error)) -> tmp2
+  mutate(M=mean(kappa_coord), SD=sd(kappa_coord)) -> tmp2
 
-ggplot(data=tmp1, mapping=aes(x=osc_rate, y=mse_error, group=osc_rate)) +
+ggplot(data=tmp1, mapping=aes(x=osc_rate, y=kappa_coord, group=osc_rate)) +
   geom_jitter(alpha=0.2, size=0.2, position = position_jitter(width = .05)) +
@@
   # geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
-  labs(title="a.", y="Variance (s)", x="Osc. rate (Hz)") +
+  labs(title="d.", y="Kappa", x="Osc. rate (Hz)") +
   # # lims(y=c(0, .15)) +
@@
   # geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
-  labs(title="b.", y="Variance (s)", x="Osc. rate (Hz)") +
+  labs(title="e.", y="Kappa", x="Osc. rate (Hz)") +
   # lims(y=c(0, .01)) +
@@
   # geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
-  labs(title="d.", y=expression(Delta*" rate (Hz)"), x="Osc. rate (Hz)") +
+  labs(title="a.", y=expression(Delta*" rate (Hz)"), x="Osc. rate (Hz)") +
   # lims(y=c(0, 70)) +
@@
   # geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
-  labs(title="e.", y=expression(Delta*" rate (Hz)"), x="Osc. rate (Hz)") +
+  labs(title="b.", y=expression(Delta*" rate (Hz)"), x="Osc. rate (Hz)") +
   # lims(y=c(-4, 4)) +
@@
   group_by(osc_rate) %>% 
-  mutate(M=mean(mse_error), SD=sd(mse_error)) -> tmp2
+  mutate(M=mean(kappa_coord), SD=sd(kappa_coord)) -> tmp2
 
-ggplot(data=tmp1, mapping=aes(x=osc_rate, y=mse_error, group=osc_rate)) +
+ggplot(data=tmp1, mapping=aes(x=osc_rate, y=kappa_coord, group=osc_rate)) +
   geom_jitter(alpha=0.2, size=0.2, position = position_jitter(width = .05), color="dodgerblue3") +
@@
                 width=.15, size=0.2, color="dodgerblue3") +
-  labs(title="c.", y="Variance (s)", x="Osc. rate (Hz)") +
+  labs(title="f.", y="Kappa", x="Osc. rate (Hz)") +
   theme_classic() + 
@@
   geom_hline(yintercept=0, size=0.2) +
-  labs(title="d.", y=expression(Delta*" rate (Hz)"), x="Osc. rate (Hz)") +
+  labs(title="c.", y=expression(Delta*" rate (Hz)"), x="Osc. rate (Hz)") +
   # lims(y=c(-3, 3)) +
@@
   geom_boxplot(notch = TRUE, width=0.4,  outlier.size=0.05, outlier.alpha=0.5, show.legend=FALSE) +
-  labs(title="f.", y=expression(Delta*" rate (Hz)"), x="") +
+  labs(title="g.", y=expression(Delta*" rate (Hz)"), x="") +
   theme_classic() +
@@
   theme(
-    legend.position = c(0.1, 2),
+    legend.position = c(0.15, 2),
     legend.background = element_rect(colour ="black"),
@@
 
-# NEW
-
 # -
@@
   c(NA, 8, 8, 9, 9, 9, 9, NA),
-  c(10, 1, 1, 2, 2, 5, 5, NA), 
-  c(10, 1, 1, 2, 2, 5, 5, NA), 
-  c(10, 1, 1, 2, 2, 5, 5, NA), 
+  c(11, 3, 3, 4, 4, 6, 6, NA),
+  c(11, 3, 3, 4, 4, 6, 6, NA),
+  c(11, 3, 3, 4, 4, 6, 6, NA),
+  c(11, 3, 3, 4, 4, 6, 6, 7),
   c(10, 1, 1, 2, 2, 5, 5, 7), 
-  c(11, 3, 3, 4, 4, 6, 6, 7),
-  c(11, 3, 3, 4, 4, 6, 6, 7),
-  c(11, 3, 3, 4, 4, 6, 6, 7),
-  c(11, 3, 3, 4, 4, 6, 6, 7)
+  c(10, 1, 1, 2, 2, 5, 5, 7), 
+  c(10, 1, 1, 2, 2, 5, 5, 7), 
+  c(10, 1, 1, 2, 2, 5, 5, 7)
+
 )
@@
 p9 <- textGrob("Homeostatsis")
-p10 <- textGrob("Synchrony")
+p10 <- textGrob("Coordination")
 p11 <- textGrob("Excitability")
@@
 
-```{r, fig.width=4.5, fig.height=2.0}
+```{r, fig.width=5, fig.height=2.25}
 shift <- -0.15
@@
   # geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
-  labs(title="a.", y="Variance (s)", x="Osc. rate (Hz)") +
+  labs(title="d.", y="Kappa", x="Osc. rate (Hz)") +
   # lims(y=c(0, .15)) +
@@
   # geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
-  labs(title="b.", y="Variance (s)", x="Osc. rate (Hz)") +
+  labs(title="e.", y="Kappa", x="Osc. rate (Hz)") +
   # lims(y=c(0, .15)) +
@@
   c(NA, 8, 8, 9, 9, 9, 9, NA),
-  c(10, 1, 1, 2, 2, 5, 5, NA), 
-  c(10, 1, 1, 2, 2, 5, 5, NA), 
-  c(10, 1, 1, 2, 2, 5, 5, NA), 
+  c(11, 3, 3, 4, 4, 6, 6, NA),
+  c(11, 3, 3, 4, 4, 6, 6, NA),
+  c(11, 3, 3, 4, 4, 6, 6, NA),
+  c(11, 3, 3, 4, 4, 6, 6, 7),
   c(10, 1, 1, 2, 2, 5, 5, 7), 
-  c(11, 3, 3, 4, 4, 6, 6, 7),
-  c(11, 3, 3, 4, 4, 6, 6, 7),
-  c(11, 3, 3, 4, 4, 6, 6, 7),
-  c(11, 3, 3, 4, 4, 6, 6, 7)
+  c(10, 1, 1, 2, 2, 5, 5, 7), 
+  c(10, 1, 1, 2, 2, 5, 5, 7), 
+  c(10, 1, 1, 2, 2, 5, 5, 7)
 )
@@
 # Var
-results19 %>% 
+results218 %>% 
   filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
   group_by(osc_rate, Ca_target) %>% 
-  summarise(M=mean(mse_error), SD=sd(mse_error)) -> tmp1
+  summarise(M=mean(kappa_coord - mse_ref), SD=sd(kappa_coord - mse_ref)) -> tmp1
 
@@
 # Rate
-results19 %>% 
+results218 %>% 
   filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 

### 2018-11-02 resistingrhythm/analysis/paper_figures_v3.Rmd
Tweak plot colors

@@
 ggplot(data=tmp1, mapping=aes(x=osc_rate, y=kappa_coord, group=osc_rate)) +
-  geom_jitter(alpha=0.2, size=0.2, position = position_jitter(width = .05), color="dodgerblue3") +
-  geom_point(data=tmp2, mapping=aes(x=osc_rate - shift, y=M), size=0.8, color="dodgerblue3") +
+  geom_jitter(alpha=0.2, size=0.2, position = position_jitter(width = .05), color="darkgoldenrod3") +
+  geom_point(data=tmp2, mapping=aes(x=osc_rate - shift, y=M), size=0.8, color="darkgoldenrod3") +
   geom_errorbar(data=tmp2, mapping=aes(x=osc_rate - shift, ymin=M - SD, ymax=M + SD), 
-                width=.15, size=0.2, color="dodgerblue3") +
+                width=.15, size=0.2, color="darkgoldenrod3") +
   labs(title="f.", y="Kappa", x="Osc. rate (Hz)") +
@@
 ggplot(data=tmp1, mapping=aes(x=osc_rate, y=rate_k - rate_ref, group=osc_rate)) +
-  geom_jitter(alpha=0.2, size=0.2, position = position_jitter(width = .05), color="dodgerblue3") +
-  geom_point(data=tmp2, mapping=aes(x=osc_rate - shift, y=M), size=0.6, color="dodgerblue3") +
+  geom_jitter(alpha=0.2, size=0.2, position = position_jitter(width = .05), color="darkgoldenrod3") +
+  geom_point(data=tmp2, mapping=aes(x=osc_rate - shift, y=M), size=0.6, color="darkgoldenrod3") +
   geom_errorbar(data=tmp2, mapping=aes(x=osc_rate - shift, ymin=M - SD, ymax=M + SD), 
-                width=.15, size=0.2, color="dodgerblue3") +
+                width=.15, size=0.2, color="darkgoldenrod3") +
   geom_hline(yintercept=0, size=0.2) +
@@
   # lims(y=c(-3, 3)) +
-  scale_fill_manual(values=c("dodgerblue3", "black"), name="Oscillation") +
-  scale_color_manual(values=c("dodgerblue3", "black"), name="Oscillation") +
+  scale_fill_manual(values=c("darkgoldenrod3", "black"), name="Oscillation") +
+  scale_color_manual(values=c("darkgoldenrod3", "black"), name="Oscillation") +
   stat_compare_means(method="wilcox.test", label="p.signif", 
@@
   group_by(osc_rate, Ca_target) %>% 
-  summarise(M=mean(kappa_coord - mse_ref), SD=sd(kappa_coord - mse_ref)) -> tmp1
+  summarise(M=mean(kappa_coord), SD=sd(kappa_coord)) -> tmp1
 
@@
   geom_errorbar(aes(ymin=M - SD, ymax=M + SD), alpha=0.5, width=.1, size=0.4)  +
-  labs(title="a", y="Variance (s)", x="Osc. rate (Hz)") +
+  labs(title="b", y="Kappa", x="Osc. rate (Hz)") +
   scale_color_manual(
-    values=c("paleturquoise3", "paleturquoise4", "black", "indianred4", "indianred1"), 
+    values=c("plum1", "plum2", "black", "plum3", "plum4"), 
     guide=FALSE) +
@@
   geom_errorbar(aes(ymin=M - SD, ymax=M + SD), alpha=0.5, width=.1, size=0.4)  +
-  labs(title="b", y=expression(Delta*" rate (Hz)"), x="Osc. rate (Hz)") +
+  labs(title="a", y=expression(Delta*" rate (Hz)"), x="Osc. rate (Hz)") +
   geom_hline(yintercept=0, size=0.2) +
   scale_color_manual(
-    values=c("paleturquoise3", "paleturquoise4", "black", "indianred4", "indianred1"), 
+    values=c("plum1", "plum2", "black", "plum3", "plum4"), 
     name="Target [Ca]\n(mmolar)") +
@@
   theme(
-    plot.title = element_text(hjust = -.34, size=18, face="bold"),
-    legend.position = c(1.35, 1.5),
+    plot.title = element_text(hjust = -.5, size=18, face="bold"),
+    legend.position = c(1.35, 0.0),
     legend.background = element_rect(colour ="black"),
@@
 
-# p3 <- textGrob("Homeostatsis")
-p3 <- textGrob("Synchrony")
+p3 <- textGrob("Coordination")
 p4 <- textGrob("Excitability")
@@
   c(6, 6, 6, 6), 
+  c(4, 2, 2, 5),
+  c(4, 2, 2, 5),
+  c(4, 2, 2, 5),
+  c(4, 2, 2, 5),
   c(3, 1, 1, 5),
@@
   c(3, 1, 1, 5), 
-  c(3, 1, 1, 5), 
-  c(4, 2, 2, 5),
-  c(4, 2, 2, 5),
-  c(4, 2, 2, 5),
-  c(4, 2, 2, 5))
+  c(3, 1, 1, 5) 
+)
 

### 2018-11-02 resistingrhythm/analysis/paper_figures_v3.Rmd
Moved to un-norm rates in all figures

@@
   group_by(osc_rate) %>% 
-  mutate(M=mean(rate_k - rate_ref), SD=sd(rate_k - rate_ref)) -> tmp2
+  mutate(M=mean(rate_k), SD=sd(rate_k)) -> tmp2
 
-ggplot(data=tmp1, mapping=aes(x=osc_rate, y=rate_k - rate_ref, group=osc_rate)) +
+ggplot(data=tmp1, mapping=aes(x=osc_rate, y=rate_k, group=osc_rate)) +
   geom_jitter(alpha=0.2, size=0.2, position = position_jitter(width = .05)) +
@@
   # geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
-  labs(title="a.", y=expression(Delta*" rate (Hz)"), x="Osc. rate (Hz)") +
+  labs(title="a.", y="Pop. rate (Hz)", x="Osc. rate (Hz)") +
   # lims(y=c(0, 70)) +
@@
   # geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
-  labs(title="b.", y=expression(Delta*" rate (Hz)"), x="Osc. rate (Hz)") +
+  labs(title="b.", y="Pop. rate (Hz)", x="Osc. rate (Hz)") +
   # lims(y=c(-4, 4)) +
@@
   group_by(osc_rate) %>% 
-  mutate(M=mean(rate_k - rate_ref), SD=sd(rate_k - rate_ref)) -> tmp2
+  mutate(M=mean(rate_k), SD=sd(rate_k)) -> tmp2
 
-ggplot(data=tmp1, mapping=aes(x=osc_rate, y=rate_k - rate_ref, group=osc_rate)) +
+ggplot(data=tmp1, mapping=aes(x=osc_rate, y=rate_k, group=osc_rate)) +
   geom_jitter(alpha=0.2, size=0.2, position = position_jitter(width = .05), color="darkgoldenrod3") +
@@
   geom_hline(yintercept=0, size=0.2) +
-  labs(title="c.", y=expression(Delta*" rate (Hz)"), x="Osc. rate (Hz)") +
+  labs(title="c.", y="Pop. rate (Hz)", x="Osc. rate (Hz)") +
   # lims(y=c(-3, 3)) +
@@
   geom_boxplot(notch = TRUE, width=0.4,  outlier.size=0.05, outlier.alpha=0.5, show.legend=FALSE) +
-  labs(title="g.", y=expression(Delta*" rate (Hz)"), x="") +
+  labs(title="g.", y="Norm. rate (Hz)", x="") +
   theme_classic() +
@@
   group_by(osc_rate, Ca_target) %>% 
-  summarise(M=mean(rate_k - rate_ref), SD=sd(rate_k - rate_ref)) -> tmp2
+  summarise(M=mean(rate_k), SD=sd(rate_k)) -> tmp2
 
@@
   geom_errorbar(aes(ymin=M - SD, ymax=M + SD), alpha=0.5, width=.1, size=0.4)  +
-  labs(title="a", y=expression(Delta*" rate (Hz)"), x="Osc. rate (Hz)") +
+  labs(title="a", y="Pop. rate (Hz)", x="Osc. rate (Hz)") +
   geom_hline(yintercept=0, size=0.2) +

### 2018-11-03 resistingrhythm/analysis/paper_figures_v3.Rmd
Update fig plots. Tweak same.

@@
 # 16: Burst E, with H
-exp_code <- 204
+exp_code <- 214
 osc_codes <- c(100, 101, 102, 103, 104, 105, 110, 115, 120, 125, 130, 135, 140, 145, 150, 155, 160)
@@
 
-results204 <- NULL
+results214 <- NULL
 for(i in 1:length(osc_codes)){
@@
 
-    results204 <- rbind(results204, df)
+    results214 <- rbind(results214, df)
   }
@@
 
-results204 %>%
-  filter(rate_k > 0) -> results204
+results214 %>%
+  filter(rate_k > 0) -> results214
 
@@
 # 15: Sustained E, with H
-exp_code <- 201
+exp_code <- 211
 osc_codes <- c(100, 101, 102, 103, 104, 105, 110, 115, 120, 125, 130, 135, 140, 145, 150, 155, 160)
 osc_rates <- c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0, 3.5, 4.0, 4.5, 5.0, 5.5, 6.0)
-stim_codes <- c(3)# , 4)
+stim_codes <- c(3, 4)
 
-results201 <- NULL
+results211 <- NULL
 for(i in 1:length(osc_codes)){
@@
 
-    results201 <- rbind(results201, df)
+    results211 <- rbind(results211, df)
   }
@@
 
-results201 %>%
-  filter(rate_k > 0) -> results201
+results211 %>%
+  filter(rate_k > 0) -> results211
 
@@
 # 22: Sustained E, with NO H
-exp_code <- 200
+exp_code <- 210
 osc_codes <- c(100, 101, 102, 103, 104, 105, 110, 115, 120, 125, 130, 135, 140, 145, 150, 155, 160)
 osc_rates <- c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0, 3.5, 4.0, 4.5, 5.0, 5.5, 6.0)
-stim_codes <- c(3)#, 4)
+stim_codes <- c(3, 4)
 
-results200 <- NULL
+results210 <- NULL
 for(i in 1:length(osc_codes)){
@@
 
-    results200 <- rbind(results200, df)
+    results210 <- rbind(results210, df)
   }
@@
 
-results200 %>%
-  filter(rate_k > 0) -> results200
+results210 %>%
+  filter(rate_k > 0) -> results210
 
@@
 # 21: Sustained I, with H
-exp_code <- 203
+exp_code <- 213
 osc_codes <- c(100, 101, 102, 103, 104, 105, 110, 115, 120, 125, 130, 135, 140, 145, 150, 155, 160)
@@
 
-results203 <- NULL
+results213 <- NULL
 for(i in 1:length(osc_codes)){
@@
 
-    results203 <- rbind(results203, df)
+    results213 <- rbind(results213, df)
   }
@@
 
-results203 %>%
-  filter(rate_k > 0) -> results203
+results213 %>%
+  filter(rate_k > 0) -> results213
 
@@
 # 23: Sustained I, with NO H
-exp_code <- 202
+exp_code <- 212
 osc_codes <- c(100, 101, 102, 103, 104, 105, 110, 115, 120, 125, 130, 135, 140, 145, 150, 155, 160)
 osc_rates <- c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0, 3.5, 4.0, 4.5, 5.0, 5.5, 6.0)
-stim_codes <- c(3)#, 4)
+stim_codes <- c(3, 4)
 
-results202 <- NULL
+results212 <- NULL
 for(i in 1:length(osc_codes)){
@@
 
-    results202 <- rbind(results202, df)
+    results212 <- rbind(results212, df)
   }
@@
 
-results202 %>%
-  filter(rate_k > 0) -> results202
+results212 %>%
+  filter(rate_k > 0) -> results212
 
@@
 # 30: Burst I, with H
-exp_code <- 207
+# HERE
+exp_code <- 217
 osc_codes <- c(100, 101, 102, 103, 104, 105, 110, 115, 120, 125, 130, 135, 140, 145, 150, 155, 160)
@@
 
-results207 <- NULL
+results217 <- NULL
 for(i in 1:length(osc_codes)){
@@
 
-    results207 <- rbind(results207, df)
+    results217 <- rbind(results217, df)
   }
@@
 
-results207 %>%
-  filter(rate_k > 0) -> results207
+results217 %>%
+  filter(rate_k > 0) -> results217
 
@@
 # No H, E
-results200 %>% 
+results210 %>% 
   filter(osc_rate < 0.1 | osc_rate > 0.4) -> tmp1
 
-results200 %>% 
+results210 %>% 
   filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
@@
   theme_classic() +
-  theme(plot.title = element_text(hjust = -.35, size=18, face="bold")) -> p1
+  theme(plot.title = element_text(hjust = -.3, size=18, face="bold")) -> p1
 
@@
 # With H, E
-results201 %>% 
+results211 %>% 
   filter(osc_rate < 0.1 | osc_rate > 0.4) -> tmp1
 
-results201 %>% 
+results211 %>% 
   filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
@@
   theme_classic() +
-  theme(plot.title = element_text(hjust = -.5, size=18, face="bold")) -> p2
+  theme(plot.title = element_text(hjust = -.3, size=18, face="bold")) -> p2
 
@@
 # Rate, no H, E
-results200 %>% 
+results210 %>% 
   filter(osc_rate < 0.1 | osc_rate > 0.4) -> tmp1
 
-results200 %>% 
+results210 %>% 
   filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
@@
   theme_classic() + 
-  theme(plot.title = element_text(hjust = -.25, size=18, face="bold")) -> p3
+  theme(plot.title = element_text(hjust = -.3, size=18, face="bold")) -> p3
 
@@
 # Rate, with H, E
-results201 %>% 
+results211 %>% 
   filter(osc_rate < 0.1 | osc_rate > 0.4) -> tmp1
 
-results201 %>% 
+results211 %>% 
   filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
@@
 # Var
-results204 %>% 
+results214 %>% 
   filter(osc_rate < 0.1 | osc_rate > 0.4) -> tmp1
 
-results204 %>% 
+results214 %>% 
   filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
@@
   # lims(y=c(0, .01)) +
-  theme(plot.title = element_text(hjust = -.6, size=18, face="bold")) -> p5
+  theme(plot.title = element_text(hjust = -.3, size=18, face="bold")) -> p5
 
@@
 # Rate
-results204 %>% 
+results214 %>% 
   filter(osc_rate < 0.1 | osc_rate > 0.4) -> tmp1
 
-results204 %>% 
+results214 %>% 
   filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
@@
   theme_classic() +
-  theme(plot.title = element_text(hjust = -.4, size=18, face="bold")) -> p6
+  theme(plot.title = element_text(hjust = -.3, size=18, face="bold")) -> p6
 
@@
 # Rate: burst v sustained
-tmp3 <- results201
-tmp3$osc_mode <- rep("Sustained", nrow(results201))
+tmp3 <- results211
+tmp3$osc_mode <- rep("Sustained", nrow(results211))
 
-tmp4 <- results204
-tmp4$osc_mode <- rep("Burst", nrow(results204))
+tmp4 <- results214
+tmp4$osc_mode <- rep("Burst", nrow(results214))
 
@@
     axis.text.x = element_text(angle = 70, hjust = 1),
-    plot.title = element_text(hjust = -1.2, size=18, face="bold")) -> p7
+    plot.title = element_text(hjust = -1.3, size=18, face="bold")) -> p7
 
@@
 # No H, E
-results202 %>% 
+results212 %>% 
   filter(osc_rate < 0.1 | osc_rate > 0.4) -> tmp1
 
-results202 %>% 
+results212 %>% 
   filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
@@
 # With H, E
-results203 %>% 
+results213 %>% 
   filter(osc_rate < 0.1 | osc_rate > 0.4) -> tmp1
 
-results203 %>% 
+results213 %>% 
   filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
@@
 # Rate, no H, E
-results202 %>% 
+results212 %>% 
   filter(osc_rate < 0.1 | osc_rate > 0.4) -> tmp1
 
-results202 %>% 
+results212 %>% 
   filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
@@
 # Rate, with H, E
-results203 %>% 
+results213 %>% 
   filter(osc_rate < 0.1 | osc_rate > 0.4) -> tmp1
 
-results203 %>% 
+results213 %>% 
   filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
@@
 # Var
-results207 %>% 
+results217 %>% 
   filter(osc_rate < 0.1 | osc_rate > 0.4) -> tmp1
 
-results207 %>% 
+results217 %>% 
   filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
@@
 # Rate
-results207 %>% 
+results217 %>% 
   filter(osc_rate < 0.1 | osc_rate > 0.4) -> tmp1
 
-results207 %>% 
+results217 %>% 
   filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
@@
 # Rate: burst v sustained
-tmp3 <- results203
-tmp3$osc_mode <- rep("Sustained", nrow(results203))
+tmp3 <- results213
+tmp3$osc_mode <- rep("Sustained", nrow(results213))
 
-tmp4 <- results207
-tmp4$osc_mode <- rep("Burst", nrow(results207))
+tmp4 <- results217
+tmp4$osc_mode <- rep("Burst", nrow(results217))
 

### 2018-11-05 resistingrhythm/analysis/paper_figures_v3.Rmd
Tweaked SFN figures
All obs now relative
Fixed y axis so comparisons are fair.

@@
   group_by(osc_rate) %>% 
-  mutate(M=mean(kappa_coord), SD=sd(kappa_coord)) -> tmp2
+  mutate(M=mean(kappa_coord - k_ref), SD=sd(kappa_coord - k_ref)) -> tmp2
 
-ggplot(data=tmp1, mapping=aes(x=osc_rate, y=kappa_coord, group=osc_rate)) +
-  geom_jitter(alpha=0.2, size=0.2, position = position_jitter(width = .05)) +
-  geom_point(data=tmp2, mapping=aes(x=osc_rate - shift, y=M), size=0.8) +
+ggplot(data=tmp1, mapping=aes(x=osc_rate, y=kappa_coord - k_ref, group=osc_rate)) +
+  # geom_jitter(alpha=0.2, size=0.2, position = position_jitter(width = .05)) +
+  geom_point(data=tmp2, mapping=aes(x=osc_rate - shift, y=M), size=0.8, shape="-") +
   geom_errorbar(data=tmp2, mapping=aes(x=osc_rate - shift, ymin=M - SD, ymax=M + SD), width=.15, size=0.2) +
+  geom_hline(yintercept=0, size=0.2) +
   # geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
-  labs(title="d.", y="Kappa", x="Osc. rate (Hz)") +
-  # # lims(y=c(0, .15)) +
+  labs(title="d.", y="Rel. kappa", x="Osc. rate (Hz)") +
+ lims(y=c(-.15, .15)) +
   theme_classic() +
@@
   group_by(osc_rate) %>% 
-  mutate(M=mean(kappa_coord), SD=sd(kappa_coord)) -> tmp2
+  mutate(M=mean(kappa_coord - k_ref), SD=sd(kappa_coord - k_ref)) -> tmp2
 
-ggplot(data=tmp1, mapping=aes(x=osc_rate, y=kappa_coord, group=osc_rate)) +
-  geom_jitter(alpha=0.2, size=0.2, position = position_jitter(width = .05)) +
+ggplot(data=tmp1, mapping=aes(x=osc_rate, y=kappa_coord - k_ref, group=osc_rate)) +
+  # # geom_jitter(alpha=0.2, size=0.2, position = position_jitter(width = .05)) +
   geom_point(data=tmp2, mapping=aes(x=osc_rate - shift, y=M), size=0.8) +
@@
   # geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
-  labs(title="e.", y="Kappa", x="Osc. rate (Hz)") +
-  # lims(y=c(0, .01)) +
+  labs(title="e.", y="Rel. kappa", x="Osc. rate (Hz)") +
+ lims(y=c(-.15, .15)) +
+  geom_hline(yintercept=0, size=0.2) +
   theme_classic() +
@@
   group_by(osc_rate) %>% 
-  mutate(M=mean(rate_k), SD=sd(rate_k)) -> tmp2
+  mutate(M=mean(rate_k - rate_ref), SD=sd(rate_k - rate_ref)) -> tmp2
 
-ggplot(data=tmp1, mapping=aes(x=osc_rate, y=rate_k, group=osc_rate)) +
-  geom_jitter(alpha=0.2, size=0.2, position = position_jitter(width = .05)) +
+ggplot(data=tmp1, mapping=aes(x=osc_rate, y=rate_k - rate_ref, group=osc_rate)) +
+  # geom_jitter(alpha=0.2, size=0.2, position = position_jitter(width = .05)) +
   geom_point(data=tmp2, mapping=aes(x=osc_rate - shift, y=M), size=0.8) +
@@
   # geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
-  labs(title="a.", y="Pop. rate (Hz)", x="Osc. rate (Hz)") +
+  labs(title="a.", y="Rel. rate (Hz)", x="Osc. rate (Hz)") +
   # lims(y=c(0, 70)) +
@@
   # geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
-  labs(title="b.", y="Pop. rate (Hz)", x="Osc. rate (Hz)") +
+  labs(title="b.", y="Rel. rate (Hz)", x="Osc. rate (Hz)") +
   # lims(y=c(-4, 4)) +
@@
   group_by(osc_rate) %>% 
-  mutate(M=mean(kappa_coord), SD=sd(kappa_coord)) -> tmp2
+  mutate(M=mean(kappa_coord - k_ref), SD=sd(kappa_coord - k_ref)) -> tmp2
 
-ggplot(data=tmp1, mapping=aes(x=osc_rate, y=kappa_coord, group=osc_rate)) +
-  geom_jitter(alpha=0.2, size=0.2, position = position_jitter(width = .05), color="darkgoldenrod3") +
+ggplot(data=tmp1, mapping=aes(x=osc_rate, y=kappa_coord - k_ref, group=osc_rate)) +
+  # geom_jitter(alpha=0.2, size=0.2, position = position_jitter(width = .05), color="darkgoldenrod3") +
   geom_point(data=tmp2, mapping=aes(x=osc_rate - shift, y=M), size=0.8, color="darkgoldenrod3") +
@@
                 width=.15, size=0.2, color="darkgoldenrod3") +
-  labs(title="f.", y="Kappa", x="Osc. rate (Hz)") +
+  labs(title="f.", y="Rel. kappa", x="Osc. rate (Hz)") +
   theme_classic() +
-  # lims(y=c(0, .01)) +
+  geom_hline(yintercept=0, size=0.2) +
+ lims(y=c(-.15, .15)) +
   theme(plot.title = element_text(hjust = -.3, size=18, face="bold")) -> p5
@@
   group_by(osc_rate) %>% 
-  mutate(M=mean(rate_k), SD=sd(rate_k)) -> tmp2
+  mutate(M=mean(rate_k - rate_ref), SD=sd(rate_k - rate_ref)) -> tmp2
 
-ggplot(data=tmp1, mapping=aes(x=osc_rate, y=rate_k, group=osc_rate)) +
-  geom_jitter(alpha=0.2, size=0.2, position = position_jitter(width = .05), color="darkgoldenrod3") +
+ggplot(data=tmp1, mapping=aes(x=osc_rate, y=rate_k - rate_ref, group=osc_rate)) +
+  # geom_jitter(alpha=0.2, size=0.2, position = position_jitter(width = .05), color="darkgoldenrod3") +
   geom_point(data=tmp2, mapping=aes(x=osc_rate - shift, y=M), size=0.6, color="darkgoldenrod3") +
@@
   geom_hline(yintercept=0, size=0.2) +
-  labs(title="c.", y="Pop. rate (Hz)", x="Osc. rate (Hz)") +
+  labs(title="c.", y="Rel. rate (Hz)", x="Osc. rate (Hz)") +
   # lims(y=c(-3, 3)) +
@@
   geom_boxplot(notch = TRUE, width=0.4,  outlier.size=0.05, outlier.alpha=0.5, show.legend=FALSE) +
-  labs(title="g.", y="Norm. rate (Hz)", x="") +
+  labs(title="g.", y="Rel. rate (Hz)", x="") +
   theme_classic() +
@@
   group_by(osc_rate) %>% 
-  mutate(M=mean(kappa_coord), SD=sd(kappa_coord)) -> tmp2
+  mutate(M=mean(kappa_coord - k_ref), SD=sd(kappa_coord - k_ref)) -> tmp2
 
-ggplot(data=tmp1, mapping=aes(x=osc_rate, y=kappa_coord, group=osc_rate)) +
-  geom_jitter(alpha=0.2, size=0.2, position = position_jitter(width = .05)) +
+ggplot(data=tmp1, mapping=aes(x=osc_rate, y=kappa_coord - k_ref, group=osc_rate)) +
+  # geom_jitter(alpha=0.2, size=0.2, position = position_jitter(width = .05)) +
   geom_point(data=tmp2, mapping=aes(x=osc_rate - shift, y=M), size=0.8) +
   geom_errorbar(data=tmp2, mapping=aes(x=osc_rate - shift, ymin=M - SD, ymax=M + SD), width=.15, size=0.2) +
+  geom_hline(yintercept=0, size=0.2) +
   # geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
-  labs(title="d.", y="Kappa", x="Osc. rate (Hz)") +
-  # lims(y=c(0, .15)) +
+  labs(title="d.", y="Rel. kappa", x="Osc. rate (Hz)") +
+  lims(y=c(-0.05, .05)) +
   theme_classic() +
-  theme(plot.title = element_text(hjust = -.35, size=18, face="bold")) -> p1
+  theme(plot.title = element_text(hjust = -.3, size=18, face="bold")) -> p1
 
@@
   group_by(osc_rate) %>% 
-  mutate(M=mean(kappa_coord), SD=sd(kappa_coord)) -> tmp2
+  mutate(M=mean(kappa_coord - k_ref), SD=sd(kappa_coord - k_ref)) -> tmp2
 
-ggplot(data=tmp1, mapping=aes(x=osc_rate, y=kappa_coord, group=osc_rate)) +
-  geom_jitter(alpha=0.2, size=0.2, position = position_jitter(width = .05)) +
+ggplot(data=tmp1, mapping=aes(x=osc_rate, y=kappa_coord - k_ref, group=osc_rate)) +
+  # geom_jitter(alpha=0.2, size=0.2, position = position_jitter(width = .05)) +
   geom_point(data=tmp2, mapping=aes(x=osc_rate - shift, y=M), size=0.8) +
   geom_errorbar(data=tmp2, mapping=aes(x=osc_rate - shift, ymin=M - SD, ymax=M + SD), width=.15, size=0.2) +
+  geom_hline(yintercept=0, size=0.2) +
   # geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
-  labs(title="e.", y="Kappa", x="Osc. rate (Hz)") +
-  # lims(y=c(0, .15)) +
+  labs(title="e.", y="Rel. kappa", x="Osc. rate (Hz)") +
+  lims(y=c(-0.05, .05)) +
   theme_classic() +
-  theme(plot.title = element_text(hjust = -.5, size=18, face="bold")) -> p2
+  theme(plot.title = element_text(hjust = -.3, size=18, face="bold")) -> p2
 
@@
   # geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
-  labs(title="a.", y="Pop. rate (Hz)", x="Osc. rate (Hz)") +
-  # lims(y=c(0, 70)) +
+  labs(title="a.", y="Rel. rate (Hz)", x="Osc. rate (Hz)") +
+  lims(y=c(-30, 2)) +
   geom_hline(yintercept=0, size=0.2) +
   theme_classic() + 
-  theme(plot.title = element_text(hjust = -.25, size=18, face="bold")) -> p3
+  theme(plot.title = element_text(hjust = -.3, size=18, face="bold")) -> p3
 
@@
   # geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
-  labs(title="b.", y="Pop. rate (Hz)", x="Osc. rate (Hz)") +
-  # lims(y=c(-4, 4)) +
+  labs(title="b.", y="Rel. rate (Hz)", x="Osc. rate (Hz)") +
+  lims(y=c(-30, 2)) +
   geom_hline(yintercept=0, size=0.2) +
@@
                 width=.15, size=0.2, color="darkgoldenrod3") +
-  labs(title="f.", y="Kappa", x="Osc. rate (Hz)") +
+  geom_hline(yintercept=0, size=0.2) +
+  labs(title="f.", y="Rel. kappa", x="Osc. rate (Hz)") +
   theme_classic() + 
-  # lims(y=c(0, .15)) +
-  theme(plot.title = element_text(hjust = -.6, size=18, face="bold")) -> p5
+  lims(y=c(-0.05, .05)) +
+  theme(plot.title = element_text(hjust = -.3, size=18, face="bold")) -> p5
 
@@
   geom_hline(yintercept=0, size=0.2) +
-  labs(title="c.", y="Pop. rate (Hz)", x="Osc. rate (Hz)") +
-  # lims(y=c(-3, 3)) +
+  labs(title="c.", y="Rel. rate (Hz)", x="Osc. rate (Hz)") +
+  geom_hline(yintercept=0, size=0.2) +
+  lims(y=c(-30, 2)) +
   theme_classic() +
-  theme(plot.title = element_text(hjust = -.4, size=18, face="bold")) -> p6
+  theme(plot.title = element_text(hjust = -.3, size=18, face="bold")) -> p6
 
@@
   geom_boxplot(notch = TRUE, width=0.4,  outlier.size=0.05, outlier.alpha=0.5, show.legend=FALSE) +
-  labs(title="g.", y="Norm. rate (Hz)", x="") +
+  labs(title="g.", y="Rel. rate (Hz)", x="") +
   theme_classic() +
   geom_hline(yintercept=0, size=0.2) +
-  # lims(y=c(-3, 3)) +
+  lims(y=c(-30, 2)) +
   scale_fill_manual(values=c("darkgoldenrod3", "black"), name="Oscillation") +
@@
 # Figure 4. Calcium targets
-
 ```{r, fig.width=2.4, fig.height=1.7}
@@
   group_by(osc_rate, Ca_target) %>% 
-  summarise(M=mean(kappa_coord), SD=sd(kappa_coord)) -> tmp1
+  summarise(M=mean(kappa_coord - k_ref), SD=sd(kappa_coord - k_ref)) -> tmp1
 
@@
   geom_errorbar(aes(ymin=M - SD, ymax=M + SD), alpha=0.5, width=.1, size=0.4)  +
-  labs(title="b", y="Kappa", x="Osc. rate (Hz)") +
+  labs(title="b", y="Rel. kappa", x="Osc. rate (Hz)") +
   scale_color_manual(
@@
     guide=FALSE) +
+  geom_hline(yintercept=0, size=0.2) +
   theme_classic() +
+  # ylim(0, .35) +
   theme(plot.title = element_text(hjust = -.5, size=18, face="bold")) -> p1
@@
   group_by(osc_rate, Ca_target) %>% 
-  summarise(M=mean(rate_k), SD=sd(rate_k)) -> tmp2
+  summarise(M=mean(rate_k - rate_ref), SD=sd(rate_k - rate_ref)) -> tmp2
 
@@
   geom_errorbar(aes(ymin=M - SD, ymax=M + SD), alpha=0.5, width=.1, size=0.4)  +
-  labs(title="a", y="Pop. rate (Hz)", x="Osc. rate (Hz)") +
+  labs(title="a", y="Rel. rate (Hz)", x="Osc. rate (Hz)") +
   geom_hline(yintercept=0, size=0.2) +

### 2018-11-10 resistingrhythm/neurons.py
Tweaked G/g intial values and re-balanced Na/K conductances.
This removed rhe AHP spike seen in exp20* and exp21*

@@ -88,29 +88,33 @@ def HHH(time,
     Et = 20 * mvolt
     Cm = 1 * uF  # /cm2
 
-    g_Na = 100 * msiemens
-    g_K = 80 * msiemens
-    g_KCa = 40 * msiemens
-    g_Ca = 0.01 * msiemens
     g_l = 1.0 * msiemens
 
     V_K = -100 * mV  # was 100, changed to match LeMasson
     V_l = -70 * mV
     V_Na = 50 * mV
 
-    # Ca + homeo specific
+    # Ca and Homeostasis values from 
+    # Siegel, M., Marder, E.V.E. & Abbott, L.F., 1994. Activity-dependent 
+    # current distributions in model neurons. , 91(November), pp.11308-11312.
+    # Who modeled a hippocampul neuron.
+
+    # d[Ca]/dt
     delta = 0.6 * umolar  # TODO: was umolar?
     k = 1 / (200.0 * msecond)
     gamma = -4.7e-2 * (mmolar / mamp / msecond)
-
     V_Ca = 150 * mV
     V1 = -50 * mV
     V2 = 10 * mV
+    g_Ca = 0.03 * msiemens
 
-    G_Ca = 3 * msiemens
+    # dg/dt 
     G_Na = 360 * msiemens
-    G_K = 180 * msiemens
-    G_KCa = 90 * msiemens
+    G_K = 120 * msiemens  # Try 90?
+    G_KCa = 60 * msiemens
+    g_Na = G_Na / 2
+    g_K = G_K / 2
+    g_KCa = G_KCa / 2
 
     # ----------------------------------------------------
     eqs = """
@@ -153,7 +157,8 @@ def HHH(time,
     if homeostasis:
         eqs += """ 
         dg_Na/dt = (1 / tau_h) * (G_Na / (1 + exp(1 * (Ca - Ca_target)/delta)) - g_Na) : siemens 
-        dg_Ca/dt = (1 / tau_h) * (G_Ca / (1 + exp(1 * (Ca - Ca_target)/delta)) - g_Ca) : siemens 
+        # dg_Ca/dt = (1 / tau_h) * (G_Ca / (1 + exp(1 * (Ca - Ca_target)/delta)) - g_Ca) : siemens 
+        g_Ca : siemens
         dg_K/dt = (1 / tau_h) * (G_K / (1 + exp(-1 * (Ca - Ca_target)/delta)) - g_K) : siemens 
[…]

### 2018-11-12 resistingrhythm/analysis/paper_figures_v4.Rmd
Added plots exp22*

---
title: "Analysis : exp220 - 228 (Nov 2018, for J Neurophys draft 2018)"
output: html_notebook
---

```{r, message=FALSE}
library(tidyverse)
library(gridExtra)
library(grid)
library(ggpubr)
library(cowplot)

data_path <- "~/Code/resistingrhythm/data/"
```

# Load all data

```{r, message=FALSE}
# -----------------------------------------------------------------------
# 16: Burst E, with H
exp_code <- 224
osc_codes <- c(100, 101, 102, 103, 104, 105, 110, 115, 120, 125, 130, 135, 140, 145, 150, 155, 160)
osc_rates <- c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0, 3.5, 4.0, 4.5, 5.0, 5.5, 6.0)
stim_codes <- c(3, 4) # 4

results224 <- NULL
for(i in 1:length(osc_codes)){
  for(s_c in stim_codes){
    o_c <- osc_codes[i]
    o_r <- osc_rates[i]

    # Load the csv
    df <- read_csv(paste(data_path, 
                         "exp", as.character(exp_code), 
                         "_stim", as.character(s_c), 
                         "_burst", as.character(o_c),
                         ".csv", sep=""))

    # Add metadata
    df$osc_code <- rep(o_c, nrow(df))
    df$osc_rate <- rep(o_r, nrow(df))
    df$stim_code <- rep(s_c, nrow(df))
    df$synapse <- rep("Excitatory", nrow(df))
    results224 <- rbind(results224, df)
  }
}

results224 %>%
  filter(rate_k > 0) -> results224

# -----------------------------------------------------------------------
# 15: Sustained E, with H
exp_code <- 221
osc_codes <- c(100, 101, 102, 103, 104, 105, 110, 115, 120, 125, 130, 135, 140, 145, 150, 155, 160)
osc_rates <- c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0, 3.5, 4.0, 4.5, 5.0, 5.5, 6.0)
stim_codes <- c(3, 4)

results221 <- NULL
for(i in 1:length(osc_codes)){
  for(s_c in stim_codes){
    o_c <- osc_codes[i]
    o_r <- osc_rates[i]

    # Load the csv
    df <- read_csv(paste(data_path, 
                         "exp", as.character(exp_code), 
                         "_stim", as.character(s_c), 
                         "_osc", as.character(o_c),
                         ".csv", sep=""))

    # Add metadata
    df$osc_code <- rep(o_c, nrow(df))
    df$osc_rate <- rep(o_r, nrow(df))
    df$synapse <- rep("Excitatory", nrow(df))
    df$stim_code <- rep(s_c, nrow(df))

    results221 <- rbind(results221, df)
  }
}

results221 %>%
  filter(rate_k > 0) -> results221

# -----------------------------------------------------------------------
# 22: Sustained E, with NO H
exp_code <- 220
osc_codes <- c(100, 101, 102, 103, 104, 105, 110, 115, 120, 125, 130, 135, 140, 145, 150, 155, 160)
osc_rates <- c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0, 3.5, 4.0, 4.5, 5.0, 5.5, 6.0)
stim_codes <- c(3, 4)

results220 <- NULL
for(i in 1:length(osc_codes)){
  for(s_c in stim_codes){
    o_c <- osc_codes[i]
    o_r <- osc_rates[i]

    # Load the csv
    df <- read_csv(paste(data_path, 
                         "exp", as.character(exp_code), 
                         "_stim", as.character(s_c), 
                         "_osc", as.character(o_c),
                         ".csv", sep=""))

    # Add metadata
    df$osc_code <- rep(o_c, nrow(df))
    df$osc_rate <- rep(o_r, nrow(df))
    df$stim_code <- rep(s_c, nrow(df))
    df$synapse <- rep("Excitatory", nrow(df))

    results220 <- rbind(results220, df)
  }
}

results220 %>%
  filter(rate_k > 0) -> results220

# -----------------------------------------------------------------------
# 21: Sustained I, with H
exp_code <- 223
osc_codes <- c(100, 101, 102, 103, 104, 105, 110, 115, 120, 125, 130, 135, 140, 145, 150, 155, 160)
osc_rates <- c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0, 3.5, 4.0, 4.5, 5.0, 5.5, 6.0)
stim_codes <- c(3, 4)

results223 <- NULL
for(i in 1:length(osc_codes)){
  for(s_c in stim_codes){
    o_c <- osc_codes[i]
    o_r <- osc_rates[i]

    # Load the csv
    df <- read_csv(paste(data_path, 
                         "exp", as.character(exp_code), 
                         "_stim", as.character(s_c), 
                         "_osc", as.character(o_c),
                         ".csv", sep=""))

    # Add metadata
    df$osc_code <- rep(o_c, nrow(df))
    df$osc_rate <- rep(o_r, nrow(df))
    df$stim_code <- rep(s_c, nrow(df))
    df$synapse <- rep("Inhibitory", nrow(df))

    results223 <- rbind(results223, df)
  }
}

results223 %>%
  filter(rate_k > 0) -> results223

# -----------------------------------------------------------------------
# 23: Sustained I, with NO H
exp_code <- 222
osc_codes <- c(100, 101, 102, 103, 104, 105, 110, 115, 120, 125, 130, 135, 140, 145, 150, 155, 160)
osc_rates <- c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0, 3.5, 4.0, 4.5, 5.0, 5.5, 6.0)
stim_codes <- c(3, 4)

results222 <- NULL
for(i in 1:length(osc_codes)){
  for(s_c in stim_codes){
    o_c <- osc_codes[i]
    o_r <- osc_rates[i]

    # Load the csv
    df <- read_csv(paste(data_path, 
                         "exp", as.character(exp_code), 
                         "_stim", as.character(s_c), 
                         "_osc", as.character(o_c),
                         ".csv", sep=""))

    # Add metadata
    df$osc_code <- rep(o_c, nrow(df))
    df$osc_rate <- rep(o_r, nrow(df))
    df$stim_code <- rep(s_c, nrow(df))
    df$synapse <- rep("Inhibitory", nrow(df))

    results222 <- rbind(results222, df)
  }
}

results222 %>%
  filter(rate_k > 0) -> results222

# -----------------------------------------------------------------------
# 30: Burst I, with H
# HERE
exp_code <- 227
osc_codes <- c(100, 101, 102, 103, 104, 105, 110, 115, 120, 125, 130, 135, 140, 145, 150, 155, 160)
osc_rates <- c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0, 3.5, 4.0, 4.5, 5.0, 5.5, 6.0)
stim_codes <- c(3, 4)

results227 <- NULL
for(i in 1:length(osc_codes)){
  for(s_c in stim_codes){
    o_c <- osc_codes[i]
    o_r <- osc_rates[i]

    # Load the csv
    df <- read_csv(paste(data_path, 
                         "exp", as.character(exp_code), 
                         "_stim", as.character(s_c), 
                         "_burst", as.character(o_c),
                         ".csv", sep=""))

    # Add metadata
    df$osc_code <- rep(o_c, nrow(df))
    df$osc_rate <- rep(o_r, nrow(df))
    df$stim_code <- rep(s_c, nrow(df))
    df$synapse <- rep("Inhibitory", nrow(df))

    results227 <- rbind(results227, df)
  }
}

results227 %>%
  filter(rate_k > 0) -> results227

# -----------------------------------------------------------------------
# Calcium exp, E, sustained
exp_code <- 228
osc_codes <- c(105, 115, 125, 135, 145, 155)
osc_rates <- c(0.5, 1.5, 2.5, 3.5, 4.5, 5.5)
stim_codes <- c(3)

ca_targets <- c(0.0026, 0.0028, 0.0032, 0.0034)

results228 <- NULL
for(i in 1:length(osc_codes)){
  for(s_c in stim_codes){
    for(ca in ca_targets){
      o_c <- osc_codes[i]
      o_r <- osc_rates[i]

      # Load the csv
      df <- read_csv(paste(data_path,
                           "exp", as.character(exp_code),
                           "_stim", as.character(s_c),
                           "_osc", as.character(o_c),
                           "_ca", as.character(ca),
                           ".csv", sep=""))

      # Add metadata
      df$osc_code <- rep(o_c, nrow(df))
      df$osc_rate <- rep(o_r, nrow(df))
      df$stim_code <- rep(s_c, nrow(df))
      df$Ca_target <- rep(ca, nrow(df))
      df$synapse <- rep("Excitatory", nrow(df))

      results228 <- rbind(results228, df)
    }
  }
}

# -----------------------------------------------------------------------
# # Add default Ca value, from exp
exp_code <- 221
osc_codes <- c(105, 115, 125, 135, 145, 155)
osc_rates <- c(0.5, 1.5, 2.5, 3.5, 4.5, 5.5)
stim_codes <- c(3)
ca_targets <- c(0.003, 0.003, 0.003, 0.003)

df <- NULL
for(i in 1:length(osc_codes)){
  for(s_c in stim_codes){
    for(ca in ca_targets){

      o_c <- osc_codes[i]
      o_r <- osc_rates[i]

      # Load the csv
      df <- read_csv(paste(data_path,
                           "exp", as.character(exp_code),
                           "_stim", as.character(s_c),
                           "_osc", as.character(o_c),
                           ".csv", sep=""))

      # Add metadata
      df$osc_code <- rep(o_c, nrow(df))
      df$osc_rate <- rep(o_r, nrow(df))
      df$stim_code <- rep(s_c, nrow(df))
      df$Ca_target <- rep(ca, nrow(df))
      df$synapse <- rep("Excitatory", nrow(df))

      results228 <- rbind(results228, df)
    }
  }
}

# Clean up
rm(df, exp_code, i, o_c, o_r, osc_codes, osc_rates, s_c, stim_codes)
```

# Figure: Main results
```{r fig.height=2.25, fig.width=5.5}
# Kappa no H, E
bind_rows(results220, results222) %>%
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  mutate(kappa_coord=replace(kappa_coord, rate_k < 1, NA)) %>% 
  group_by(synapse, osc_rate) %>% 
  mutate(M=mean(kappa_coord), SD=sd(kappa_coord)) %>% 
  ggplot(mapping=aes(x=osc_rate, y=M, group=osc_rate, color=synapse)) +
    geom_point(size=0.8) +
    geom_errorbar(mapping=aes(x=osc_rate, ymin=M - SD, ymax=M + SD, color=synapse),
                  width=.15, size=0.2) +
    scale_color_manual(values=c("black", "grey")) +
    lims(y=c(0.0, 0.2)) +
    labs(title="d.", y="Kappa", x="Osc. rate (Hz)") +
    theme_classic() +
    theme(plot.title = element_text(hjust = -.3, size=18, face="bold"),
          legend.position="none") -> p1

# Kappa with H, E
bind_rows(results221, results223) %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  mutate(kappa_coord=replace(kappa_coord, rate_k < 1, NA)) %>%
  group_by(synapse, osc_rate) %>% 
  mutate(M=mean(kappa_coord), SD=sd(kappa_coord)) %>% 
  ggplot(mapping=aes(x=osc_rate, y=M, group=osc_rate, color=synapse)) +
    geom_point(size=0.8) +
    geom_errorbar(mapping=aes(x=osc_rate, ymin=M - SD, ymax=M + SD, color=synapse),
                  width=.15, size=0.2) +
    scale_color_manual(values=c("black", "grey")) +
    lims(y=c(0.0, 0.2)) +
    labs(title="e.", y="Kappa", x="Osc. rate (Hz)") +
    theme_classic() +
    theme(plot.title = element_text(hjust = -.3, size=18, face="bold"),
          legend.position="none") -> p2

# Rate no H, E
bind_rows(results220, results222) %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  mutate(kappa_coord=replace(kappa_coord, rate_k < 1, NA)) %>% 
  group_by(synapse, osc_rate) %>% 
  mutate(M=mean(rate_k), SD=sd(rate_k)) %>% 
  ggplot(mapping=aes(x=osc_rate, y=M, group=osc_rate, color=synapse)) +
  geom_point(size=0.8) +
  geom_errorbar(mapping=aes(x=osc_rate, ymin=M - SD, ymax=M + SD, color=synapse),
                width=.15, size=0.2) +
  scale_color_manual(values=c("black", "grey")) +
  labs(title="a.", y="Pop. rate (Hz)", x="Osc. rate (Hz)") +
  lims(y=c(0.0, 175.0)) +
  guides(fill = guide_legend(override.aes = list(shape = 15, size = 7, alpha=0.8))) +
  theme_classic() +
  theme(plot.title = element_text(hjust = -.3, size=18, face="bold"),
        legend.position="none") -> p3

# -
# Rate, with H, E
bind_rows(results221, results223) %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  mutate(kappa_coord=replace(kappa_coord, rate_k < 1, NA)) %>%
  group_by(synapse, osc_rate) %>% 
  mutate(M=mean(rate_k), SD=sd(rate_k)) %>% 
  ggplot(mapping=aes(x=osc_rate, y=M, group=osc_rate, color=synapse)) +
  geom_point(size=0.8) +
  geom_errorbar(mapping=aes(x=osc_rate, ymin=M - SD, ymax=M + SD, color=synapse), 
                width=.15, size=0.2) +
  scale_color_manual(values=c("black", "grey")) +
  labs(title="b.", y="Pop. rate (Hz)", x="Osc. rate (Hz)") +
  lims(y=c(0.0, 175.0)) +
  theme_classic() +
  theme(
    legend.position = c(-.6, -0.2),
    legend.background = element_rect(colour ="black"),
    legend.key.size = unit(.5, "cm"),
    legend.title=element_blank(),
    plot.title = element_text(hjust = -.3, size=18, face="bold")) -> p4

# --------------------------------------------------------
# Bursts
bind_rows(results224, results227)  %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  mutate(kappa_coord=replace(kappa_coord, rate_k < 1, NA)) %>%
  group_by(synapse, osc_rate) %>% 
  mutate(M=mean(kappa_coord), SD=sd(kappa_coord)) %>% 
  ggplot(mapping=aes(x=osc_rate, y=M, group=osc_rate, color=synapse)) +
    geom_point(size=0.8) +
    geom_errorbar(mapping=aes(x=osc_rate, ymin=M - SD, ymax=M + SD, color=synapse), 
                width=.15, size=0.2) +
    scale_color_manual(values=c("darkgoldenrod3", "goldenrod1")) +
    lims(y=c(0.0, 0.2)) +
    labs(title="f.", y="Kappa", x="Osc. rate (Hz)") +
    theme_classic() +
    geom_hline(yintercept=0, size=0.2) +
    theme(plot.title = element_text(hjust = -.3, size=18, face="bold"),
          legend.position="none") -> p5

# 
# Rate
bind_rows(results224, results227)  %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  mutate(kappa_coord=replace(kappa_coord, rate_k < 1, NA)) %>%
  group_by(synapse, osc_rate) %>% 
  mutate(M=mean(rate_k), SD=sd(rate_k)) %>% 
  ggplot(mapping=aes(x=osc_rate, y=M, group=osc_rate, color=synapse)) +
    geom_point(size=0.8) +
    geom_errorbar(mapping=aes(x=osc_rate, ymin=M - SD, ymax=M + SD, color=synapse), 
                width=.15, size=0.2) +
    scale_color_manual(values=c("darkgoldenrod3", "goldenrod1")) +
    labs(title="c.", y="Pop. rate (Hz)", x="Osc. rate (Hz)") +
    lims(y=c(0.0, 175.0)) +
    theme_classic() +
  theme(
    legend.position = c(1.35, .5),
    legend.background = element_rect(colour ="black"),
    legend.key.size = unit(.5, "cm"),
    legend.title=element_blank(),
    plot.title = element_text(hjust = -.3, size=18, face="bold")) -> p6

# -
# Rate: burst v sustained
tmp3 <- results221
tmp3$osc_mode <- rep("Sustained", nrow(results221))
tmp4 <- results224
tmp4$osc_mode <- rep("Burst", nrow(results224))

bind_rows(tmp3, tmp4) %>% 
  filter(synapse=="Excitatory") %>% 
  ggplot(aes(x=osc_mode, y=rate_k, color=osc_mode)) +
  geom_point(size=-1, aes(fill=osc_mode)) +
  geom_boxplot(notch = TRUE, width=0.4,  outlier.size=0.05, outlier.alpha=0.5, show.legend=FALSE) +
  labs(title="g.", y="Pop. rate (Hz)", x="") +
  theme_classic() +
  scale_fill_manual(values=c("darkgoldenrod3", "black"), name="Oscillation") +
  scale_color_manual(values=c("darkgoldenrod3", "black"), name="Oscillation") +
  stat_compare_means(method="wilcox.test", label="p.signif", 
                     label.x=1.3, size=3, show.legend=FALSE) +
  lims(y=c(0.0, 175.0)) +
  guides(fill = guide_legend(override.aes = list(shape = 15, size = 7, alpha=0.8))) +
  theme(plot.title = element_text(hjust = -.1, size=18, face="bold"), 
          legend.position="none",
          axis.text.x = element_text(angle = 70, hjust = 1)) -> p7

# -
layout_matrix <- rbind(
  c(NA, 8, 8, NA, 9, 9, 9, 9, NA),
  c(11, 3, 3, NA, 4, 4, 6, 6, NA),
  c(11, 3, 3, NA, 4, 4, 6, 6, NA),
  c(11, 3, 3, NA, 4, 4, 6, 6, NA),
  c(11, 3, 3, NA, 4, 4, 6, 6, 7),
  c(10, 1, 1, NA, 2, 2, 5, 5, 7), 
  c(10, 1, 1, NA, 2, 2, 5, 5, 7), 
  c(10, 1, 1, NA, 2, 2, 5, 5, 7), 
  c(10, 1, 1, NA, 2, 2, 5, 5, 7)
)

p8 <- textGrob("No homeostatsis")
p9 <- textGrob("Homeostatsis")
p10 <- textGrob("Coordination")
p11 <- textGrob("Excitability")
p <- grid.arrange(p1, p2, p3, p4, p5, p6, p7, p8, p9, p10, p11, layout_matrix=layout_matrix)
plot(p)

# -
png(file="fig2.png", bg="white", width=9.0, height=4.5, unit="in", res=300)
plot(p)
dev.off()
```

```{r}
print(wilcox.test(x=tmp3$rate_k, y=tmp4$rate_k))
```

# Figure: Kap v Err
```{r, fig.width=3.25, fig.height=1.1}
# -
results220 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  mutate(kappa_coord=replace(kappa_coord, rate_k < 1, NA)) %>%
  group_by(osc_rate) %>% 
  mutate(
    M_error=mean(abs_error), SD_error=sd(abs_error), 
    M_kappa=mean(kappa_coord), SD_kappa=sd(kappa_coord)) -> tmp1
tmp1$mode <- rep("No homeostatsis", nrow(tmp1))
results221 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  mutate(kappa_coord=replace(kappa_coord, rate_k < 1, NA)) %>%
  group_by(osc_rate) %>% 
  mutate(
    M_error=mean(abs_error), SD_error=sd(abs_error), 
    M_kappa=mean(kappa_coord), SD_kappa=sd(kappa_coord)) -> tmp2
tmp2$mode <- rep("Homeostatsis", nrow(tmp2))

bind_rows(tmp1, tmp2) %>% 
ggplot(mapping=aes(x=M_kappa, y=M_error, color=mode)) +
  # No H
  geom_point(size=0.2) +
  geom_errorbar(mapping=aes(x=M_kappa, ymin=M_error - SD_error, ymax=M_error + SD_error),
                width=0.004, size=0.2) +
  geom_errorbarh(mapping=aes(y=M_error, xmin=M_kappa - SD_kappa, xmax=M_kappa + SD_kappa),
                 height=0.002, size=0.2) +
  scale_color_manual(values=c("black", "darkgrey")) +
  labs(title="a.", y="Log error (s)", x="Kappa") +
  lims(x=c(0.0, 0.25)) +
  scale_y_log10() + annotation_logticks() +
  theme_classic() + 
  theme(plot.title = element_text(hjust = -.3, size=18, face="bold"),
        legend.position = "none") -> p1

# -
results220 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  mutate(kappa_coord=replace(kappa_coord, rate_k < 1, NA)) %>%
  group_by(osc_rate) %>% 
  mutate(
    M_error=mean(abs_error), SD_error=sd(abs_error), 
    M_kappa=mean(kappa_coord), SD_kappa=sd(kappa_coord)) -> tmp1
tmp1$mode <- rep("No homeostatsis", nrow(tmp1))
results224 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  mutate(kappa_coord=replace(kappa_coord, rate_k < 1, NA)) %>%
  group_by(osc_rate) %>% 
  mutate(
    M_error=mean(abs_error), SD_error=sd(abs_error), 
    M_kappa=mean(kappa_coord), SD_kappa=sd(kappa_coord)) -> tmp2
tmp2$mode <- rep("Homeostatsis", nrow(tmp2))

bind_rows(tmp1, tmp2) %>% 
ggplot(mapping=aes(x=M_kappa, y=M_error, color=mode)) +
  geom_point(size=0.2) +
  geom_errorbar(mapping=aes(x=M_kappa, ymin=M_error - SD_error, ymax=M_error + SD_error),
                width=0.004, size=0.2) +
  geom_errorbarh(mapping=aes(y=M_error, xmin=M_kappa - SD_kappa, xmax=M_kappa + SD_kappa),
                 height=0.002, size=0.2) +
  scale_color_manual(values=c("black", "darkgrey")) +
  labs(title="b.", y="Log error (s)", x="Kappa") +
  lims(x=c(0.0, 0.25)) + annotation_logticks() +
  theme_classic() + 
  scale_y_log10() +
  theme(plot.title = element_text(hjust = -.3, size=18, face="bold"),
        legend.title=element_blank()) -> p2

# -
layout_matrix <- rbind(
  c(3, 3, 4, 4, NA),
  c(1, 1, 2, 2, 2),
  c(1, 1, 2, 2, 2),
  c(1, 1, 2, 2, 2),
  c(1, 1, 2, 2, 2)
)
p3 <- textGrob("Sustained")
p4 <- textGrob("Burst", gp=gpar(col="darkgoldenrod3"))

grid.arrange(p1, p2, p3, p4, layout_matrix=layout_matrix)
```

# Figure: Calcium control
```{r, fig.width=2.4, fig.height=1.8}
# -
# With H, E
# Var
results228 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  mutate(kappa_coord=replace(kappa_coord, rate_k < 1, NA)) %>%
  group_by(osc_rate, Ca_target) %>% 
  summarise(M=mean(kappa_coord), SD=sd(kappa_coord)) -> tmp1

tmp1 %>% 
  ggplot(aes(x=osc_rate, y=M, color=factor(Ca_target, 
                                           levels = c(0.0026, 0.0028, 0.003, 0.0032, 0.0034)))) +
  geom_line(size=0.8) +
  geom_point(size=1.5) +
  geom_errorbar(aes(ymin=M - SD, ymax=M + SD), alpha=0.5, width=.1, size=0.4)  +
  labs(title="b.", y="Kappa", x="Osc. rate (Hz)") +
  scale_color_manual(
    values=c("plum1", "plum2", "black", "plum3", "plum4"), 
    guide=FALSE) +
  theme_classic() +
  # ylim(0, .35) +
  theme(plot.title = element_text(hjust = -.5, size=18, face="bold")) -> p1

# Rate
results228 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  mutate(kappa_coord=replace(kappa_coord, rate_k < 1, NA)) %>%
  group_by(osc_rate, Ca_target) %>% 
  summarise(M=mean(rate_k), SD=sd(rate_k)) -> tmp2

tmp2 %>% 
ggplot(aes(x=osc_rate, y=M, color=factor(Ca_target, levels = c(0.0026, 0.0028, 0.003, 0.0032, 0.0034)))) +
  geom_line(size=0.8) +
  geom_point(size=1.5) +
  geom_errorbar(aes(ymin=M - SD, ymax=M + SD), alpha=0.5, width=.1, size=0.4)  +
  labs(title="a.", y="Pop. rate (Hz)", x="Osc. rate (Hz)") +
  scale_color_manual(
    values=c("plum1", "plum2", "black", "plum3", "plum4"), 
    name="Target [Ca]\n(mmolar)") +
  # lims(y=c(0, .01)) 
  # guides(col = guide_legend(ncol = 2)) +
  theme_classic() +
  theme(
    plot.title = element_text(hjust = -.5, size=18, face="bold"),
    legend.position = c(1.35, -0.5),
    legend.background = element_rect(colour ="black"),
    legend.key.size = unit(.4, "cm")) -> p2

p3 <- textGrob("Coordination")
p4 <- textGrob("Excitability")

layout_matrix <- rbind(
  c(6, 6, 6, 6), 
  c(4, 2, 2, 5),
  c(4, 2, 2, 5),
  c(4, 2, 2, 5),
  c(4, 2, 2, 5),
  c(3, 1, 1, 5),
  c(3, 1, 1, 5),
  c(3, 1, 1, 5), 
  c(3, 1, 1, 5) 
)

p5 <- nullGrob()
p6 <- textGrob("Target Calcium")
p <- grid.arrange(p1, p2, p3, p4, p5, p6,layout_matrix=layout_matrix)
plot(p)

# -
# png(file="fig5.png", bg="white", width=4.2, height=3.8, unit="in", res=300)
# plot(p)
# dev.off()

rm(p1, p2, p3, p4, p5, tmp1, tmp2)
```

### 2018-11-13 resistingrhythm/analysis/paper_figures_v4.Rmd
Tweak v4 plots

@@
 # Load all data
-
 ```{r, message=FALSE}
@@
   labs(title="a.", y="Pop. rate (Hz)", x="Osc. rate (Hz)") +
-  lims(y=c(0.0, 175.0)) +
+  lims(y=c(0.0, 180.0)) +
   guides(fill = guide_legend(override.aes = list(shape = 15, size = 7, alpha=0.8))) +
@@
   labs(title="b.", y="Pop. rate (Hz)", x="Osc. rate (Hz)") +
-  lims(y=c(0.0, 175.0)) +
+  lims(y=c(0.0, 180.0)) +
   theme_classic() +
@@
 # --------------------------------------------------------
-# Bursts
 bind_rows(results224, results227)  %>% 
@@
 
-# 
-# Rate
+# -
 bind_rows(results224, results227)  %>% 
@@
     labs(title="c.", y="Pop. rate (Hz)", x="Osc. rate (Hz)") +
-    lims(y=c(0.0, 175.0)) +
+    lims(y=c(0.0, 180.0)) +
     theme_classic() +
@@
 # -
-# Rate: burst v sustained
 tmp3 <- results221
@@
                      label.x=1.3, size=3, show.legend=FALSE) +
-  lims(y=c(0.0, 175.0)) +
+  lims(y=c(0.0, 180.0)) +
   guides(fill = guide_legend(override.aes = list(shape = 15, size = 7, alpha=0.8))) +
@@
           axis.text.x = element_text(angle = 70, hjust = 1)) -> p7
+
+# -
+p8 <- textGrob("No homeostatsis")
+p9 <- textGrob("Homeostatsis")
+p10 <- textGrob("Coordination")
+p11 <- textGrob("Excitability")
 
@@
 )
-
-p8 <- textGrob("No homeostatsis")
-p9 <- textGrob("Homeostatsis")
-p10 <- textGrob("Coordination")
-p11 <- textGrob("Excitability")
-p <- grid.arrange(p1, p2, p3, p4, p5, p6, p7, p8, p9, p10, p11, layout_matrix=layout_matrix)
-plot(p)
+grid.arrange(p1, p2, p3, p4, p5, p6, p7, p8, p9, p10, p11, layout_matrix=layout_matrix)
 
 # -
-png(file="fig2.png", bg="white", width=9.0, height=4.5, unit="in", res=300)
-plot(p)
-dev.off()
+# png(file="fig2.png", bg="white", width=9.0, height=4.5, unit="in", res=300)
+# plot(p)
+# dev.off()
 ```
@@
 ggplot(mapping=aes(x=M_kappa, y=M_error, color=mode)) +
-  # No H
   geom_point(size=0.2) +
@@
 # -
+p3 <- textGrob("Sustained")
+p4 <- textGrob("Burst", gp=gpar(col="darkgoldenrod3"))
+
+# -
 layout_matrix <- rbind(
@@
 )
-p3 <- textGrob("Sustained")
-p4 <- textGrob("Burst", gp=gpar(col="darkgoldenrod3"))
-
 grid.arrange(p1, p2, p3, p4, layout_matrix=layout_matrix)
@@
 # -
-# With H, E
-# Var
 results228 %>% 
@@
   theme_classic() +
-  # ylim(0, .35) +
   theme(plot.title = element_text(hjust = -.5, size=18, face="bold")) -> p1
 
-# Rate
+# -
 results228 %>% 
@@
 tmp2 %>% 
-ggplot(aes(x=osc_rate, y=M, color=factor(Ca_target, levels = c(0.0026, 0.0028, 0.003, 0.0032, 0.0034)))) +
+ggplot(aes(x=osc_rate, y=M, color=factor(Ca_target, 
+                                         levels = c(0.0026, 0.0028, 0.003, 0.0032, 0.0034)))) +
   geom_line(size=0.8) +
@@
     name="Target [Ca]\n(mmolar)") +
-  # lims(y=c(0, .01)) 
-  # guides(col = guide_legend(ncol = 2)) +
   theme_classic() +
@@
 
+# -
 p3 <- textGrob("Coordination")
@@
 
+# -
 layout_matrix <- rbind(
@@
 )
-
 p5 <- nullGrob()
 p6 <- textGrob("Target Calcium")
-p <- grid.arrange(p1, p2, p3, p4, p5, p6,layout_matrix=layout_matrix)
-plot(p)
+grid.arrange(p1, p2, p3, p4, p5, p6, layout_matrix=layout_matrix)
 
@@
 
-rm(p1, p2, p3, p4, p5, tmp1, tmp2)
+rm(p1, p2, p3, p4, p5, p6, tmp1, tmp2)
 ```

### 2018-11-17 resistingrhythm/analysis/exp229.Rmd
exp229 analysis intial commit

---
title: "Analysis : exp229 analysis"
output: html_notebook
---

```{r, message=FALSE}
library(tidyverse)
library(gridExtra)
library(grid)
library(ggpubr)
library(cowplot)

data_path <- "~/Code/resistingrhythm/data/"
```

# Load all data
```{r, message=FALSE}
# -----------------------------------------------------------------------
# 16: Burst E, with H
tau_h <- 4.0
exp_code <- 229
run_time_codes <- c('1.0', '2.0', '3.0', '4.0', '5.0', '6.0', '7.0', '8.0')
onset_time_codes <- c('0.5', '1.5', '2.5', '3.5', '4.5', '5.5', '6.5', '7.5')
freq_codes <- c('8', '12', '16', '20', '24', '28')
osc_rate_codes <- c('0', '2', '4', '6')

results229 <- NULL
for(i in 1:length(run_time_codes)){
  for(f_c in freq_codes){
    for(o_r in osc_rate_codes){
      r_t <- run_time_codes[i]
      o_t <- onset_time_codes[i]

      # Load the csv
      df <- read_csv(paste(data_path, 
                         "exp", as.character(exp_code), 
                         "_T", r_t, 
                         "_t", o_t,
                         "_r", o_r,
                         "_f", f_c,
                         ".csv", sep=""))  
      # Add metadata
      df$run_time <- rep(r_t, nrow(df))
      df$frac_tau_h <- rep(as.character(as.numeric(r_t)/tau_h, nrow(df)))
      df$onset_time <- rep(o_t, nrow(df))
      df$osc_rate <- rep(o_r, nrow(df))
      df$freq <- rep(f_c, nrow(df))
      df$synapse <- rep("Excitatory", nrow(df))
      results229 <- rbind(results229, df)
    }
  }
}

results229$freq <- factor(results229$freq, levels = freq_codes)
results229$run_time <- factor(results229$run_time, levels = run_time_codes)
results229$osc_rate <- factor(results229$osc_rate, levels = osc_rate_codes)
```

```{r, fig.width=1.5, fig.height=1.2}
null_rate <- mean(filter(results229, osc_rate == "0")$rate_k)
results229 %>% 
  filter(osc_rate != "0") %>%
  ggplot(aes(x=frac_tau_h, y=rate_k)) +
    geom_boxplot() +
    theme_classic2() +
    scale_color_brewer(palette="PuOr", direction=-1) +
    labs(x="Frac. tau_h", y="Pop. rate") +
    theme(legend.position = "none")
```

```{r}
results229 %>% 
  filter(osc_rate == "2") %>% 
  ggplot(aes(x=freq, y=rate_k, color=frac_tau_h)) +
  geom_boxplot() +
  theme_classic2() +
  scale_color_brewer(palette="BrBG", direction=-1) +
  labs(x="Frequency (Hz)", y="Pop. rate") 
```

```{r}
results229 %>% 
  filter(osc_rate != "0") %>% 
  ggplot(aes(x=osc_rate, y=rate_k, color=frac_tau_h)) +
  geom_boxplot() +
  theme_classic2() +
  scale_color_brewer(palette="BrBG", direction=-1) +
  labs(x="Osc. rate", y="Pop. rate") 
```

### 2018-11-17 resistingrhythm/analysis/paper_figures_v4.Rmd
Ongoing fig design for the paper

@@
     df$stim_code <- rep(s_c, nrow(df))
-    df$synapse <- rep("Excitatory", nrow(df))
+    df$synapse <- rep("AMPA", nrow(df))
     results224 <- rbind(results224, df)
@@
     df$osc_rate <- rep(o_r, nrow(df))
-    df$synapse <- rep("Excitatory", nrow(df))
+    df$synapse <- rep("AMPA", nrow(df))
     df$stim_code <- rep(s_c, nrow(df))
@@
     df$stim_code <- rep(s_c, nrow(df))
-    df$synapse <- rep("Excitatory", nrow(df))
+    df$synapse <- rep("AMPA", nrow(df))
 
@@
     df$stim_code <- rep(s_c, nrow(df))
-    df$synapse <- rep("Inhibitory", nrow(df))
+    df$synapse <- rep("GABA", nrow(df))
 
@@
       df$Ca_target <- rep(ca, nrow(df))
-      df$synapse <- rep("Excitatory", nrow(df))
+      df$synapse <- rep("AMPA", nrow(df))
 
@@
 # Figure: Main results
-```{r fig.height=2.25, fig.width=5.5}
+```{r fig.height=2.25, fig.width=6}
 # Kappa no H, E
@@
     lims(y=c(0.0, 0.2)) +
-    labs(title="d.", y="Kappa", x="Osc. rate (Hz)") +
-    theme_classic() +
+    labs(title="b.", y="Kappa", x="Osc. rate") +
+    theme_classic2() +
     theme(plot.title = element_text(hjust = -.3, size=18, face="bold"),
@@
     lims(y=c(0.0, 0.2)) +
-    labs(title="e.", y="Kappa", x="Osc. rate (Hz)") +
-    theme_classic() +
+    labs(title="d.", y="Kappa", x="Osc. rate") +
+    theme_classic2() +
     theme(plot.title = element_text(hjust = -.3, size=18, face="bold"),
@@
   scale_color_manual(values=c("black", "grey")) +
-  labs(title="a.", y="Pop. rate (Hz)", x="Osc. rate (Hz)") +
+  labs(title="a.", y="Pop. rate", x="Osc. rate") +
   lims(y=c(0.0, 180.0)) +
   guides(fill = guide_legend(override.aes = list(shape = 15, size = 7, alpha=0.8))) +
-  theme_classic() +
+  theme_classic2() +
   theme(plot.title = element_text(hjust = -.3, size=18, face="bold"),
@@
                 width=.15, size=0.2) +
-  scale_color_manual(values=c("black", "grey")) +
-  labs(title="b.", y="Pop. rate (Hz)", x="Osc. rate (Hz)") +
+  scale_color_manual(values=c("black", "grey"), name="Tonic") +
+  labs(title="c.", y="Pop. rate", x="Osc. rate") +
   lims(y=c(0.0, 180.0)) +
-  theme_classic() +
+  theme_classic2() +
   theme(
-    legend.position = c(-.6, -0.2),
+    legend.position = c(-.5, -0.2),
     legend.background = element_rect(colour ="black"),
     legend.key.size = unit(.5, "cm"),
-    legend.title=element_blank(),
     plot.title = element_text(hjust = -.3, size=18, face="bold")) -> p4
@@
     lims(y=c(0.0, 0.2)) +
-    labs(title="f.", y="Kappa", x="Osc. rate (Hz)") +
-    theme_classic() +
-    geom_hline(yintercept=0, size=0.2) +
+    labs(title="f.", y="Kappa", x="Osc. rate") +
+    theme_classic2() +
     theme(plot.title = element_text(hjust = -.3, size=18, face="bold"),
@@
                 width=.15, size=0.2) +
-    scale_color_manual(values=c("darkgoldenrod3", "goldenrod1")) +
-    labs(title="c.", y="Pop. rate (Hz)", x="Osc. rate (Hz)") +
+    scale_color_manual(values=c("darkgoldenrod3", "goldenrod1"), name="Burst") +
+    labs(title="e.", y="Pop. rate", x="Osc. rate") +
     lims(y=c(0.0, 180.0)) +
-    theme_classic() +
+    theme_classic2() +
   theme(
     legend.position = c(1.35, .5),
+    legend.title = element_text(colour = 'darkgoldenrod3'),
     legend.background = element_rect(colour ="black"),
     legend.key.size = unit(.5, "cm"),
-    legend.title=element_blank(),
     plot.title = element_text(hjust = -.3, size=18, face="bold")) -> p6
@@
 tmp3 <- results221
-tmp3$osc_mode <- rep("Sustained", nrow(results221))
+tmp3$osc_mode <- rep("Tonic", nrow(tmp3))
 tmp4 <- results224
-tmp4$osc_mode <- rep("Burst", nrow(results224))
+tmp4$osc_mode <- rep("Burst", nrow(tmp4))
 
-bind_rows(tmp3, tmp4) %>% 
-  filter(synapse=="Excitatory") %>% 
+tmp5 <- results223
+tmp5$osc_mode <- rep("Tonic", nrow(tmp5))
+tmp6 <- results227
+tmp6$osc_mode <- rep("Burst", nrow(tmp6))
+
+bind_rows(tmp3, tmp4, tmp5, tmp6) %>% 
+  # filter(synapse=="AMPA") %>% 
   ggplot(aes(x=osc_mode, y=rate_k, color=osc_mode)) +
@@
   geom_boxplot(notch = TRUE, width=0.4,  outlier.size=0.05, outlier.alpha=0.5, show.legend=FALSE) +
-  labs(title="g.", y="Pop. rate (Hz)", x="") +
-  theme_classic() +
-  scale_fill_manual(values=c("darkgoldenrod3", "black"), name="Oscillation") +
-  scale_color_manual(values=c("darkgoldenrod3", "black"), name="Oscillation") +
+  facet_grid(.~synapse) +
+  labs(title="g.", y="Pop. rate", x="") +
+  theme_classic2() +
+  scale_fill_manual(values=c("black", "black"), name="Oscillation") +
+  scale_color_manual(values=c("black", "black"), name="Oscillation") +
   stat_compare_means(method="wilcox.test", label="p.signif", 
                      label.x=1.3, size=3, show.legend=FALSE) +
-  lims(y=c(0.0, 180.0)) +
+  # lims(y=c(0.0, 180.0)) +
   guides(fill = guide_legend(override.aes = list(shape = 15, size = 7, alpha=0.8))) +
@@
           legend.position="none",
+          strip.background = element_blank(),
           axis.text.x = element_text(angle = 70, hjust = 1)) -> p7
@@
 p9 <- textGrob("Homeostatsis")
-p10 <- textGrob("Coordination")
+p10 <- textGrob("Synchrony")
 p11 <- textGrob("Excitability")
@@
 layout_matrix <- rbind(
-  c(NA, 8, 8, NA, 9, 9, 9, 9, NA),
-  c(11, 3, 3, NA, 4, 4, 6, 6, NA),
-  c(11, 3, 3, NA, 4, 4, 6, 6, NA),
-  c(11, 3, 3, NA, 4, 4, 6, 6, NA),
-  c(11, 3, 3, NA, 4, 4, 6, 6, 7),
-  c(10, 1, 1, NA, 2, 2, 5, 5, 7), 
-  c(10, 1, 1, NA, 2, 2, 5, 5, 7), 
-  c(10, 1, 1, NA, 2, 2, 5, 5, 7), 
-  c(10, 1, 1, NA, 2, 2, 5, 5, 7)
+  c(NA, 8, 8, 8, NA, 9, 9, 9, 9, 9, 9, NA, NA),
+  c(11, 3, 3, 3, NA, 4, 4, 4, 6, 6, 6, NA, NA),
+  c(11, 3, 3, 3, NA, 4, 4, 4, 6, 6, 6, NA, NA),
+  c(11, 3, 3, 3, NA, 4, 4, 4, 6, 6, 6, NA, NA),
+  c(11, 3, 3, 3, NA, 4, 4, 4, 6, 6, 6, 7, 7),
+  c(10, 1, 1, 1, NA, 2, 2, 2, 5, 5, 5, 7, 7), 
+  c(10, 1, 1, 1, NA, 2, 2, 2, 5, 5, 5, 7, 7), 
+  c(10, 1, 1, 1, NA, 2, 2, 2, 5, 5, 5, 7, 7), 
+  c(10, 1, 1, 1, NA, 2, 2, 2, 5, 5, 5, 7, 7)
 )
@@
 # -
-# png(file="fig2.png", bg="white", width=9.0, height=4.5, unit="in", res=300)
-# plot(p)
-# dev.off()
+png(file="fig2.png", bg="white", width=12.0, height=4.5, unit="in", res=300)
+grid.arrange(p1, p2, p3, p4, p5, p6, p7, p8, p9, p10, p11, layout_matrix=layout_matrix)
+dev.off()
 ```
@@
 # Figure: Kap v Err
-```{r, fig.width=3.25, fig.height=1.1}
+```{r, fig.width=3, fig.height=1.1}
 # -
@@
   scale_y_log10() + annotation_logticks() +
-  theme_classic() + 
+  theme_classic2() + 
   theme(plot.title = element_text(hjust = -.3, size=18, face="bold"),
@@
   lims(x=c(0.0, 0.25)) + annotation_logticks() +
-  theme_classic() + 
+  theme_classic2() + 
   scale_y_log10() +
@@
 # -
-p3 <- textGrob("Sustained")
+p3 <- textGrob("Tonic")
 p4 <- textGrob("Burst", gp=gpar(col="darkgoldenrod3"))
@@
 grid.arrange(p1, p2, p3, p4, layout_matrix=layout_matrix)
+
+png(file="fig3.png", bg="white", width=6, height=2.1, unit="in", res=300)
+grid.arrange(p1, p2, p3, p4, layout_matrix=layout_matrix)
+dev.off()
 ```
@@
 # Figure: Calcium control
-```{r, fig.width=2.4, fig.height=1.8}
+```{r, fig.width=2.4, fig.height=1.6}
 # -
@@
   geom_errorbar(aes(ymin=M - SD, ymax=M + SD), alpha=0.5, width=.1, size=0.4)  +
-  labs(title="b.", y="Kappa", x="Osc. rate (Hz)") +
+  labs(title="b.", y="Kappa", x="Osc. rate") +
   scale_color_manual(
@@
     guide=FALSE) +
-  theme_classic() +
+  theme_classic2() +
   theme(plot.title = element_text(hjust = -.5, size=18, face="bold")) -> p1
@@
   geom_errorbar(aes(ymin=M - SD, ymax=M + SD), alpha=0.5, width=.1, size=0.4)  +
-  labs(title="a.", y="Pop. rate (Hz)", x="Osc. rate (Hz)") +
+  labs(title="a.", y="Pop. rate", x="Osc. rate") +
   scale_color_manual(
@@
     name="Target [Ca]\n(mmolar)") +
-  theme_classic() +
+  theme_classic2() +
   theme(
@@
 # -
-p3 <- textGrob("Coordination")
+p3 <- textGrob("Synchrony")
 p4 <- textGrob("Excitability")
@@
 layout_matrix <- rbind(
-  c(6, 6, 6, 6), 
   c(4, 2, 2, 5),
@@
 p5 <- nullGrob()
-p6 <- textGrob("Target Calcium")
-grid.arrange(p1, p2, p3, p4, p5, p6, layout_matrix=layout_matrix)
+grid.arrange(p1, p2, p3, p4, p5, layout_matrix=layout_matrix)
 
-# -
-# png(file="fig5.png", bg="white", width=4.2, height=3.8, unit="in", res=300)
-# plot(p)
-# dev.off()
-
-rm(p1, p2, p3, p4, p5, p6, tmp1, tmp2)
+png(file="fig4.png", bg="white", width=4.8, height=3.2, unit="in", res=300)
+grid.arrange(p1, p2, p3, p4, p5, layout_matrix=layout_matrix)
+dev.off()
 ```

### 2018-11-21 resistingrhythm/analysis/exp231.Rmd
Add analysis for exp231

---
title: "Analysis : exp231 analysis"
output: html_notebook
---

```{r, message=FALSE}
library(tidyverse)
library(gridExtra)
library(grid)
library(ggpubr)
library(cowplot)

data_path <- "~/Code/resistingrhythm/data/"
```

# Load all data
```{r, message=FALSE}
# 231
tau_h <- 600
exp_code <- 231
n_cycles <- c("4", "8", "480")

results231 <- NULL
for(i in 1:length(n_cycles)){
  n_c <- n_cycles[i]

  # Load the csv
  df <- read_csv(paste(data_path, 
                       "exp", as.character(exp_code), 
                       "_c", n_c, 
                       ".csv", sep=""))  
  # Add metadata
  df$n_cycles <- rep(n_c, nrow(df))
  df$frac_tau_h <- rep(as.character(
    (
      round(as.numeric(n_c)*(1/8)/tau_h, digits=3)
    ), nrow(df)
    )
  )
  df$osc_rate <- rep("6", nrow(df))
  df$freq <- rep("b", nrow(df))
  df$synapse <- rep("Excitatory", nrow(df))
  df$homeo <- rep("Homeostasis", nrow(df))
  if(n_c <= 8){
    df$mode <- rep("Burst", nrow(df))
  } else {
    df$mode <- rep("Tonic", nrow(df))
  }

  results231 <- rbind(results231, df)
}

exp_code <- 232
results232 <- NULL
for(i in 1:length(n_cycles)){
  n_c <- n_cycles[i]

  # Load the csv
  df <- read_csv(paste(data_path, 
                       "exp", as.character(exp_code), 
                       "_c", n_c, 
                       ".csv", sep=""))  
  # Add metadata
  df$n_cycles <- rep(n_c, nrow(df))
  df$frac_tau_h <- rep(as.character(
    (
      round(as.numeric(n_c)*(1/8)/tau_h, digits=3)
    ), nrow(df)
    )
  )
  df$osc_rate <- rep("6", nrow(df))
  df$freq <- rep("b", nrow(df))
  df$synapse <- rep("Excitatory", nrow(df))
  df$homeo <- rep("No homeostasis", nrow(df))
  if(n_c <= 8){
    df$mode <- rep("Burst", nrow(df))
  } else {
    df$mode <- rep("Tonic", nrow(df))
  }

  results232 <- rbind(results232, df)
}

rm(df, n_c, i, exp_code)
```

```{r, fig.width=2.2, fig.height=1.1}
rbind(results231, results232) %>% 
  ggplot(aes(x=frac_tau_h, y=rate_k, color=homeo, group=interaction(homeo, frac_tau_h))) +
  geom_boxplot() +
  scale_color_manual(values=c("black", "grey"), name="") 
```

```{r, fig.width=2.2, fig.height=1.1}
rbind(results231, results232) %>% 
  ggplot(aes(x=frac_tau_h, y=kappa_coord, color=homeo, group=interaction(homeo, frac_tau_h))) +
  geom_boxplot() +
  scale_color_manual(values=c("black", "grey"), name="") 
```

### 2018-11-21 resistingrhythm/analysis/exp229.Rmd
Update exp229 analysis

@@
 results229 %>% 
-  filter(osc_rate == "2") %>% 
+  # filter(osc_rate == "2") %>% 
   ggplot(aes(x=freq, y=rate_k, color=frac_tau_h)) +

### 2018-12-02 resistingrhythm/analysis/paper_figures_v4.Rmd
Update figs

@@
 
-# Figure: Kap v Err
-```{r, fig.width=3, fig.height=1.1}
-# -
+# Figure: Error
+```{r, fig.width=3.2, fig.height=3.1}
+# ------------------------------------------------------------
+# Kappa
 results220 %>% 
@@
   mutate(
-    M_error=mean(abs_error), SD_error=sd(abs_error), 
+    M_error=mean(mse_error), SD_error=sd(mse_error), 
+    M_rate_k=mean(rate_k), SD_rate_k=sd(rate_k), 
     M_kappa=mean(kappa_coord), SD_kappa=sd(kappa_coord)) -> tmp1
@@
   mutate(
-    M_error=mean(abs_error), SD_error=sd(abs_error), 
+    M_error=mean(mse_error), SD_error=sd(mse_error), 
+    M_rate_k=mean(rate_k), SD_rate_k=sd(rate_k), 
     M_kappa=mean(kappa_coord), SD_kappa=sd(kappa_coord)) -> tmp2
@@
 
+# Kappa
 bind_rows(tmp1, tmp2) %>% 
@@
 
-# -
+# Rate
+bind_rows(tmp1, tmp2) %>% 
+ggplot(mapping=aes(x=M_rate_k, y=M_error, color=mode)) +
+  geom_point(size=0.2) +
+  geom_errorbar(mapping=aes(x=M_rate_k, ymin=M_error - SD_error, ymax=M_error + SD_error),
+                width=0.004, size=0.2) +
+  geom_errorbarh(mapping=aes(y=M_error, xmin=M_rate_k - SD_rate_k, xmax=M_rate_k + SD_rate_k),
+                 height=0.002, size=0.2) +
+  scale_color_manual(values=c("black", "darkgrey")) +
+  labs(title="c.", y="Log error (s)", x="Pop. rate") +
+  # lims(x=c(0.0, 0.25)) +
+  scale_y_log10() + annotation_logticks() +
+  theme_classic2() + 
+  theme(plot.title = element_text(hjust = -.3, size=18, face="bold"),
+        legend.position = "none") -> p3
+
+# ---------------------------------------------------------------------
 results220 %>% 
@@
   mutate(
-    M_error=mean(abs_error), SD_error=sd(abs_error), 
+      M_error=mean(mse_error), SD_error=sd(mse_error), 
+      M_rate_k=mean(rate_k), SD_rate_k=sd(rate_k), 
       M_kappa=mean(kappa_coord), SD_kappa=sd(kappa_coord)) -> tmp1
@@
 
+# Rate
+bind_rows(tmp1, tmp2) %>% 
+ggplot(mapping=aes(x=M_rate_k, y=M_error, color=mode)) +
+  geom_point(size=0.2) +
+  geom_errorbar(mapping=aes(x=M_rate_k, ymin=M_error - SD_error, ymax=M_error + SD_error),
+                width=0.004, size=0.2) +
+  geom_errorbarh(mapping=aes(y=M_error, xmin=M_rate_k - SD_rate_k, xmax=M_rate_k + SD_rate_k),
+                 height=0.002, size=0.2) +
+  scale_color_manual(values=c("black", "darkgrey")) +
+  labs(title="d.", y="Log error (s)", x="Pop. rate") +
+  # lims(x=c(0.0, 0.25)) +
+  theme_classic2() + 
+  scale_y_log10() +
+  theme(plot.title = element_text(hjust = -.3, size=18, face="bold"),
+        legend.title=element_blank()) -> p4
+
 # -
-p3 <- textGrob("Tonic")
-p4 <- textGrob("Burst", gp=gpar(col="darkgoldenrod3"))
+p5 <- textGrob("Tonic")
+p6 <- textGrob("Burst", gp=gpar(col="darkgoldenrod3"))
 
@@
 layout_matrix <- rbind(
-  c(3, 3, 4, 4, NA),
-  c(1, 1, 2, 2, 2),
-  c(1, 1, 2, 2, 2),
-  c(1, 1, 2, 2, 2),
-  c(1, 1, 2, 2, 2)
+  c(5, 5, 5, 6, 6, 6, 6, NA),
+  c(1, 1, 1, 2, 2, 2, 2, 2),
+  c(1, 1, 1, 2, 2, 2, 2, 2),
+  c(1, 1, 1, 2, 2, 2, 2, 2),
+  c(1, 1, 1, 2, 2, 2, 2, 2),
+  c(3, 3, 3, 4, 4, 4, 4, 4),
+  c(3, 3, 3, 4, 4, 4, 4, 4),
+  c(3, 3, 3, 4, 4, 4, 4, 4),
+  c(3, 3, 3, 4, 4, 4, 4, 4)
 )
-grid.arrange(p1, p2, p3, p4, layout_matrix=layout_matrix)
+grid.arrange(p1, p2, p3, p4, p5, p6, layout_matrix=layout_matrix)
 
-png(file="fig3.png", bg="white", width=6, height=2.1, unit="in", res=300)
-grid.arrange(p1, p2, p3, p4, layout_matrix=layout_matrix)
+png(file="fig3.png", bg="white", width=6.4, height=2.2, unit="in", res=300)
+grid.arrange(p1, p2, p3, p4, p5, p6, layout_matrix=layout_matrix)
 dev.off()

### 2018-12-08 resistingrhythm/analysis/exp229.Rmd
Plot play

--- 2018-11-17 resistingrhythm/analysis/exp229.Rmd
@@
 ```{r, message=FALSE}
-library(tidyverse)
+library(ggplot2)
+library(dplyr)
+library(magrittr)
+library(readr)
 library(gridExtra)
@@
 
-```{r, fig.width=1.5, fig.height=1.2}
-null_rate <- mean(filter(results229, osc_rate == "0")$rate_k)
+```{r, fig.width=1.4, fig.height=0.8}
+# null_rate <- mean(filter(results229, osc_rate == "0")$rate_k)
 results229 %>% 
-  filter(osc_rate != "0") %>%
   ggplot(aes(x=frac_tau_h, y=rate_k)) +
@@
     theme_classic2() +
-    scale_color_brewer(palette="PuOr", direction=-1) +
     labs(x="Frac. tau_h", y="Pop. rate") +
+    theme(legend.position = "right") 
+```
+
+```{r, fig.width=2.2, fig.height=1.2}
+null_rate <- mean(filter(results229, osc_rate == "0")$rate_k)
+results229 %>% 
+  filter(osc_)
+  ggplot(aes(x=frac_tau_h, y=rate_k - null_rate, color=osc_rate)) +
+    geom_jitter(size=0.01, width=.2) +
+    theme_classic2() +
+    scale_color_manual(values=c("grey", "firebrick1", "firebrick3", "firebrick4")) +
+    labs(x="Frac. tau_h", y="Pop. rate") +
+    theme(legend.position = "right") 
+```
+
+```{r, fig.width=1.2, fig.height=0.6}
+results229 %>% 
+  # filter(osc_rate == "4") %>%
+  ggplot(aes(x=freq, y=rate_k, color=as.numeric(frac_tau_h), group=interaction(freq, frac_tau_h))) +
+  geom_jitter(size=0.02, width=.2, alpha=0.5, outlier.colour = NA) +
+  # geom_boxplot() +
+  # geom_jitter() +
+  theme_classic2() +
+  scale_color_gradient(high="plum4", low="lightgrey") +
+  labs(x="Frequency (Hz)", y="Pop. rate") +
   theme(legend.position = "none")
@@
 
-```{r}
+```{r fig.width=1, fig.height=0.85}
 results229 %>% 
-  filter(osc_rate == "2") %>% 
-  ggplot(aes(x=freq, y=rate_k, color=frac_tau_h)) +
-  geom_boxplot() +
-  theme_classic2() +
-  scale_color_brewer(palette="BrBG", direction=-1) +
-  labs(x="Frequency (Hz)", y="Pop. rate") 
+  # filter(osc_rate != "0") %>%
+  # filter(freq == "8") %>%
+  ggplot(aes(x=osc_rate, y=rate_k, 
+             color=as.numeric(frac_tau_h), group=interaction(frac_tau_h, osc_rate))) +
+  geom_jitter(size=0.02, width=.2, outlier.colour = NA) +
+  theme_pubr() +
+  scale_color_gradient(high="plum4", low="lightgrey") +
+  labs(x="Osc. rate", y="Pop. rate") +
+  theme(legend.position = "none")
 ```
-
-```{r}
-results229 %>% 
-  filter(osc_rate != "0") %>% 
-  ggplot(aes(x=osc_rate, y=rate_k, color=frac_tau_h)) +
-  geom_boxplot() +
-  theme_classic2() +
-  scale_color_brewer(palette="BrBG", direction=-1) +
-  labs(x="Osc. rate", y="Pop. rate") 
-```

### 2018-12-08 resistingrhythm/analysis/exp231.Rmd
Plot play

@@
   ggplot(aes(x=frac_tau_h, y=rate_k, color=homeo, group=interaction(homeo, frac_tau_h))) +
-  geom_boxplot() +
+  geom_boxplot(size=0.6) +
   scale_color_manual(values=c("black", "grey"), name="") 

### 2018-12-08 resistingrhythm/neurons.py
Reactivate dg_CA/dt

@@ -69,12 +69,12 @@ def HHH(time,
 
     # While concentration vars are said to be
     # passed in 'molar',
-    # we correct for the way units in brian2 
+    # we correct for the way units in brian2
     # define liter and how that interacts with
     # the float() values of numbers who've been
-    # touched by volume units. 
+    # touched by volume units.
     # For example, if you passed 1 and we convert to
-    # 1 liter internally, then cast back to float the 
+    # 1 liter internally, then cast back to float the
     # '1' becomes 0.001.
     # that is
     # > float(1 * liter)
@@ -94,8 +94,8 @@ def HHH(time,
     V_l = -70 * mV
     V_Na = 50 * mV
 
-    # Ca and Homeostasis values from 
-    # Siegel, M., Marder, E.V.E. & Abbott, L.F., 1994. Activity-dependent 
+    # Ca and Homeostasis values from
+    # Siegel, M., Marder, E.V.E. & Abbott, L.F., 1994. Activity-dependent
     # current distributions in model neurons. , 91(November), pp.11308-11312.
     # Who modeled a hippocampul neuron.
 
@@ -107,8 +107,9 @@ def HHH(time,
     V1 = -50 * mV
     V2 = 10 * mV
     g_Ca = 0.03 * msiemens
+    G_Ca = g_Ca * 2
 
-    # dg/dt 
+    # dg/dt
     G_Na = 360 * msiemens
     G_K = 120 * msiemens  # Try 90?
     G_KCa = 60 * msiemens
@@ -157,8 +158,8 @@ def HHH(time,
     if homeostasis:
         eqs += """ 
         dg_Na/dt = (1 / tau_h) * (G_Na / (1 + exp(1 * (Ca - Ca_target)/delta)) - g_Na) : siemens 
-        # dg_Ca/dt = (1 / tau_h) * (G_Ca / (1 + exp(1 * (Ca - Ca_target)/delta)) - g_Ca) : siemens 
-        g_Ca : siemens
+        dg_Ca/dt = (1 / tau_h) * (G_Ca / (1 + exp(1 * (Ca - Ca_target)/delta)) - g_Ca) : siemens 
+        # g_Ca : siemens
         dg_K/dt = (1 / tau_h) * (G_K / (1 + exp(-1 * (Ca - Ca_target)/delta)) - g_K) : siemens 
         dg_KCa/dt = (1 / tau_h) * (G_KCa / (1 + exp(-1 * (Ca - Ca_target)/delta)) - g_KCa) : siemens 
         """

### 2018-12-08 resistingrhythm/analysis/paper_figures_v4.Rmd
Cleanup imports
Tweak vis for paper

@@
 ```{r, message=FALSE}
-library(tidyverse)
+library(ggplot2)
+library(latex2exp)
+library(dplyr)
+library(magrittr)
+library(readr)
 library(gridExtra)
@@
 rm(df, exp_code, i, o_c, o_r, osc_codes, osc_rates, s_c, stim_codes)
+
+# 231
+tau_h <- 600
+exp_code <- 231
+n_cycles <- c("4", "8", "480")
+
+results231 <- NULL
+for(i in 1:length(n_cycles)){
+  n_c <- n_cycles[i]
+
+  # Load the csv
+  df <- read_csv(paste(data_path, 
+                       "exp", as.character(exp_code), 
+                       "_c", n_c, 
+                       ".csv", sep=""))  
+  # Add metadata
+  df$n_cycles <- rep(n_c, nrow(df))
+  df$frac_tau_h <- rep(as.character(
+    (
+      round(as.numeric(n_c)*(1/8)/tau_h, digits=3)
+    ), nrow(df)
+    )
+  )
+  df$osc_rate <- rep("6", nrow(df))
+  df$freq <- rep("b", nrow(df))
+  df$synapse <- rep("Excitatory", nrow(df))
+  df$homeo <- rep("Homeostasis", nrow(df))
+  if(n_c <= 8){
+    df$mode <- rep("Burst", nrow(df))
+  } else {
+    df$mode <- rep("Tonic", nrow(df))
+  }
+
+  results231 <- rbind(results231, df)
+}
+
+# Realistic tau_h and oscillation.
+exp_code <- 232
+results232 <- NULL
+for(i in 1:length(n_cycles)){
+  n_c <- n_cycles[i]
+
+  # Load the csv
+  df <- read_csv(paste(data_path, 
+                       "exp", as.character(exp_code), 
+                       "_c", n_c, 
+                       ".csv", sep=""))  
+  # Add metadata
+  df$n_cycles <- rep(n_c, nrow(df))
+  df$frac_tau_h <- rep(as.character(
+    (
+      round(as.numeric(n_c)*(1/8)/tau_h, digits=3)
+    ), nrow(df)
+    )
+  )
+  df$osc_rate <- rep("6", nrow(df))
+  df$freq <- rep("b", nrow(df))
+  df$synapse <- rep("Excitatory", nrow(df))
+  df$homeo <- rep("No homeostasis", nrow(df))
+  if(n_c <= 8){
+    df$mode <- rep("Burst", nrow(df))
+  } else {
+    df$mode <- rep("Tonic", nrow(df))
+  }
+
+  results232 <- rbind(results232, df)
+}
+
+rm(df, n_c, i, exp_code)
 ```
@@
 # Figure: Error
-```{r, fig.width=3.2, fig.height=3.1}
+```{r, fig.width=3.2, fig.height=1.2}
 # ------------------------------------------------------------
@@
 # Rate
-bind_rows(tmp1, tmp2) %>% 
-ggplot(mapping=aes(x=M_rate_k, y=M_error, color=mode)) +
-  geom_point(size=0.2) +
-  geom_errorbar(mapping=aes(x=M_rate_k, ymin=M_error - SD_error, ymax=M_error + SD_error),
-                width=0.004, size=0.2) +
-  geom_errorbarh(mapping=aes(y=M_error, xmin=M_rate_k - SD_rate_k, xmax=M_rate_k + SD_rate_k),
-                 height=0.002, size=0.2) +
-  scale_color_manual(values=c("black", "darkgrey")) +
-  labs(title="c.", y="Log error (s)", x="Pop. rate") +
-  # lims(x=c(0.0, 0.25)) +
-  scale_y_log10() + annotation_logticks() +
-  theme_classic2() + 
-  theme(plot.title = element_text(hjust = -.3, size=18, face="bold"),
-        legend.position = "none") -> p3
+# bind_rows(tmp1, tmp2) %>% 
+# ggplot(mapping=aes(x=M_rate_k, y=M_error, color=mode)) +
+#   geom_point(size=0.2) +
+#   geom_errorbar(mapping=aes(x=M_rate_k, ymin=M_error - SD_error, ymax=M_error + SD_error),
+#                 width=0.004, size=0.2) +
+#   geom_errorbarh(mapping=aes(y=M_error, xmin=M_rate_k - SD_rate_k, xmax=M_rate_k + SD_rate_k),
+#                  height=0.002, size=0.2) +
+#   scale_color_manual(values=c("black", "darkgrey")) +
+#   labs(title="c.", y="Log error (s)", x="Pop. rate") +
+#   # lims(x=c(0.0, 0.25)) +
+#   scale_y_log10() + annotation_logticks() +
+#   theme_classic2() + 
+#   theme(plot.title = element_text(hjust = -.3, size=18, face="bold"),
+#         legend.position = "none") -> p3
 
@@
 # Rate
-bind_rows(tmp1, tmp2) %>% 
-ggplot(mapping=aes(x=M_rate_k, y=M_error, color=mode)) +
-  geom_point(size=0.2) +
-  geom_errorbar(mapping=aes(x=M_rate_k, ymin=M_error - SD_error, ymax=M_error + SD_error),
-                width=0.004, size=0.2) +
-  geom_errorbarh(mapping=aes(y=M_error, xmin=M_rate_k - SD_rate_k, xmax=M_rate_k + SD_rate_k),
-                 height=0.002, size=0.2) +
-  scale_color_manual(values=c("black", "darkgrey")) +
-  labs(title="d.", y="Log error (s)", x="Pop. rate") +
-  # lims(x=c(0.0, 0.25)) +
-  theme_classic2() + 
-  scale_y_log10() +
-  theme(plot.title = element_text(hjust = -.3, size=18, face="bold"),
-        legend.title=element_blank()) -> p4
+# bind_rows(tmp1, tmp2) %>% 
+# ggplot(mapping=aes(x=M_rate_k, y=M_error, color=mode)) +
+#   geom_point(size=0.2) +
+#   geom_errorbar(mapping=aes(x=M_rate_k, ymin=M_error - SD_error, ymax=M_error + SD_error),
+#                 width=0.004, size=0.2) +
+#   geom_errorbarh(mapping=aes(y=M_error, xmin=M_rate_k - SD_rate_k, xmax=M_rate_k + SD_rate_k),
+#                  height=0.002, size=0.2) +
+#   scale_color_manual(values=c("black", "darkgrey")) +
+#   labs(title="d.", y="Log error (s)", x="Pop. rate") +
+#   # lims(x=c(0.0, 0.25)) +
+#   theme_classic2() + 
+#   scale_y_log10() +
+#   theme(plot.title = element_text(hjust = -.3, size=18, face="bold"),
+#         legend.title=element_blank()) -> p4
 
@@
 layout_matrix <- rbind(
-  c(5, 5, 5, 6, 6, 6, 6, NA),
+  c(3, 3, 3, 4, 4, 4, 4, NA),
   c(1, 1, 1, 2, 2, 2, 2, 2),
@@
   c(1, 1, 1, 2, 2, 2, 2, 2),
-  c(1, 1, 1, 2, 2, 2, 2, 2),
-  c(3, 3, 3, 4, 4, 4, 4, 4),
-  c(3, 3, 3, 4, 4, 4, 4, 4),
-  c(3, 3, 3, 4, 4, 4, 4, 4),
-  c(3, 3, 3, 4, 4, 4, 4, 4)
+  c(1, 1, 1, 2, 2, 2, 2, 2)
 )
-grid.arrange(p1, p2, p3, p4, p5, p6, layout_matrix=layout_matrix)
+grid.arrange(p1, p2, p5, p6, layout_matrix=layout_matrix)
 
-png(file="fig3.png", bg="white", width=6.4, height=2.2, unit="in", res=300)
-grid.arrange(p1, p2, p3, p4, p5, p6, layout_matrix=layout_matrix)
+png(file="fig3.png", bg="white", width=6.4, height=2.4, unit="in", res=300)
+grid.arrange(p1, p2, p5, p6, layout_matrix=layout_matrix)
 dev.off()
@@
 
-# Figure: Calcium control
-```{r, fig.width=2.4, fig.height=1.6}
+# Figure: Control
+```{r, fig.width=2.4, fig.height=2.8}
 # -
@@
 
-# -
-p3 <- textGrob("Synchrony")
-p4 <- textGrob("Excitability")
+# -----------------------------------------------------------------------------------
+# Frac of tau_h
+# rate
+rbind(results231, results232) %>% 
+  ggplot(aes(x=frac_tau_h, y=rate_k, color=homeo, group=interaction(homeo, frac_tau_h))) +
+  geom_boxplot(size=0.6) +
+  stat_compare_means(method="wilcox.test", label="p.signif", 
+                     label.x=1.3, size=3, show.legend=FALSE) +
+  labs(title="c.", y="Pop. rate", x=TeX("$t_{oscillation} / \\tau_{homeostasis}$")) +
+  scale_color_manual(values=c("black", "grey"), name=NA) +
+  theme_classic2() +
+  theme(
+    plot.title = element_text(hjust = -.5, size=18, face="bold"),
+    legend.background = element_rect(colour ="black"),
+    legend.position = c(1.35, 0.5),
+    legend.title=element_blank(),
+    legend.key.size = unit(.3, "cm")) -> p6
 
 # -
+p3 <- textGrob("")
+p4 <- textGrob("Target [Ca]\nperturbation")
+p8 <- textGrob(TeX("Biological $\\tau_h$"))
+p5 <- nullGrob()
+p9 <- nullGrob()
+
+# -
+# layout_matrix <- rbind(
+#   c(4, 2, 2, 5), 6, 6, 5),
+#   c(4, 2, 2, 5), 6, 6, 5),
+#   c(4, 2, 2, 5), 6, 6, 5),
+#   c(4, 2, 2, 5), 6, 6, 5),
+#   c(3, 1, 1, 5), 7, 7, 5),
+#   c(3, 1, 1, 5), 7, 7, 5),
+#   c(3, 1, 1, 5), 7, 7, 5), 
+#   c(3, 1, 1, 5), 7, 7, 5) 
+# )
+
 layout_matrix <- rbind(
@@
   c(3, 1, 1, 5),  
-  c(3, 1, 1, 5) 
+  c(3, 1, 1, 9), 
+  c(8, 6, 6, 9),
+  c(8, 6, 6, 9),
+  c(8, 6, 6, 9),
+  c(8, 6, 6, 9)
 )
-p5 <- nullGrob()
-grid.arrange(p1, p2, p3, p4, p5, layout_matrix=layout_matrix)
+grid.arrange(p1, p2, p3, p4, p5, p6, p8, p9, layout_matrix=layout_matrix)
 
-png(file="fig4.png", bg="white", width=4.8, height=3.2, unit="in", res=300)
-grid.arrange(p1, p2, p3, p4, p5, layout_matrix=layout_matrix)
+png(file="fig4.png", bg="white", width=4.8, height=5.6, unit="in", res=300)
+grid.arrange(p1, p2, p3, p4, p5, p6, p8, p9, layout_matrix=layout_matrix)
 dev.off()

### 2018-12-08 resistingrhythm/analysis/exp229.Rmd
WIP

@@
 ```{r, fig.width=1.4, fig.height=0.8}
-# null_rate <- mean(filter(results229, osc_rate == "0")$rate_k)
 results229 %>% 
+  filter(osc_rate == "6", freq =="8") %>% 
   ggplot(aes(x=frac_tau_h, y=rate_k)) +
+    geom_jitter(size=0.01) +
+    theme_classic2() +
+    labs(x="Frac. tau_h", y="Pop. rate") +
+    theme(legend.position = "right") 
+```
+
+```{r, fig.width=2, fig.height=1}
+results229 %>% 
+  filter(osc_rate == "6", freq =="8") %>% 
+  group_by(osc_rate, frac_tau_h) %>%
+  summarise(M=mean(rate_k), SD=sd(rate_k)) %>%
+  ggplot(aes(x=frac_tau_h, y=M)) +
+  geom_point(size=1.5) +
+  geom_errorbar(aes(ymin=M - SD, ymax=M + SD), alpha=0.5, width=.2, size=0.8)  +
+  labs(y="Pop. rate", x="tau_h") +
+  lims(y=c(0, 160))
+```
+
+```{r, fig.width=2.2, fig.height=1.2}
+results229 %>% 
+  filter(frac_tau_h == "2") %>% 
+  filter(osc_rate != "0") %>% 
+  ggplot(aes(x=osc_rate, y=rate_k)) +
     geom_boxplot() +
     theme_classic2() +
-    labs(x="Frac. tau_h", y="Pop. rate") +
+    labs(x="Osc rate", y="Pop. rate") +
     theme(legend.position = "right") 
@@
 results229 %>% 
-  # filter(osc_rate == "4") %>%
+  filter(osc_rate == "6") %>%
   ggplot(aes(x=freq, y=rate_k, color=as.numeric(frac_tau_h), group=interaction(freq, frac_tau_h))) +

### 2019-04-21 resistingrhythm/analysis/paper_figures_v4.Rmd
Fig tweaks

@@
   ggplot(mapping=aes(x=osc_rate, y=M, group=osc_rate, color=synapse)) +
-    geom_point(size=0.8) +
+    geom_point(size=1.25) +
     geom_errorbar(mapping=aes(x=osc_rate, ymin=M - SD, ymax=M + SD, color=synapse),
@@
   ggplot(mapping=aes(x=osc_rate, y=M, group=osc_rate, color=synapse)) +
-  geom_point(size=0.8) +
+  geom_point(size=1.25) +
   geom_errorbar(mapping=aes(x=osc_rate, ymin=M - SD, ymax=M + SD, color=synapse),
@@
   ggplot(mapping=aes(x=osc_rate, y=M, group=osc_rate, color=synapse)) +
-  geom_point(size=0.8) +
+  geom_point(size=1.25) +
   geom_errorbar(mapping=aes(x=osc_rate, ymin=M - SD, ymax=M + SD, color=synapse), 
@@
   ggplot(mapping=aes(x=osc_rate, y=M, group=osc_rate, color=synapse)) +
-    geom_point(size=0.8) +
+    geom_point(size=1.25) +
     geom_errorbar(mapping=aes(x=osc_rate, ymin=M - SD, ymax=M + SD, color=synapse), 
@@
   theme(
-    legend.position = c(1.35, .5),
+    legend.position = c(1.5, -1.25),
     legend.title = element_text(colour = 'darkgoldenrod3'),
@@
   c(NA, 8, 8, 8, NA, 9, 9, 9, 9, 9, 9, NA, NA),
-  c(11, 3, 3, 3, NA, 4, 4, 4, 6, 6, 6, NA, NA),
-  c(11, 3, 3, 3, NA, 4, 4, 4, 6, 6, 6, NA, NA),
-  c(11, 3, 3, 3, NA, 4, 4, 4, 6, 6, 6, NA, NA),
+  c(11, 3, 3, 3, NA, 4, 4, 4, 6, 6, 6, 7, 7),
+  c(11, 3, 3, 3, NA, 4, 4, 4, 6, 6, 6, 7, 7),
+  c(11, 3, 3, 3, NA, 4, 4, 4, 6, 6, 6, 7, 7),
   c(11, 3, 3, 3, NA, 4, 4, 4, 6, 6, 6, 7, 7),
   c(10, 1, 1, 1, NA, 2, 2, 2, 5, 5, 5, 7, 7), 
-  c(10, 1, 1, 1, NA, 2, 2, 2, 5, 5, 5, 7, 7), 
-  c(10, 1, 1, 1, NA, 2, 2, 2, 5, 5, 5, 7, 7), 
-  c(10, 1, 1, 1, NA, 2, 2, 2, 5, 5, 5, 7, 7)
+  c(10, 1, 1, 1, NA, 2, 2, 2, 5, 5, 5, NA, NA), 
+  c(10, 1, 1, 1, NA, 2, 2, 2, 5, 5, 5, NA, NA), 
+  c(10, 1, 1, 1, NA, 2, 2, 2, 5, 5, 5, NA, NA)
 )
@@
 ggplot(mapping=aes(x=M_kappa, y=M_error, color=mode)) +
-  geom_point(size=0.2) +
+  geom_point(size=1.25) +
   geom_errorbar(mapping=aes(x=M_kappa, ymin=M_error - SD_error, ymax=M_error + SD_error),
@@
                      label.x=1.3, size=3, show.legend=FALSE) +
-  labs(title="c.", y="Pop. rate", x=TeX("$t_{oscillation} / \\tau_{homeostasis}$")) +
+  labs(title="c.", y="Pop. rate", x=TeX("$t_{oscillation} / \\tau_{h}$")) +
   scale_color_manual(values=c("black", "grey"), name=NA) +

### 2019-05-08 resistingrhythm/neurons.py
Docs

@@ -42,7 +42,7 @@ def HHH(time,
         record_traces=True,
         progress_report=None,
         seed_value=None):
-    """Homeostasis in HH neurons."""
+    """Homeostasis in Hippocampal HH neurons."""
     prefs.codegen.target = 'numpy'
 
     prng = np.random.RandomState(seed_value)

### 2019-05-08 resistingrhythm/neurons.py
Exposed internal params

@@ -26,6 +26,9 @@ def HHH(time,
         external_current=None,
         Ca_target=50e-9,
         tau_h=10,
+        g_l=1.0e-3,
+        g_Ca=0.03e-3,
+        sigma=0,
         N=1,
         w_in=0.8e-9,
         tau_in=5e-3,
@@ -35,7 +38,6 @@ def HHH(time,
         tau_osc=5e-3,
         V_osc=0,
         p_connection=0.1,
-        sigma=0,
         burn_time=0,
         time_step=1e-5,
         homeostasis=True,
@@ -87,8 +89,7 @@ def HHH(time,
     # HH general params, in misc units
     Et = 20 * mvolt
     Cm = 1 * uF  # /cm2
-
-    g_l = 1.0 * msiemens
+    g_l *= siemens
 
     V_K = -100 * mV  # was 100, changed to match LeMasson
     V_l = -70 * mV
@@ -106,7 +107,7 @@ def HHH(time,
     V_Ca = 150 * mV
     V1 = -50 * mV
     V2 = 10 * mV
-    g_Ca = 0.03 * msiemens
+    g_Ca *= siemens
     G_Ca = g_Ca * 2
 
     # dg/dt

### 2019-05-08 resistingrhythm/neurons.py
DOcs

@@ -96,9 +96,8 @@ def HHH(time,
     V_Na = 50 * mV
 
     # Ca and Homeostasis values from
-    # Siegel, M., Marder, E.V.E. & Abbott, L.F., 1994. Activity-dependent
-    # current distributions in model neurons. , 91(November), pp.11308-11312.
-    # Who modeled a hippocampul neuron.
+    # Siegel, M., Marder, & Abbott, L.F., 1994. Activity-dependent
+    # current distributions in model neurons. 91, pp.11308-11312.
 
     # d[Ca]/dt
     delta = 0.6 * umolar  # TODO: was umolar?

### 2019-05-08 resistingrhythm/analysis/paper_figures_v4.Rmd
Limited osc_rate: 0-3 (from 0-6)

@@
 exp_code <- 224
-osc_codes <- c(100, 101, 102, 103, 104, 105, 110, 115, 120, 125, 130, 135, 140, 145, 150, 155, 160)
-osc_rates <- c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0, 3.5, 4.0, 4.5, 5.0, 5.5, 6.0)
+osc_codes <- c(100, 101, 102, 103, 104, 105, 110, 115, 120, 125, 130)
+osc_rates <- c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0)
 stim_codes <- c(3, 4) # 4
@@
 exp_code <- 221
-osc_codes <- c(100, 101, 102, 103, 104, 105, 110, 115, 120, 125, 130, 135, 140, 145, 150, 155, 160)
-osc_rates <- c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0, 3.5, 4.0, 4.5, 5.0, 5.5, 6.0)
+osc_codes <- c(100, 101, 102, 103, 104, 105, 110, 115, 120, 125, 130)
+osc_rates <- c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0)
 stim_codes <- c(3, 4)
@@
 exp_code <- 220
-osc_codes <- c(100, 101, 102, 103, 104, 105, 110, 115, 120, 125, 130, 135, 140, 145, 150, 155, 160)
-osc_rates <- c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0, 3.5, 4.0, 4.5, 5.0, 5.5, 6.0)
+osc_codes <- c(100, 101, 102, 103, 104, 105, 110, 115, 120, 125, 130)
+osc_rates <- c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0)
 stim_codes <- c(3, 4)
@@
 exp_code <- 223
-osc_codes <- c(100, 101, 102, 103, 104, 105, 110, 115, 120, 125, 130, 135, 140, 145, 150, 155, 160)
-osc_rates <- c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0, 3.5, 4.0, 4.5, 5.0, 5.5, 6.0)
+osc_codes <- c(100, 101, 102, 103, 104, 105, 110, 115, 120, 125, 130)
+osc_rates <- c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0)
 stim_codes <- c(3, 4)
@@
 exp_code <- 222
-osc_codes <- c(100, 101, 102, 103, 104, 105, 110, 115, 120, 125, 130, 135, 140, 145, 150, 155, 160)
-osc_rates <- c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0, 3.5, 4.0, 4.5, 5.0, 5.5, 6.0)
+osc_codes <- c(100, 101, 102, 103, 104, 105, 110, 115, 120, 125, 130)
+osc_rates <- c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0)
 stim_codes <- c(3, 4)
@@
 exp_code <- 227
-osc_codes <- c(100, 101, 102, 103, 104, 105, 110, 115, 120, 125, 130, 135, 140, 145, 150, 155, 160)
-osc_rates <- c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0, 3.5, 4.0, 4.5, 5.0, 5.5, 6.0)
+osc_codes <- c(100, 101, 102, 103, 104, 105, 110, 115, 120, 125, 130)
+osc_rates <- c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0)
 stim_codes <- c(3, 4)
@@
 exp_code <- 228
-osc_codes <- c(105, 115, 125, 135, 145, 155)
-osc_rates <- c(0.5, 1.5, 2.5, 3.5, 4.5, 5.5)
+osc_codes <- c(105, 115, 125)
+osc_rates <- c(0.5, 1.5, 2.5)
 stim_codes <- c(3)
@@
 exp_code <- 221
-osc_codes <- c(105, 115, 125, 135, 145, 155)
-osc_rates <- c(0.5, 1.5, 2.5, 3.5, 4.5, 5.5)
+osc_codes <- c(105, 115, 125)
+osc_rates <- c(0.5, 1.5, 2.5)
 stim_codes <- c(3)
@@
 
-# Figure: Error
-```{r, fig.width=3.2, fig.height=1.2}
-# ------------------------------------------------------------
-# Kappa
-results220 %>% 
-  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
-  mutate(kappa_coord=replace(kappa_coord, rate_k < 1, NA)) %>%
-  group_by(osc_rate) %>% 
-  mutate(
-    M_error=mean(mse_error), SD_error=sd(mse_error), 
-    M_rate_k=mean(rate_k), SD_rate_k=sd(rate_k), 
-    M_kappa=mean(kappa_coord), SD_kappa=sd(kappa_coord)) -> tmp1
-tmp1$mode <- rep("No homeostatsis", nrow(tmp1))
-results221 %>% 
-  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
-  mutate(kappa_coord=replace(kappa_coord, rate_k < 1, NA)) %>%
-  group_by(osc_rate) %>% 
-  mutate(
-    M_error=mean(mse_error), SD_error=sd(mse_error), 
-    M_rate_k=mean(rate_k), SD_rate_k=sd(rate_k), 
-    M_kappa=mean(kappa_coord), SD_kappa=sd(kappa_coord)) -> tmp2
-tmp2$mode <- rep("Homeostatsis", nrow(tmp2))
-
-# Kappa
-bind_rows(tmp1, tmp2) %>% 
-ggplot(mapping=aes(x=M_kappa, y=M_error, color=mode)) +
-  geom_point(size=1.25) +
-  geom_errorbar(mapping=aes(x=M_kappa, ymin=M_error - SD_error, ymax=M_error + SD_error),
-                width=0.004, size=0.2) +
-  geom_errorbarh(mapping=aes(y=M_error, xmin=M_kappa - SD_kappa, xmax=M_kappa + SD_kappa),
-                 height=0.002, size=0.2) +
-  scale_color_manual(values=c("black", "darkgrey")) +
-  labs(title="a.", y="Log error (s)", x="Kappa") +
-  lims(x=c(0.0, 0.25)) +
-  scale_y_log10() + annotation_logticks() +
-  theme_classic2() + 
-  theme(plot.title = element_text(hjust = -.3, size=18, face="bold"),
-        legend.position = "none") -> p1
-
-# Rate
-# bind_rows(tmp1, tmp2) %>% 
-# ggplot(mapping=aes(x=M_rate_k, y=M_error, color=mode)) +
-#   geom_point(size=0.2) +
-#   geom_errorbar(mapping=aes(x=M_rate_k, ymin=M_error - SD_error, ymax=M_error + SD_error),
-#                 width=0.004, size=0.2) +
-#   geom_errorbarh(mapping=aes(y=M_error, xmin=M_rate_k - SD_rate_k, xmax=M_rate_k + SD_rate_k),
-#                  height=0.002, size=0.2) +
-#   scale_color_manual(values=c("black", "darkgrey")) +
-#   labs(title="c.", y="Log error (s)", x="Pop. rate") +
-#   # lims(x=c(0.0, 0.25)) +
-#   scale_y_log10() + annotation_logticks() +
-#   theme_classic2() + 
-#   theme(plot.title = element_text(hjust = -.3, size=18, face="bold"),
-#         legend.position = "none") -> p3
-
-# ---------------------------------------------------------------------
-results220 %>% 
-  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
-  mutate(kappa_coord=replace(kappa_coord, rate_k < 1, NA)) %>%
-  group_by(osc_rate) %>% 
-  mutate(
-      M_error=mean(mse_error), SD_error=sd(mse_error), 
-      M_rate_k=mean(rate_k), SD_rate_k=sd(rate_k), 
-      M_kappa=mean(kappa_coord), SD_kappa=sd(kappa_coord)) -> tmp1
-tmp1$mode <- rep("No homeostatsis", nrow(tmp1))
-results224 %>% 
-  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
-  mutate(kappa_coord=replace(kappa_coord, rate_k < 1, NA)) %>%
-  group_by(osc_rate) %>% 
-  mutate(
-    M_error=mean(mse_error), SD_error=sd(mse_error), 
-    M_rate_k=mean(rate_k), SD_rate_k=sd(rate_k), 
-    M_kappa=mean(kappa_coord), SD_kappa=sd(kappa_coord)) -> tmp2
-tmp2$mode <- rep("Homeostatsis", nrow(tmp2))
-
-# Kappa
-bind_rows(tmp1, tmp2) %>% 
-ggplot(mapping=aes(x=M_kappa, y=M_error, color=mode)) +
-  geom_point(size=1.25) +
-  geom_errorbar(mapping=aes(x=M_kappa, ymin=M_error - SD_error, ymax=M_error + SD_error),
-                width=0.004, size=0.2) +
-  geom_errorbarh(mapping=aes(y=M_error, xmin=M_kappa - SD_kappa, xmax=M_kappa + SD_kappa),
-                 height=0.002, size=0.2) +
-  scale_color_manual(values=c("black", "darkgrey")) +
-  labs(title="b.", y="Log error (s)", x="Kappa") +
-  lims(x=c(0.0, 0.25)) + annotation_logticks() +
-  theme_classic2() + 
-  scale_y_log10() +
-  theme(plot.title = element_text(hjust = -.3, size=18, face="bold"),
-        legend.title=element_blank()) -> p2
-
-# Rate
-# bind_rows(tmp1, tmp2) %>% 
-# ggplot(mapping=aes(x=M_rate_k, y=M_error, color=mode)) +
-#   geom_point(size=0.2) +
-#   geom_errorbar(mapping=aes(x=M_rate_k, ymin=M_error - SD_error, ymax=M_error + SD_error),
-#                 width=0.004, size=0.2) +
-#   geom_errorbarh(mapping=aes(y=M_error, xmin=M_rate_k - SD_rate_k, xmax=M_rate_k + SD_rate_k),
-#                  height=0.002, size=0.2) +
-#   scale_color_manual(values=c("black", "darkgrey")) +
-#   labs(title="d.", y="Log error (s)", x="Pop. rate") +
-#   # lims(x=c(0.0, 0.25)) +
-#   theme_classic2() + 
-#   scale_y_log10() +
-#   theme(plot.title = element_text(hjust = -.3, size=18, face="bold"),
-#         legend.title=element_blank()) -> p4
-
-# -
-p5 <- textGrob("Tonic")
-p6 <- textGrob("Burst", gp=gpar(col="darkgoldenrod3"))
-
-# -
-layout_matrix <- rbind(
-  c(3, 3, 3, 4, 4, 4, 4, NA),
-  c(1, 1, 1, 2, 2, 2, 2, 2),
-  c(1, 1, 1, 2, 2, 2, 2, 2),
-  c(1, 1, 1, 2, 2, 2, 2, 2),
-  c(1, 1, 1, 2, 2, 2, 2, 2)
-)
-grid.arrange(p1, p2, p5, p6, layout_matrix=layout_matrix)
-
-png(file="fig3.png", bg="white", width=6.4, height=2.4, unit="in", res=300)
-grid.arrange(p1, p2, p5, p6, layout_matrix=layout_matrix)
-dev.off()
-```
-
 # Figure: Control

### 2019-05-08 resistingrhythm/util.py
Added util.poisson_hippocampus_theta
Added test for poisson_hippocampus_theta

@@ -7,7 +7,10 @@ from scipy.signal import square
 from fakespikes import neurons, rates
 from fakespikes import util as fsutil
 
+import resistingrhythm
+
 import numpy as np
+from scipy import signal
 
 
 def filter_spikes(ns, ts, window):
@@ -249,6 +252,62 @@ def current_pulse(t=1, t_onset=0.8, t_offset=0.9, I=10e-9, dt=1e-5, name=None):
 def load_current(filename):
     x = np.loadtxt(filename)
     return x
+
+
+def poisson_hippocampus_theta(t=1,
+                              t_onset=0.2,
+                              n_cycles=8,
+                              rate=6,
+                              n=10,
+                              dt=1e-3,
+                              name=None,
+                              seed=None):
+    """Simulate a Poisson population based on LFP from CA1."""
+    # Requested rate
+    sampling_rate = int(1 / dt)
+
+    # Load LFP
+    base_path = os.path.split(resistingrhythm.__file__)[0]
+    lfp_raw = np.load(os.path.join(base_path, 'data/ca1.npy'))
+    native_sampling_rate = int(1252)  # sampling rate in ../data/ca1.npy
+
+    # Limit to t; lfp_raw is 41 Mb on disk.
+    times = np.arange(0,
+                      len(lfp_raw) / native_sampling_rate,
+                      1 / native_sampling_rate)
+    lfp_raw = lfp_raw[times <= t]
+
+    # Resample lfp?
+    if native_sampling_rate != sampling_rate:
+        lfp = signal.resample(
+            lfp_raw, int(
+                (lfp_raw.size / native_sampling_rate) * sampling_rate))
+    else:
+        lfp = lfp_raw
+
+    # Normalize lfp -> (0, 1)
+    lfp = (lfp - np.min(lfp)) / (np.max(lfp) - np.min(lfp))
+
+    # Recreate time
+    times = np.arange(0, len(lfp) / sampling_rate, 1 / sampling_rate)
+
+    # Truncate lFP to burst parameters.
+    f = 8  # fixed here; approximate.
+    burst_l = (1 / float(f)) * n_cycles
+    m = np.logical_not(
+        np.logical_and(times >= t_onset, times <= (t_onset + burst_l)))
+    lfp[m] = 0
+
+    # Make spikes
+    nrns = neurons.Spikes(n, t, dt=dt, refractory=dt, seed=None)
[…]

### 2019-05-08 resistingrhythm/exp/homeostasis_experiments.py
Added CL interface for poisson_hippocampus_theta

@@ -10,6 +10,7 @@ from resistingrhythm.neurons import HHH
 from resistingrhythm.util import filter_spikes
 from resistingrhythm.util import poisson_impulse
 from resistingrhythm.util import poisson_oscillation
+from resistingrhythm.util import poisson_hippocampus_theta
 from resistingrhythm.util import current_pulse
 from resistingrhythm.util import load_spikes
 from resistingrhythm.util import load_current
@@ -146,26 +147,27 @@ def run(run_name,
         # -
         if verbose:
             print(">>> Running the modulation model")
-        results_k = HHH(t,
-                        ns_stim,
-                        ts_stim,
-                        ns_osc,
-                        ts_osc,
-                        external_current=external_current,
-                        N=N,
-                        Ca_target=Ca_target,
-                        bias_in=bias_in,
-                        sigma=sigma,
-                        w_in=w,
-                        w_osc=w,
-                        V_osc=V_osc,
-                        tau_osc=tau_osc,
-                        tau_h=tau_h,
-                        time_step=time_step,
-                        burn_time=burn_t,
-                        seed_value=seed_value + k,
-                        record_traces=True,
-                        homeostasis=homeostasis)
+        results_k = HHH(
+            t,
+            ns_stim,
+            ts_stim,
+            ns_osc,
+            ts_osc,
+            external_current=external_current,
+            N=N,
+            Ca_target=Ca_target,
+            bias_in=bias_in,
+            sigma=sigma,
+            w_in=w,
+            w_osc=w,
+            V_osc=V_osc,
+            tau_osc=tau_osc,
+            tau_h=tau_h,
+            time_step=time_step,
+            burn_time=burn_t,
+            seed_value=seed_value + k,
+            record_traces=True,
+            homeostasis=homeostasis)
 
         # -
         if verbose:
@@ -231,6 +233,7 @@ if __name__ == "__main__":
     fire.Fire({
         'create_stim': poisson_impulse,
         'create_osc': poisson_oscillation,
+        'create_hippocampus_theta': poisson_hippocampus_theta,
         'create_current': current_pulse,
         'run': run
     })

### 2019-05-09 resistingrhythm/util.py
Added min_rate flag

@@ -258,6 +258,7 @@ def poisson_hippocampus_theta(t=1,
                               t_onset=0.2,
                               n_cycles=8,
                               rate=6,
+                              min_rate=0,
                               n=10,
                               dt=1e-3,
                               name=None,
@@ -296,7 +297,7 @@ def poisson_hippocampus_theta(t=1,
     burst_l = (1 / float(f)) * n_cycles
     m = np.logical_not(
         np.logical_and(times >= t_onset, times <= (t_onset + burst_l)))
-    lfp[m] = 0
+    lfp[m] = min_rate
 
     # Make spikes
     nrns = neurons.Spikes(n, t, dt=dt, refractory=dt, seed=None)

### 2019-05-09 resistingrhythm/exp/homeostasis_experiments.py
Exposed new params

@@ -33,6 +33,8 @@ def run(run_name,
         V_osc=0,
         tau_osc=5e-3,
         bias_in=0,
+        g_l=1.0e-3,
+        g_Ca=0.03e-3,
         sigma=0,
         num_trials=2,
         seed_value=42,
@@ -132,6 +134,8 @@ def run(run_name,
             Ca_target=Ca_ref,
             bias_in=bias_in,
             sigma=sigma,
+            g_l=g_l,
+            g_Ca=g_Ca,
             w_in=w,
             w_osc=w,
             tau_h=tau_h,

### 2019-05-28 resistingrhythm/analysis/exp244-245.Rmd
Analyze 244/45

---
title: "Analysis : exp244-245 analysis"
output: html_notebook
---

```{r, message=FALSE}
library(ggplot2)
library(dplyr)
library(magrittr)
library(readr)
library(gridExtra)
library(grid)
library(ggpubr)
library(cowplot)

data_path <- "~/Code/resistingrhythm/data/"
```

# Load all data
```{r, message=FALSE}
# -----------------------------------------------------------------------
# LFP E, no H
exp_code <- 244
osc_codes <- c(100, 101, 102, 103, 104, 105, 110, 115, 120, 125, 130)
osc_rates <- c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0)
stim_codes <- c(3, 4) # 4

results244 <- NULL
for(i in 1:length(osc_codes)){
  for(s_c in stim_codes){
    o_c <- osc_codes[i]
    o_r <- osc_rates[i]

    # Load the csv
    df <- read_csv(paste(data_path, 
                         "exp", as.character(exp_code), 
                         "_stim", as.character(s_c), 
                         "lfp", as.character(o_c),
                         ".csv", sep=""))

    # Add metadata
    df$osc_code <- rep(o_c, nrow(df))
    df$osc_rate <- rep(o_r, nrow(df))
    df$stim_code <- rep(s_c, nrow(df))
    df$synapse <- rep("AMPA", nrow(df))
    df$homeo <- rep("No homeostasis", nrow(df))
    results244 <- rbind(results244, df)
  }
}

results244 %>%
  filter(rate_k > 0) -> results244

# LFP E, w/ H
exp_code <- 245
osc_codes <- c(100, 101, 102, 103, 104, 105, 110, 115, 120, 125, 130)
osc_rates <- c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0)
stim_codes <- c(3, 4) # 4

results245 <- NULL
for(i in 1:length(osc_codes)){
  for(s_c in stim_codes){
    o_c <- osc_codes[i]
    o_r <- osc_rates[i]

    # Load the csv
    df <- read_csv(paste(data_path, 
                         "exp", as.character(exp_code), 
                         "_stim", as.character(s_c), 
                         "_lfp", as.character(o_c),
                         ".csv", sep=""))

    # Add metadata
    df$osc_code <- rep(o_c, nrow(df))
    df$osc_rate <- rep(o_r, nrow(df))
    df$stim_code <- rep(s_c, nrow(df))
    df$synapse <- rep("AMPA", nrow(df))
    df$homeo <- rep("Homeostasis", nrow(df))
    results245 <- rbind(results245, df)
  }
}

results245 %>%
  filter(rate_k > 0) -> results245

results <- rbind(results244, results245)
rm(df)
```

```{r}
results %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  mutate(kappa_coord=replace(kappa_coord, rate_k < 1, NA)) %>% 
  ggplot(aes(x=osc_rate, y=kappa_coord, group=interaction(osc_rate, homeo), color=homeo)) +
  geom_boxplot() +
  theme_classic() +
  scale_color_grey()
```

```{r}
results %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  mutate(kappa_coord=replace(kappa_coord, rate_k < 1, NA)) %>% 
  ggplot(aes(x=osc_rate, y=rate_k, group=interaction(osc_rate, homeo), color=homeo)) +
  geom_boxplot() +
  theme_classic() +
  scale_color_grey()
```

### 2019-05-28 resistingrhythm/analysis/exp249-253.Rmd
Analyze 249-253

---
title: "Analysis : exp249-253 analysis"
output: html_notebook
---

```{r, message=FALSE}
library(ggplot2)
library(dplyr)
library(magrittr)
library(readr)
library(gridExtra)
library(grid)
library(ggpubr)
library(cowplot)

data_path <- "~/Code/resistingrhythm/data/"
```

# Load all data

- Explore gamma=60Hz, gamma=90Hz, ripple=150 Hz

```{r, message=FALSE}
# ----------------------------------------------------------------------
# Load 8 Hz theta AMPA
# 16: Burst E, with H
exp_code <- 224
osc_codes <- c(100, 105, 110, 115, 120, 125, 130)
osc_rates <- c(0, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0)
stim_codes <- c(3, 4) # 4

results224 <- NULL
for(i in 1:length(osc_codes)){
  for(s_c in stim_codes){
    o_c <- osc_codes[i]
    o_r <- osc_rates[i]

    # Load the csv
    df <- read_csv(paste(data_path, 
                         "exp", as.character(exp_code), 
                         "_stim", as.character(s_c), 
                         "_burst", as.character(o_c),
                         ".csv", sep=""))

    # Add metadata
    df$osc_code <- rep(o_c, nrow(df))
    df$osc_rate <- rep(o_r, nrow(df))
    df$stim_code <- rep(s_c, nrow(df))
    df$synapse <- rep("AMPA", nrow(df))
    df$homeo <- rep("Homeostasis", nrow(df))
    df$freq <- rep(8, nrow(df))
    df$freq_name <- rep("Theta (8 Hz)", nrow(df))
    results224 <- rbind(results224, df)
  }
}
results224 %>%
  filter(rate_k > 0) -> results224

# 22: Burst E, NO H @ 8 hz
exp_code <- 220
osc_codes <- c(100, 105, 110, 115, 120, 125, 130)
osc_rates <- c(0, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0)
stim_codes <- c(3, 4)

results220 <- NULL
for(i in 1:length(osc_codes)){
  for(s_c in stim_codes){
    o_c <- osc_codes[i]
    o_r <- osc_rates[i]

    # Load the csv
    df <- read_csv(paste(data_path, 
                         "exp", as.character(exp_code), 
                         "_stim", as.character(s_c), 
                         "_osc", as.character(o_c),
                         ".csv", sep=""))

    # Add metadata
    df$osc_code <- rep(o_c, nrow(df))
    df$osc_rate <- rep(o_r, nrow(df))
    df$stim_code <- rep(s_c, nrow(df))
    df$synapse <- rep("AMPA", nrow(df))
    df$homeo <- rep("No homeostasis", nrow(df))
    df$freq <- rep(8, nrow(df))
    df$freq_name <- rep("Theta (8 Hz)", nrow(df))
    results220 <- rbind(results220, df)
  }
}
results220 %>%
  filter(rate_k > 0) -> results220

# ----------------------------------------------------------------------
# 60 Hz gamma
# exp248
exp_code <- 248
osc_codes <- c(100, 105, 110, 115, 120, 125, 130)
osc_rates <- c(0, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0)
stim_codes <- c(3, 4)

results248 <- NULL
for(i in 1:length(osc_codes)){
  for(s_c in stim_codes){
    o_c <- osc_codes[i]
    o_r <- osc_rates[i]

    # Load the csv
    df <- read_csv(paste(data_path, 
                         "exp", as.character(exp_code), 
                         "_stim", as.character(s_c), 
                         "_burst", as.character(o_c),
                         ".csv", sep=""))

    # Add metadata
    df$osc_code <- rep(o_c, nrow(df))
    df$osc_rate <- rep(o_r, nrow(df))
    df$stim_code <- rep(s_c, nrow(df))
    df$synapse <- rep("AMPA", nrow(df))
    df$homeo <- rep("Homeostasis", nrow(df))
    df$freq <- rep(60, nrow(df))
    df$freq_name <- rep("Slow gamma (60 Hz)", nrow(df))
    results248 <- rbind(results248, df)
  }
}
results248 %>%
  filter(rate_k > 0) -> results248

# exp249, no H
exp_code <- 249
osc_codes <- c(100, 105, 110, 115, 120, 125, 130)
osc_rates <- c(0, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0)
stim_codes <- c(3, 4)

results249 <- NULL
for(i in 1:length(osc_codes)){
  for(s_c in stim_codes){
    o_c <- osc_codes[i]
    o_r <- osc_rates[i]

    # Load the csv
    df <- read_csv(paste(data_path, 
                         "exp", as.character(exp_code), 
                         "_stim", as.character(s_c), 
                         "_burst", as.character(o_c),
                         ".csv", sep=""))

    # Add metadata
    df$osc_code <- rep(o_c, nrow(df))
    df$osc_rate <- rep(o_r, nrow(df))
    df$stim_code <- rep(s_c, nrow(df))
    df$synapse <- rep("AMPA", nrow(df))
    df$freq <- rep(60, nrow(df))
    df$freq_name <- rep("Slow gamma (60 Hz)", nrow(df))
    df$homeo <- rep("No homeostasis", nrow(df))
    results249 <- rbind(results249, df)
  }
}
results249 %>%
  filter(rate_k > 0) -> results249

# ----------------------------------------------------------------------
# 90 Hz gmma
# exp250, w H
exp_code <- 250
osc_codes <- c(100, 105, 110, 115, 120, 125, 130)
osc_rates <- c(0, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0)
stim_codes <- c(3, 4)

results250 <- NULL
for(i in 1:length(osc_codes)){
  for(s_c in stim_codes){
    o_c <- osc_codes[i]
    o_r <- osc_rates[i]

    # Load the csv
    df <- read_csv(paste(data_path, 
                         "exp", as.character(exp_code), 
                         "_stim", as.character(s_c), 
                         "_burst", as.character(o_c),
                         ".csv", sep=""))

    # Add metadata
    df$osc_code <- rep(o_c, nrow(df))
    df$osc_rate <- rep(o_r, nrow(df))
    df$stim_code <- rep(s_c, nrow(df))
    df$synapse <- rep("AMPA", nrow(df))
    df$freq <- rep(90, nrow(df))
    df$freq_name <- rep("Fast gamma (90 Hz)", nrow(df))
    df$homeo <- rep("Homeostasis", nrow(df))
    results250 <- rbind(results250, df)
  }
}
results250 %>%
  filter(rate_k > 0) -> results250

# exp251, no H
exp_code <- 251
osc_codes <- c(100, 105, 110, 115, 120, 125, 130)
osc_rates <- c(0, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0)
stim_codes <- c(3, 4)

results251 <- NULL
for(i in 1:length(osc_codes)){
  for(s_c in stim_codes){
    o_c <- osc_codes[i]
    o_r <- osc_rates[i]

    # Load the csv
    df <- read_csv(paste(data_path, 
                         "exp", as.character(exp_code), 
                         "_stim", as.character(s_c), 
                         "_burst", as.character(o_c),
                         ".csv", sep=""))

    # Add metadata
    df$osc_code <- rep(o_c, nrow(df))
    df$osc_rate <- rep(o_r, nrow(df))
    df$stim_code <- rep(s_c, nrow(df))
    df$synapse <- rep("AMPA", nrow(df))
    df$freq <- rep(90, nrow(df))
    df$freq_name <- rep("Fast gamma (90 Hz)", nrow(df))
    df$homeo <- rep("No homeostasis", nrow(df))
    results251 <- rbind(results251, df)
  }
}
results251 %>%
  filter(rate_k > 0) -> results251

# ----------------------------------------------------------------------
# 150 Hz ripple

# exp252 w/ H
exp_code <- 252
osc_codes <- c(100, 105, 110, 115, 120, 125, 130)
osc_rates <- c(0, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0)
stim_codes <- c(3, 4)

results252 <- NULL
for(i in 1:length(osc_codes)){
  for(s_c in stim_codes){
    o_c <- osc_codes[i]
    o_r <- osc_rates[i]

    # Load the csv
    df <- read_csv(paste(data_path, 
                         "exp", as.character(exp_code), 
                         "_stim", as.character(s_c), 
                         "_burst", as.character(o_c),
                         ".csv", sep=""))

    # Add metadata
    df$osc_code <- rep(o_c, nrow(df))
    df$osc_rate <- rep(o_r, nrow(df))
    df$stim_code <- rep(s_c, nrow(df))
    df$synapse <- rep("AMPA", nrow(df))
    df$freq <- rep(150, nrow(df))
    df$freq_name <- rep("Ripple (150 Hz)", nrow(df))
    df$homeo <- rep("Homeostasis", nrow(df))
    results252 <- rbind(results252, df)
  }
}
results252 %>%
  filter(rate_k > 0) -> results252

# exp253, no H
exp_code <- 253
osc_codes <- c(100, 105, 110, 115, 120, 125, 130)
osc_rates <- c(0, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0)
stim_codes <- c(3, 4)

results253 <- NULL
for(i in 1:length(osc_codes)){
  for(s_c in stim_codes){
    o_c <- osc_codes[i]
    o_r <- osc_rates[i]

    # Load the csv
    df <- read_csv(paste(data_path, 
                         "exp", as.character(exp_code), 
                         "_stim", as.character(s_c), 
                         "_burst", as.character(o_c),
                         ".csv", sep=""))

    # Add metadata
    df$osc_code <- rep(o_c, nrow(df))
    df$osc_rate <- rep(o_r, nrow(df))
    df$stim_code <- rep(s_c, nrow(df))
    df$synapse <- rep("AMPA", nrow(df))
    df$freq <- rep(150, nrow(df))
    df$freq_name <- rep("Ripple (150 Hz)", nrow(df))
    df$homeo <- rep("No homeostasis", nrow(df))
    results253 <- rbind(results253, df)
  }
}
results253 %>%
  filter(rate_k > 0) -> results253

results <- rbind(
  results220, results224, results248, results249, results250, results251, results252, results253)
results$freq_name <- factor(results$freq_name, 
                               levels=c("Theta (8 Hz)", "Slow gamma (60 Hz)", "Fast gamma (90 Hz)", "Ripple (150 Hz)"))
```

```{r}
results %>% 
  ggplot(aes(x=osc_rate, y=kappa_coord, group=interaction(osc_rate, homeo), color=homeo)) +
  geom_boxplot() +
  theme_classic() +
  scale_color_grey() +
  facet_grid(.~freq_name, scales = "free")
```

```{r, fig.width=4, fig.height=1.2}
results %>% 
  ggplot(aes(x=osc_rate, y=rate_k, group=interaction(osc_rate, homeo), color=homeo)) +
  geom_boxplot() +
  theme_classic() +
  scale_color_grey() + 
  facet_grid(.~freq_name, scales = "free")
```

### 2019-05-28 resistingrhythm/analysis/exp254-267.Rmd
Add analysis for exp254-275

---
title: "Analysis : exp249-253 analysis"
output: html_notebook
---

```{r, message=FALSE}
library(ggplot2)
library(dplyr)
library(magrittr)
library(readr)
library(gridExtra)
library(grid)
library(ggpubr)
library(cowplot)

data_path <- "~/Code/resistingrhythm/data/"
```

# Load all data

- Explore gamma=60Hz, gamma=90Hz, ripple=150 Hz

```{r, message=FALSE}
# ----------------------------------------------------------------------
# Load 8 Hz theta AMPA
# 16: Burst E, with H
exp_code <- 221
osc_codes <- c(100, 105, 110, 115, 120, 125, 130)
osc_rates <- c(0, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0)
stim_codes <- c(3, 4) # 4

results221 <- NULL
for(i in 1:length(osc_codes)){
  for(s_c in stim_codes){
    o_c <- osc_codes[i]
    o_r <- osc_rates[i]

    # Load the csv
    df <- read_csv(paste(data_path, 
                         "exp", as.character(exp_code), 
                         "_stim", as.character(s_c), 
                         "_osc", as.character(o_c),
                         ".csv", sep=""))

    # Add metadata
    df$osc_code <- rep(o_c, nrow(df))
    df$osc_rate <- rep(o_r, nrow(df))
    df$stim_code <- rep(s_c, nrow(df))
    df$synapse <- rep("AMPA", nrow(df))
    df$homeo <- rep("Homeostasis", nrow(df))
    df$freq <- rep(8, nrow(df))
    results221 <- rbind(results221, df)
  }
}
results221 %>%
  filter(rate_k > 0) -> results221

# 22: Burst E, NO H @ 8 hz
exp_code <- 220
osc_codes <- c(100, 105, 110, 115, 120, 125, 130)
osc_rates <- c(0, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0)
stim_codes <- c(3, 4)

results220 <- NULL
for(i in 1:length(osc_codes)){
  for(s_c in stim_codes){
    o_c <- osc_codes[i]
    o_r <- osc_rates[i]

    # Load the csv
    df <- read_csv(paste(data_path, 
                         "exp", as.character(exp_code), 
                         "_stim", as.character(s_c), 
                         "_osc", as.character(o_c),
                         ".csv", sep=""))

    # Add metadata
    df$osc_code <- rep(o_c, nrow(df))
    df$osc_rate <- rep(o_r, nrow(df))
    df$stim_code <- rep(s_c, nrow(df))
    df$synapse <- rep("AMPA", nrow(df))
    df$homeo <- rep("No homeostasis", nrow(df))
    df$freq <- rep(8, nrow(df))
    results220 <- rbind(results220, df)
  }
}
results220 %>%
  filter(rate_k > 0) -> results220

# ----------------------------------------------------------------------
# @ 6 Hz
#
# No H
exp_code <- 254
osc_codes <- c(100, 105, 110, 115, 120, 125, 130)
osc_rates <- c(0, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0)
stim_codes <- c(3, 4)

results254 <- NULL
for(i in 1:length(osc_codes)){
  for(s_c in stim_codes){
    o_c <- osc_codes[i]
    o_r <- osc_rates[i]

    # Load the csv
    df <- read_csv(paste(data_path, 
                         "exp", as.character(exp_code), 
                         "_stim", as.character(s_c), 
                         "lfp", as.character(o_c),
                         ".csv", sep=""))

    # Add metadata
    df$osc_code <- rep(o_c, nrow(df))
    df$osc_rate <- rep(o_r, nrow(df))
    df$stim_code <- rep(s_c, nrow(df))
    df$synapse <- rep("AMPA", nrow(df))
    df$homeo <- rep("No homeostasis", nrow(df))
    df$freq <- rep(6, nrow(df))
    results254 <- rbind(results254, df)
  }
}
results254 %>%
  filter(rate_k > 0) -> results254

# H
exp_code <- 255
osc_codes <- c(100, 105, 110, 115, 120, 125, 130)
osc_rates <- c(0, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0)
stim_codes <- c(3, 4)

results255 <- NULL
for(i in 1:length(osc_codes)){
  for(s_c in stim_codes){
    o_c <- osc_codes[i]
    o_r <- osc_rates[i]

    # Load the csv
    df <- read_csv(paste(data_path, 
                         "exp", as.character(exp_code), 
                         "_stim", as.character(s_c), 
                         "_lfp", as.character(o_c),
                         ".csv", sep=""))

    # Add metadata
    df$osc_code <- rep(o_c, nrow(df))
    df$osc_rate <- rep(o_r, nrow(df))
    df$stim_code <- rep(s_c, nrow(df))
    df$synapse <- rep("AMPA", nrow(df))
    df$freq <- rep(6, nrow(df))
    df$homeo <- rep("Homeostasis", nrow(df))
    results255 <- rbind(results255, df)
  }
}
results255 %>%
  filter(rate_k > 0) -> results255

# ----------------------------------------------------------------------
# @ 7 Hz
#
# No H
exp_code <- 258
osc_codes <- c(100, 105, 110, 115, 120, 125, 130)
osc_rates <- c(0, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0)
stim_codes <- c(3, 4)

results258 <- NULL
for(i in 1:length(osc_codes)){
  for(s_c in stim_codes){
    o_c <- osc_codes[i]
    o_r <- osc_rates[i]

    # Load the csv
    df <- read_csv(paste(data_path, 
                         "exp", as.character(exp_code), 
                         "_stim", as.character(s_c), 
                         "lfp", as.character(o_c),
                         ".csv", sep=""))

    # Add metadata
    df$osc_code <- rep(o_c, nrow(df))
    df$osc_rate <- rep(o_r, nrow(df))
    df$stim_code <- rep(s_c, nrow(df))
    df$synapse <- rep("AMPA", nrow(df))
    df$homeo <- rep("No homeostasis", nrow(df))
    df$freq <- rep(7, nrow(df))
    results258 <- rbind(results258, df)
  }
}
results258 %>%
  filter(rate_k > 0) -> results258

# H
exp_code <- 259
osc_codes <- c(100, 105, 110, 115, 120, 125, 130)
osc_rates <- c(0, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0)
stim_codes <- c(3, 4)

results259 <- NULL
for(i in 1:length(osc_codes)){
  for(s_c in stim_codes){
    o_c <- osc_codes[i]
    o_r <- osc_rates[i]

    # Load the csv
    df <- read_csv(paste(data_path, 
                         "exp", as.character(exp_code), 
                         "_stim", as.character(s_c), 
                         "_lfp", as.character(o_c),
                         ".csv", sep=""))

    # Add metadata
    df$osc_code <- rep(o_c, nrow(df))
    df$osc_rate <- rep(o_r, nrow(df))
    df$stim_code <- rep(s_c, nrow(df))
    df$synapse <- rep("AMPA", nrow(df))
    df$freq <- rep(7, nrow(df))
    df$homeo <- rep("Homeostasis", nrow(df))
    results259 <- rbind(results259, df)
  }
}
results259 %>%
  filter(rate_k > 0) -> results259

# ----------------------------------------------------------------------
# @ 9 Hz
#
# No H
exp_code <- 262
osc_codes <- c(100, 105, 110, 115, 120, 125, 130)
osc_rates <- c(0, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0)
stim_codes <- c(3, 4)

results262 <- NULL
for(i in 1:length(osc_codes)){
  for(s_c in stim_codes){
    o_c <- osc_codes[i]
    o_r <- osc_rates[i]

    # Load the csv
    df <- read_csv(paste(data_path, 
                         "exp", as.character(exp_code), 
                         "_stim", as.character(s_c), 
                         "lfp", as.character(o_c),
                         ".csv", sep=""))

    # Add metadata
    df$osc_code <- rep(o_c, nrow(df))
    df$osc_rate <- rep(o_r, nrow(df))
    df$stim_code <- rep(s_c, nrow(df))
    df$synapse <- rep("AMPA", nrow(df))
    df$homeo <- rep("No homeostasis", nrow(df))
    df$freq <- rep(9, nrow(df))
    results262 <- rbind(results262, df)
  }
}
results262 %>%
  filter(rate_k > 0) -> results262

# H
exp_code <- 263
osc_codes <- c(100, 105, 110, 115, 120, 125, 130)
osc_rates <- c(0, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0)
stim_codes <- c(3, 4)

results263 <- NULL
for(i in 1:length(osc_codes)){
  for(s_c in stim_codes){
    o_c <- osc_codes[i]
    o_r <- osc_rates[i]

    # Load the csv
    df <- read_csv(paste(data_path, 
                         "exp", as.character(exp_code), 
                         "_stim", as.character(s_c), 
                         "_lfp", as.character(o_c),
                         ".csv", sep=""))

    # Add metadata
    df$osc_code <- rep(o_c, nrow(df))
    df$osc_rate <- rep(o_r, nrow(df))
    df$stim_code <- rep(s_c, nrow(df))
    df$synapse <- rep("AMPA", nrow(df))
    df$freq <- rep(9, nrow(df))
    df$homeo <- rep("Homeostasis", nrow(df))
    results263 <- rbind(results263, df)
  }
}
results263 %>%
  filter(rate_k > 0) -> results263

# ----------------------------------------------------------------------
# @ 10 Hz
#
# No H
exp_code <- 266
osc_codes <- c(100, 105, 110, 115, 120, 125, 130)
osc_rates <- c(0, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0)
stim_codes <- c(3, 4)

results266 <- NULL
for(i in 1:length(osc_codes)){
  for(s_c in stim_codes){
    o_c <- osc_codes[i]
    o_r <- osc_rates[i]

    # Load the csv
    df <- read_csv(paste(data_path, 
                         "exp", as.character(exp_code), 
                         "_stim", as.character(s_c), 
                         "lfp", as.character(o_c),
                         ".csv", sep=""))

    # Add metadata
    df$osc_code <- rep(o_c, nrow(df))
    df$osc_rate <- rep(o_r, nrow(df))
    df$stim_code <- rep(s_c, nrow(df))
    df$synapse <- rep("AMPA", nrow(df))
    df$homeo <- rep("No homeostasis", nrow(df))
    df$freq <- rep(10, nrow(df))
    results266 <- rbind(results266, df)
  }
}
results266 %>%
  filter(rate_k > 0) -> results266

# H
exp_code <- 267
osc_codes <- c(100, 105, 110, 115, 120, 125, 130)
osc_rates <- c(0, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0)
stim_codes <- c(3, 4)

results267 <- NULL
for(i in 1:length(osc_codes)){
  for(s_c in stim_codes){
    o_c <- osc_codes[i]
    o_r <- osc_rates[i]

    # Load the csv
    df <- read_csv(paste(data_path, 
                         "exp", as.character(exp_code), 
                         "_stim", as.character(s_c), 
                         "_lfp", as.character(o_c),
                         ".csv", sep=""))

    # Add metadata
    df$osc_code <- rep(o_c, nrow(df))
    df$osc_rate <- rep(o_r, nrow(df))
    df$stim_code <- rep(s_c, nrow(df))
    df$synapse <- rep("AMPA", nrow(df))
    df$freq <- rep(10, nrow(df))
    df$homeo <- rep("Homeostasis", nrow(df))
    results267 <- rbind(results267, df)
  }
}
results267 %>%
  filter(rate_k > 0) -> results267

results <- rbind(
  results220, results221, results254, results255, results258, results259, results262, results263, results266, results267)
```

```{r}
results %>% 
  ggplot(aes(x=osc_rate, y=kappa_coord, group=interaction(osc_rate, homeo), color=homeo)) +
  geom_boxplot() +
  theme_classic() +
  scale_color_grey() +
  facet_grid(.~freq, scales = "free")
```

```{r, fig.width=4, fig.height=1.2}
results %>% 
  ggplot(aes(x=osc_rate, y=rate_k, group=interaction(osc_rate, homeo), color=homeo)) +
  geom_boxplot() +
  theme_classic() +
  scale_color_grey() + 
  facet_grid(.~freq, scales = "free")
```

### 2019-06-07 resistingrhythm/analysis/exp234_242.Rmd
....

--- 2019-05-08 resistingrhythm/analysis/paper_figures_v4.Rmd
@@
 ---
-title: "Analysis : exp220 - 228 (Nov 2018, for J Neurophys draft 2018)"
+title: "Analysis : exp234-242 g_Ca dynamic reactivation"
 output: html_notebook
@@
 # Load all data
+
+I turned d(g_Ca)/dt back on but don't have record of confirming everything way. I've been using sims without it...
 ```{r, message=FALSE}
@@
 # 16: Burst E, with H
-exp_code <- 224
+exp_code <- 238
 osc_codes <- c(100, 101, 102, 103, 104, 105, 110, 115, 120, 125, 130)

### 2019-06-07 resistingrhythm/exp/homeostasis_experiments.py
Exposed G_KCa

@@ -35,6 +35,7 @@ def run(run_name,
         bias_in=0,
         g_l=1.0e-3,
         g_Ca=0.03e-3,
+        G_KCa=60e-3,
         sigma=0,
         num_trials=2,
         seed_value=42,
@@ -136,6 +137,7 @@ def run(run_name,
             sigma=sigma,
             g_l=g_l,
             g_Ca=g_Ca,
+            G_KCa=G_KCa,
             w_in=w,
             w_osc=w,
             tau_h=tau_h,
@@ -162,6 +164,9 @@ def run(run_name,
             Ca_target=Ca_target,
             bias_in=bias_in,
             sigma=sigma,
+            g_l=g_l,
+            g_Ca=g_Ca,
+            G_KCa=G_KCa,
             w_in=w,
             w_osc=w,
             V_osc=V_osc,

### 2019-06-07 resistingrhythm/neurons.py

@@ -28,6 +28,7 @@ def HHH(time,
         tau_h=10,
         g_l=1.0e-3,
         g_Ca=0.03e-3,
+        G_KCa=60e-3,
         sigma=0,
         N=1,
         w_in=0.8e-9,
@@ -112,7 +113,7 @@ def HHH(time,
     # dg/dt
     G_Na = 360 * msiemens
     G_K = 120 * msiemens  # Try 90?
-    G_KCa = 60 * msiemens
+    G_KCa *= siemens
     g_Na = G_Na / 2
     g_K = G_K / 2
     g_KCa = G_KCa / 2

### 2019-06-12 resistingrhythm/neurons.py
Change for [Ca] set at Ca_target at the start.
G_Ca freed from g_Ca at init

G_Ca exposed in HHH and run

@@ -28,6 +28,7 @@ def HHH(time,
         tau_h=10,
         g_l=1.0e-3,
         g_Ca=0.03e-3,
+        G_Ca=60e-3,
         G_KCa=60e-3,
         sigma=0,
         N=1,
@@ -84,6 +85,7 @@ def HHH(time,
     # 0.001
     # **To correct for that, we use mmolar in all our unit conversions.**
     Ca_target *= mmolar
+    Ca = Ca_target
     tau_h *= second
 
     # ----------------------------------------------------
@@ -108,13 +110,14 @@ def HHH(time,
     V1 = -50 * mV
     V2 = 10 * mV
     g_Ca *= siemens
-    G_Ca = g_Ca * 2
+    G_Ca *= siemens
 
     # dg/dt
     G_Na = 360 * msiemens
     G_K = 120 * msiemens  # Try 90?
     G_KCa *= siemens
-    g_Na = G_Na / 2
+
+    g_Na = G_Na / 2  # Init
     g_K = G_K / 2
     g_KCa = G_KCa / 2
 

### 2019-06-12 resistingrhythm/exp/homeostasis_experiments.py
FIX exposure of G_Ca in run

@@ -35,6 +35,7 @@ def run(run_name,
         bias_in=0,
         g_l=1.0e-3,
         g_Ca=0.03e-3,
+        G_Ca=60e-3,
         G_KCa=60e-3,
         sigma=0,
         num_trials=2,
@@ -137,6 +138,7 @@ def run(run_name,
             sigma=sigma,
             g_l=g_l,
             g_Ca=g_Ca,
+            G_Ca=G_Ca,
             G_KCa=G_KCa,
             w_in=w,
             w_osc=w,
@@ -165,6 +167,7 @@ def run(run_name,
             bias_in=bias_in,
             sigma=sigma,
             g_l=g_l,
+            g_Ca=g_Ca,
             g_Ca=g_Ca,
             G_KCa=G_KCa,
             w_in=w,

### 2019-06-12 resistingrhythm/exp/homeostasis_experiments.py
FIX last FIX

@@ -168,7 +168,7 @@ def run(run_name,
             sigma=sigma,
             g_l=g_l,
             g_Ca=g_Ca,
-            g_Ca=g_Ca,
+            G_Ca=g_Ca,
             G_KCa=G_KCa,
             w_in=w,
             w_osc=w,

### 2019-06-12 resistingrhythm/neurons.py
Test: comment out d_Ca dynamics.

@@ -162,8 +162,8 @@ def HHH(time,
     if homeostasis:
         eqs += """ 
         dg_Na/dt = (1 / tau_h) * (G_Na / (1 + exp(1 * (Ca - Ca_target)/delta)) - g_Na) : siemens 
-        dg_Ca/dt = (1 / tau_h) * (G_Ca / (1 + exp(1 * (Ca - Ca_target)/delta)) - g_Ca) : siemens 
-        # g_Ca : siemens
+        # dg_Ca/dt = (1 / tau_h) * (G_Ca / (1 + exp(1 * (Ca - Ca_target)/delta)) - g_Ca) : siemens 
+        g_Ca : siemens
         dg_K/dt = (1 / tau_h) * (G_K / (1 + exp(-1 * (Ca - Ca_target)/delta)) - g_K) : siemens 
         dg_KCa/dt = (1 / tau_h) * (G_KCa / (1 + exp(-1 * (Ca - Ca_target)/delta)) - g_KCa) : siemens 
         """

### 2019-06-14 resistingrhythm/exp/homeostasis_experiments.py
Fix typo

@@ -168,7 +168,7 @@ def run(run_name,
             sigma=sigma,
             g_l=g_l,
             g_Ca=g_Ca,
-            G_Ca=g_Ca,
+            G_Ca=G_Ca,
             G_KCa=G_KCa,
             w_in=w,
             w_osc=w,

### 2019-06-14 resistingrhythm/exp/homeostasis_experiments.py
Added dynamic_calcium_gate flag

@@ -41,6 +41,7 @@ def run(run_name,
         num_trials=2,
         seed_value=42,
         homeostasis=True,
+        dynamic_calcium_gate=False,
         verbose=False):
     """Run a HHH experiment"""
 
@@ -147,7 +148,8 @@ def run(run_name,
             burn_time=burn_t,
             seed_value=seed_value + k,
             record_traces=True,
-            homeostasis=homeostasis)
+            homeostasis=homeostasis,
+            dynamic_calcium_gate=dynamic_calcium_gate)
 
         ns_ref, ts_ref = filter_spikes(results_ref["ns"], results_ref["ts"],
                                        a_window)
@@ -179,7 +181,8 @@ def run(run_name,
             burn_time=burn_t,
             seed_value=seed_value + k,
             record_traces=True,
-            homeostasis=homeostasis)
+            homeostasis=homeostasis,
+            dynamic_calcium_gate=dynamic_calcium_gate)
 
         # -
         if verbose:

### 2019-06-14 resistingrhythm/neurons.py

@@ -43,6 +43,7 @@ def HHH(time,
         burn_time=0,
         time_step=1e-5,
         homeostasis=True,
+        dynamic_calcium_gate=False,
         record_traces=True,
         progress_report=None,
         seed_value=None):
@@ -162,11 +163,15 @@ def HHH(time,
     if homeostasis:
         eqs += """ 
         dg_Na/dt = (1 / tau_h) * (G_Na / (1 + exp(1 * (Ca - Ca_target)/delta)) - g_Na) : siemens 
-        # dg_Ca/dt = (1 / tau_h) * (G_Ca / (1 + exp(1 * (Ca - Ca_target)/delta)) - g_Ca) : siemens 
-        g_Ca : siemens
         dg_K/dt = (1 / tau_h) * (G_K / (1 + exp(-1 * (Ca - Ca_target)/delta)) - g_K) : siemens 
         dg_KCa/dt = (1 / tau_h) * (G_KCa / (1 + exp(-1 * (Ca - Ca_target)/delta)) - g_KCa) : siemens 
         """
+        if dynamic_calcium_gate:
+            eqs += """dg_Ca/dt = (1 / tau_h) * (G_Ca / (1 + exp(1 * (Ca - Ca_target)/delta)) - g_Ca) : siemens
+            """
+        else:
+            eqs += """g_Ca : siemens
+            """
     else:
         eqs += """
         g_Na : siemens

### 2019-07-18 resistingrhythm/analysis/exp328-339.Rmd
Add analysis for 328-339

---
title: "Analysis : exp249-253 analysis"
output: html_notebook
---

```{r, message=FALSE}
library(ggplot2)
library(dplyr)
library(magrittr)
library(readr)
library(gridExtra)
library(grid)
library(ggpubr)
library(cowplot)

data_path <- "~/Code/resistingrhythm/data/"
```

# Load all data

- Explore gamma=60Hz, gamma=90Hz, ripple=150 Hz

```{r, message=FALSE}
# ----------------------------------------------------------------------
# Load 8 Hz theta AMPA
# 16: Sustained E, with H
exp_code <- 221
osc_codes <- c(100, 105, 110, 115, 120, 125, 130)
osc_rates <- c(0, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0)
stim_codes <- c(3, 4) # 4

results221 <- NULL
for(i in 1:length(osc_codes)){
  for(s_c in stim_codes){
    o_c <- osc_codes[i]
    o_r <- osc_rates[i]

    # Load the csv
    df <- read_csv(paste(data_path, 
                         "exp", as.character(exp_code), 
                         "_stim", as.character(s_c), 
                         "_osc", as.character(o_c),
                         ".csv", sep=""))

    # Add metadata
    df$osc_code <- rep(o_c, nrow(df))
    df$osc_rate <- rep(o_r, nrow(df))
    df$stim_code <- rep(s_c, nrow(df))
    df$synapse <- rep("AMPA", nrow(df))
    df$homeo <- rep("Homeostasis", nrow(df))
    df$freq <- rep(8, nrow(df))
    df$kind <- rep("Sustained", nrow(df))
    results221 <- rbind(results221, df)
  }
}

# 22: Burst E, NO H @ 8 hz
exp_code <- 220
osc_codes <- c(100, 105, 110, 115, 120, 125, 130)
osc_rates <- c(0, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0)
stim_codes <- c(3, 4)

results220 <- NULL
for(i in 1:length(osc_codes)){
  for(s_c in stim_codes){
    o_c <- osc_codes[i]
    o_r <- osc_rates[i]

    # Load the csv
    df <- read_csv(paste(data_path, 
                         "exp", as.character(exp_code), 
                         "_stim", as.character(s_c), 
                         "_osc", as.character(o_c),
                         ".csv", sep=""))

    # Add metadata
    df$osc_code <- rep(o_c, nrow(df))
    df$osc_rate <- rep(o_r, nrow(df))
    df$stim_code <- rep(s_c, nrow(df))
    df$synapse <- rep("AMPA", nrow(df))
    df$homeo <- rep("No homeostasis", nrow(df))
    df$freq <- rep(8, nrow(df))
    df$kind <- rep("Sustained", nrow(df))

    results220 <- rbind(results220, df)
  }
}

# ----------------------------------------------------------------------
# @ 60 Hz, burst
#
# No H
exp_code <- 329
osc_codes <- c("0", "0.5", "1", "1.5", "3", "6", "12")
osc_rates <- c(0, 0.5, 1, 1.5, 3, 6, 12)
stim_codes <- c(3, 4)

results329 <- NULL
for(i in 1:length(osc_codes)){
  for(s_c in stim_codes){
    o_c <- osc_codes[i]
    o_r <- osc_rates[i]

    # Load the csv
    df <- read_csv(paste(data_path, 
                         "exp", as.character(exp_code), 
                         "_stim", as.character(s_c), 
                         "_burst", as.character(o_c),
                         ".csv", sep=""))

    # Add metadata
    df$osc_code <- rep(o_c, nrow(df))
    df$osc_rate <- rep(o_r, nrow(df))
    df$stim_code <- rep(s_c, nrow(df))
    df$synapse <- rep("AMPA", nrow(df))
    df$homeo <- rep("No homeostasis", nrow(df))
    df$freq <- rep(60, nrow(df))
    df$kind <- rep("Burst", nrow(df))

    results329 <- rbind(results329, df)
  }
}

# H
exp_code <- 328
osc_codes <- c("0", "0.5", "1", "1.5", "3", "6", "12")
osc_rates <- c(0, 0.5, 1, 1.5, 3, 6, 12)
stim_codes <- c(3, 4)

results328 <- NULL
for(i in 1:length(osc_codes)){
  for(s_c in stim_codes){
    o_c <- osc_codes[i]
    o_r <- osc_rates[i]

    # Load the csv
    df <- read_csv(paste(data_path, 
                         "exp", as.character(exp_code), 
                         "_stim", as.character(s_c), 
                         "_burst", as.character(o_c),
                         ".csv", sep=""))

    # Add metadata
    df$osc_code <- rep(o_c, nrow(df))
    df$osc_rate <- rep(o_r, nrow(df))
    df$stim_code <- rep(s_c, nrow(df))
    df$synapse <- rep("AMPA", nrow(df))
    df$homeo <- rep("Homeostasis", nrow(df))
    df$freq <- rep(60, nrow(df))
    df$kind <- rep("Burst", nrow(df))

    results328 <- rbind(results328, df)
  }
}

# ----------------------------------------------------------------------
# @ 60 Hz, sustained
#
# No H
exp_code <- 331
osc_codes <- c("0", "0.5", "1", "1.5", "3", "6", "12")
osc_rates <- c(0, 0.5, 1, 1.5, 3, 6, 12)
stim_codes <- c(3, 4)

results331 <- NULL
for(i in 1:length(osc_codes)){
  for(s_c in stim_codes){
    o_c <- osc_codes[i]
    o_r <- osc_rates[i]

    # Load the csv
    df <- read_csv(paste(data_path, 
                         "exp", as.character(exp_code), 
                         "_stim", as.character(s_c), 
                         "_burst", as.character(o_c),
                         ".csv", sep=""))

    # Add metadata
    df$osc_code <- rep(o_c, nrow(df))
    df$osc_rate <- rep(o_r, nrow(df))
    df$stim_code <- rep(s_c, nrow(df))
    df$synapse <- rep("AMPA", nrow(df))
    df$homeo <- rep("No homeostasis", nrow(df))
    df$freq <- rep(60, nrow(df))
    df$kind <- rep("Sustained", nrow(df))

    results331 <- rbind(results331, df)
  }
}
results331 %>%
  filter(rate_k > 0) -> results331

# H
exp_code <- 330
osc_codes <- c("0", "0.5", "1", "1.5", "3", "6", "12")
osc_rates <- c(0, 0.5, 1, 1.5, 3, 6, 12)
stim_codes <- c(3, 4)

results330 <- NULL
for(i in 1:length(osc_codes)){
  for(s_c in stim_codes){
    o_c <- osc_codes[i]
    o_r <- osc_rates[i]

    # Load the csv
    df <- read_csv(paste(data_path, 
                         "exp", as.character(exp_code), 
                         "_stim", as.character(s_c), 
                         "_burst", as.character(o_c),
                         ".csv", sep=""))

    # Add metadata
    df$osc_code <- rep(o_c, nrow(df))
    df$osc_rate <- rep(o_r, nrow(df))
    df$stim_code <- rep(s_c, nrow(df))
    df$synapse <- rep("AMPA", nrow(df))
    df$homeo <- rep("Homeostasis", nrow(df))
    df$freq <- rep(60, nrow(df))
    df$kind <- rep("Sustained", nrow(df))

    results330 <- rbind(results330, df)
  }
}

# ----------------------------------------------------------------------
# ----------------------------------------------------------------------
# ----------------------------------------------------------------------
# @ 90 Hz, burst
#
# No H
exp_code <- 333
osc_codes <- c("0", "0.5", "1", "1.5", "3", "6", "12")
osc_rates <- c(0, 0.5, 1, 1.5, 3, 6, 12)
stim_codes <- c(3, 4)

results333 <- NULL
for(i in 1:length(osc_codes)){
  for(s_c in stim_codes){
    o_c <- osc_codes[i]
    o_r <- osc_rates[i]

    # Load the csv
    df <- read_csv(paste(data_path, 
                         "exp", as.character(exp_code), 
                         "_stim", as.character(s_c), 
                         "_burst", as.character(o_c),
                         ".csv", sep=""))

    # Add metadata
    df$osc_code <- rep(o_c, nrow(df))
    df$osc_rate <- rep(o_r, nrow(df))
    df$stim_code <- rep(s_c, nrow(df))
    df$synapse <- rep("AMPA", nrow(df))
    df$homeo <- rep("No homeostasis", nrow(df))
    df$freq <- rep(90, nrow(df))
    df$kind <- rep("Burst", nrow(df))

    results333 <- rbind(results333, df)
  }
}

# H
exp_code <- 332
osc_codes <- c("0", "0.5", "1", "1.5", "3", "6", "12")
osc_rates <- c(0, 0.5, 1, 1.5, 3, 6, 12)
stim_codes <- c(3, 4)

results332 <- NULL
for(i in 1:length(osc_codes)){
  for(s_c in stim_codes){
    o_c <- osc_codes[i]
    o_r <- osc_rates[i]

    # Load the csv
    df <- read_csv(paste(data_path, 
                         "exp", as.character(exp_code), 
                         "_stim", as.character(s_c), 
                         "_burst", as.character(o_c),
                         ".csv", sep=""))

    # Add metadata
    df$osc_code <- rep(o_c, nrow(df))
    df$osc_rate <- rep(o_r, nrow(df))
    df$stim_code <- rep(s_c, nrow(df))
    df$synapse <- rep("AMPA", nrow(df))
    df$homeo <- rep("Homeostasis", nrow(df))
    df$freq <- rep(90, nrow(df))
    df$kind <- rep("Burst", nrow(df))

    results332 <- rbind(results332, df)
  }
}

# ----------------------------------------------------------------------
# @ 90 Hz, sustained
#
# No H
exp_code <- 335
osc_codes <- c("0", "0.5", "1", "1.5", "3", "6", "12")
osc_rates <- c(0, 0.5, 1, 1.5, 3, 6, 12)
stim_codes <- c(3, 4)

results335 <- NULL
for(i in 1:length(osc_codes)){
  for(s_c in stim_codes){
    o_c <- osc_codes[i]
    o_r <- osc_rates[i]

    # Load the csv
    df <- read_csv(paste(data_path, 
                         "exp", as.character(exp_code), 
                         "_stim", as.character(s_c), 
                         "_burst", as.character(o_c),
                         ".csv", sep=""))

    # Add metadata
    df$osc_code <- rep(o_c, nrow(df))
    df$osc_rate <- rep(o_r, nrow(df))
    df$stim_code <- rep(s_c, nrow(df))
    df$synapse <- rep("AMPA", nrow(df))
    df$homeo <- rep("No homeostasis", nrow(df))
    df$freq <- rep(90, nrow(df))
    df$kind <- rep("Sustained", nrow(df))

    results335 <- rbind(results335, df)
  }
}

# H
exp_code <- 334
osc_codes <- c("0", "0.5", "1", "1.5", "3", "6", "12")
osc_rates <- c(0, 0.5, 1, 1.5, 3, 6, 12)
stim_codes <- c(3, 4)

results334 <- NULL
for(i in 1:length(osc_codes)){
  for(s_c in stim_codes){
    o_c <- osc_codes[i]
    o_r <- osc_rates[i]

    # Load the csv
    df <- read_csv(paste(data_path, 
                         "exp", as.character(exp_code), 
                         "_stim", as.character(s_c), 
                         "_burst", as.character(o_c),
                         ".csv", sep=""))

    # Add metadata
    df$osc_code <- rep(o_c, nrow(df))
    df$osc_rate <- rep(o_r, nrow(df))
    df$stim_code <- rep(s_c, nrow(df))
    df$synapse <- rep("AMPA", nrow(df))
    df$homeo <- rep("Homeostasis", nrow(df))
    df$freq <- rep(90, nrow(df))
    df$kind <- rep("Sustained", nrow(df))

    results334 <- rbind(results334, df)
  }
}

# ----------------------------------------------------------------------
# ----------------------------------------------------------------------
# ----------------------------------------------------------------------
# @ 150 Hz, burst
#
# No H
exp_code <- 337
osc_codes <- c("0", "0.5", "1", "1.5", "3", "6", "12")
osc_rates <- c(0, 0.5, 1, 1.5, 3, 6, 12)
stim_codes <- c(3, 4)

results337 <- NULL
for(i in 1:length(osc_codes)){
  for(s_c in stim_codes){
    o_c <- osc_codes[i]
    o_r <- osc_rates[i]

    # Load the csv
    df <- read_csv(paste(data_path, 
                         "exp", as.character(exp_code), 
                         "_stim", as.character(s_c), 
                         "_burst", as.character(o_c),
                         ".csv", sep=""))

    # Add metadata
    df$osc_code <- rep(o_c, nrow(df))
    df$osc_rate <- rep(o_r, nrow(df))
    df$stim_code <- rep(s_c, nrow(df))
    df$synapse <- rep("AMPA", nrow(df))
    df$homeo <- rep("No homeostasis", nrow(df))
    df$freq <- rep(150, nrow(df))
    df$kind <- rep("Burst", nrow(df))

    results337 <- rbind(results337, df)
  }
}

# H
exp_code <- 336
osc_codes <- c("0", "0.5", "1", "1.5", "3", "6", "12")
osc_rates <- c(0, 0.5, 1, 1.5, 3, 6, 12)
stim_codes <- c(3, 4)

results336 <- NULL
for(i in 1:length(osc_codes)){
  for(s_c in stim_codes){
    o_c <- osc_codes[i]
    o_r <- osc_rates[i]

    # Load the csv
    df <- read_csv(paste(data_path, 
                         "exp", as.character(exp_code), 
                         "_stim", as.character(s_c), 
                         "_burst", as.character(o_c),
                         ".csv", sep=""))

    # Add metadata
    df$osc_code <- rep(o_c, nrow(df))
    df$osc_rate <- rep(o_r, nrow(df))
    df$stim_code <- rep(s_c, nrow(df))
    df$synapse <- rep("AMPA", nrow(df))
    df$homeo <- rep("Homeostasis", nrow(df))
    df$freq <- rep(150, nrow(df))
    df$kind <- rep("Burst", nrow(df))

    results336 <- rbind(results336, df)
  }
}

# ----------------------------------------------------------------------
# @ 90 Hz, sustained
#
# No H
exp_code <- 339
osc_codes <- c("0", "0.5", "1", "1.5", "3", "6", "12")
osc_rates <- c(0, 0.5, 1, 1.5, 3, 6, 12)
stim_codes <- c(3, 4)

results339 <- NULL
for(i in 1:length(osc_codes)){
  for(s_c in stim_codes){
    o_c <- osc_codes[i]
    o_r <- osc_rates[i]

    # Load the csv
    df <- read_csv(paste(data_path, 
                         "exp", as.character(exp_code), 
                         "_stim", as.character(s_c), 
                         "_burst", as.character(o_c),
                         ".csv", sep=""))

    # Add metadata
    df$osc_code <- rep(o_c, nrow(df))
    df$osc_rate <- rep(o_r, nrow(df))
    df$stim_code <- rep(s_c, nrow(df))
    df$synapse <- rep("AMPA", nrow(df))
    df$homeo <- rep("No homeostasis", nrow(df))
    df$freq <- rep(150, nrow(df))
    df$kind <- rep("Sustained", nrow(df))

    results339 <- rbind(results339, df)
  }
}

# H
exp_code <- 338
osc_codes <- c("0", "0.5", "1", "1.5", "3", "6", "12")
osc_rates <- c(0, 0.5, 1, 1.5, 3, 6, 12)
stim_codes <- c(3, 4)

results338 <- NULL
for(i in 1:length(osc_codes)){
  for(s_c in stim_codes){
    o_c <- osc_codes[i]
    o_r <- osc_rates[i]

    # Load the csv
    df <- read_csv(paste(data_path, 
                         "exp", as.character(exp_code), 
                         "_stim", as.character(s_c), 
                         "_burst", as.character(o_c),
                         ".csv", sep=""))

    # Add metadata
    df$osc_code <- rep(o_c, nrow(df))
    df$osc_rate <- rep(o_r, nrow(df))
    df$stim_code <- rep(s_c, nrow(df))
    df$synapse <- rep("AMPA", nrow(df))
    df$homeo <- rep("Homeostasis", nrow(df))
    df$freq <- rep(150, nrow(df))
    df$kind <- rep("Sustained", nrow(df))

    results338 <- rbind(results338, df)
  }
}

# ----------------------------------------------------
results <- rbind(
  results220, results221, results328, results329, results330, results331, results332, results333, results334, results335,
  results336, results337, results338, results339
)
rm(results220, results221, results328, results329, results330, results331, results332, results333, results334, results335,
  results336, results337, results338, results339, df)
```

```{r, fig.height=2.5, fig.width=2.25}
results %>% 
  filter(osc_rate < 1.5, freq < 150) %>% 
  ggplot(aes(x=osc_rate, y=kappa_coord, group=interaction(osc_rate, homeo), color=homeo)) +
  geom_boxplot() +
  theme_classic() +
  scale_color_grey() +
  facet_grid(freq~kind, scales = "free")
```

```{r, fig.height=2.5, fig.width=2.25}
results %>% 
  filter(osc_rate < 1.5, freq < 150) %>% 
  ggplot(aes(x=osc_rate, y=rate_k, group=interaction(osc_rate, homeo), color=homeo)) +
  geom_boxplot() +
  theme_classic() +
  scale_color_grey() +
  facet_grid(freq~kind, scales = "free")
```

### 2019-08-19 resistingrhythm/analysis/exp328-339.Rmd
Added H only + gamma only plots

@@
 
-```{r, fig.height=2.5, fig.width=2.25}
+```{r, fig.height=2, fig.width=2.25}
 results %>% 
-  filter(osc_rate < 1.5, freq < 150) %>% 
+  filter(osc_rate < 1.5, freq < 150, freq > 8) %>% 
   ggplot(aes(x=osc_rate, y=rate_k, group=interaction(osc_rate, homeo), color=homeo)) +
@@
   scale_color_grey() +
-  facet_grid(freq~kind, scales = "free")
+  lims(y=c(0, 150)) +
+  facet_grid(kind~freq, scales = "free")
 ```
+
+# H only plots
+```{r, fig.height=1.3, fig.width=2.5}
+results %>% 
+  filter(osc_rate < 1.5, freq < 150, freq > 8) %>% 
+  filter(homeo == "Homeostasis") %>% 
+  ggplot(aes(x=as.factor(osc_rate), y=rate_k, group=interaction(osc_rate, kind), color=kind)) +
+  geom_boxplot() +
+  theme_classic() +
+  scale_color_manual(values=c("darkgoldenrod3", "black"), name="Oscillation") +
+  # lims(y=c(0, 100)) +
+  labs(y="Pop. rate", x="Osc. rate", tag="a.") +
+  facet_grid(.~freq, scales = "free")
+```
+
+```{r, fig.height=1.3, fig.width=2.5}
+results %>% 
+  filter(osc_rate < 1.5, freq < 150, freq > 8) %>% 
+  filter(homeo == "Homeostasis") %>% 
+  ggplot(aes(x=as.factor(osc_rate), y=kappa_coord, group=interaction(osc_rate, kind), color=kind)) +
+  geom_boxplot() +
+  theme_classic() +
+  scale_color_manual(values=c("darkgoldenrod3", "black"), name="Oscillation") +
+  # lims(y=c(0.0, .12)) +
+  labs(y="Kappa", x="Osc. rate", tag="b.") +
+  facet_grid(.~freq, scales = "free")
+```

### 2019-08-19 resistingrhythm/analysis/paper_figures_v4.Rmd
Add new gamma Figure

@@
 
-# Load all data
+# Load data
+## Main Theta (and controls)
 ```{r, message=FALSE}
@@
 }
-
 rm(df, n_c, i, exp_code)
@@
 
-# Figure: Main results
+## Main gamma
+```{r}
+# ----------------------------------------------------------------------
+# @ 60 Hz, burst
+#
+# No H
+exp_code <- 329
+osc_codes <- c("0", "0.5", "1", "1.5", "3", "6", "12")
+osc_rates <- c(0, 0.5, 1, 1.5, 3, 6, 12)
+stim_codes <- c(3, 4)
+
+results329 <- NULL
+for(i in 1:length(osc_codes)){
+  for(s_c in stim_codes){
+    o_c <- osc_codes[i]
+    o_r <- osc_rates[i]
+
+    # Load the csv
+    df <- read_csv(paste(data_path, 
+                         "exp", as.character(exp_code), 
+                         "_stim", as.character(s_c), 
+                         "_burst", as.character(o_c),
+                         ".csv", sep=""))
+
+    # Add metadata
+    df$osc_code <- rep(o_c, nrow(df))
+    df$osc_rate <- rep(o_r, nrow(df))
+    df$stim_code <- rep(s_c, nrow(df))
+    df$synapse <- rep("AMPA", nrow(df))
+    df$homeo <- rep("No homeostasis", nrow(df))
+    df$freq <- rep(60, nrow(df))
+    df$kind <- rep("Burst", nrow(df))
+
+    results329 <- rbind(results329, df)
+  }
+}
+
+# H
+exp_code <- 328
+osc_codes <- c("0", "0.5", "1", "1.5", "3", "6", "12")
+osc_rates <- c(0, 0.5, 1, 1.5, 3, 6, 12)
+stim_codes <- c(3, 4)
+
+results328 <- NULL
+for(i in 1:length(osc_codes)){
+  for(s_c in stim_codes){
+    o_c <- osc_codes[i]
+    o_r <- osc_rates[i]
+
+    # Load the csv
+    df <- read_csv(paste(data_path, 
+                         "exp", as.character(exp_code), 
+                         "_stim", as.character(s_c), 
+                         "_burst", as.character(o_c),
+                         ".csv", sep=""))
+
+    # Add metadata
+    df$osc_code <- rep(o_c, nrow(df))
+    df$osc_rate <- rep(o_r, nrow(df))
+    df$stim_code <- rep(s_c, nrow(df))
+    df$synapse <- rep("AMPA", nrow(df))
+    df$homeo <- rep("Homeostasis", nrow(df))
+    df$freq <- rep(60, nrow(df))
+    df$kind <- rep("Burst", nrow(df))
+
+    results328 <- rbind(results328, df)
+  }
+}
+
+# ----------------------------------------------------------------------
+# @ 60 Hz, sustained
+#
+# No H
+exp_code <- 331
+osc_codes <- c("0", "0.5", "1", "1.5", "3", "6", "12")
+osc_rates <- c(0, 0.5, 1, 1.5, 3, 6, 12)
+stim_codes <- c(3, 4)
+
+results331 <- NULL
+for(i in 1:length(osc_codes)){
+  for(s_c in stim_codes){
+    o_c <- osc_codes[i]
+    o_r <- osc_rates[i]
+
+    # Load the csv
+    df <- read_csv(paste(data_path, 
+                         "exp", as.character(exp_code), 
+                         "_stim", as.character(s_c), 
+                         "_burst", as.character(o_c),
+                         ".csv", sep=""))
+
+    # Add metadata
+    df$osc_code <- rep(o_c, nrow(df))
+    df$osc_rate <- rep(o_r, nrow(df))
+    df$stim_code <- rep(s_c, nrow(df))
+    df$synapse <- rep("AMPA", nrow(df))
+    df$homeo <- rep("No homeostasis", nrow(df))
+    df$freq <- rep(60, nrow(df))
+    df$kind <- rep("Tonic", nrow(df))
+
+    results331 <- rbind(results331, df)
+  }
+}
+results331 %>%
+  filter(rate_k > 0) -> results331
+
+# H
+exp_code <- 330
+osc_codes <- c("0", "0.5", "1", "1.5", "3", "6", "12")
+osc_rates <- c(0, 0.5, 1, 1.5, 3, 6, 12)
+stim_codes <- c(3, 4)
+
+results330 <- NULL
+for(i in 1:length(osc_codes)){
+  for(s_c in stim_codes){
+    o_c <- osc_codes[i]
+    o_r <- osc_rates[i]
+
+    # Load the csv
+    df <- read_csv(paste(data_path, 
+                         "exp", as.character(exp_code), 
+                         "_stim", as.character(s_c), 
+                         "_burst", as.character(o_c),
+                         ".csv", sep=""))
+
+    # Add metadata
+    df$osc_code <- rep(o_c, nrow(df))
+    df$osc_rate <- rep(o_r, nrow(df))
+    df$stim_code <- rep(s_c, nrow(df))
+    df$synapse <- rep("AMPA", nrow(df))
+    df$homeo <- rep("Homeostasis", nrow(df))
+    df$freq <- rep(60, nrow(df))
+    df$kind <- rep("Tonic", nrow(df))
+
+    results330 <- rbind(results330, df)
+  }
+}
+
+# ----------------------------------------------------------------------
+# ----------------------------------------------------------------------
+# ----------------------------------------------------------------------
+# @ 90 Hz, burst
+#
+# No H
+exp_code <- 333
+osc_codes <- c("0", "0.5", "1", "1.5", "3", "6", "12")
+osc_rates <- c(0, 0.5, 1, 1.5, 3, 6, 12)
+stim_codes <- c(3, 4)
+
+results333 <- NULL
+for(i in 1:length(osc_codes)){
+  for(s_c in stim_codes){
+    o_c <- osc_codes[i]
+    o_r <- osc_rates[i]
+
+    # Load the csv
+    df <- read_csv(paste(data_path, 
+                         "exp", as.character(exp_code), 
+                         "_stim", as.character(s_c), 
+                         "_burst", as.character(o_c),
+                         ".csv", sep=""))
+
+    # Add metadata
+    df$osc_code <- rep(o_c, nrow(df))
+    df$osc_rate <- rep(o_r, nrow(df))
+    df$stim_code <- rep(s_c, nrow(df))
+    df$synapse <- rep("AMPA", nrow(df))
+    df$homeo <- rep("No homeostasis", nrow(df))
+    df$freq <- rep(90, nrow(df))
+    df$kind <- rep("Burst", nrow(df))
+
+    results333 <- rbind(results333, df)
+  }
+}
+
+# H
+exp_code <- 332
+osc_codes <- c("0", "0.5", "1", "1.5", "3", "6", "12")
+osc_rates <- c(0, 0.5, 1, 1.5, 3, 6, 12)
+stim_codes <- c(3, 4)
+
+results332 <- NULL
+for(i in 1:length(osc_codes)){
+  for(s_c in stim_codes){
+    o_c <- osc_codes[i]
+    o_r <- osc_rates[i]
+
+    # Load the csv
+    df <- read_csv(paste(data_path, 
+                         "exp", as.character(exp_code), 
+                         "_stim", as.character(s_c), 
+                         "_burst", as.character(o_c),
+                         ".csv", sep=""))
+
+    # Add metadata
+    df$osc_code <- rep(o_c, nrow(df))
+    df$osc_rate <- rep(o_r, nrow(df))
+    df$stim_code <- rep(s_c, nrow(df))
+    df$synapse <- rep("AMPA", nrow(df))
+    df$homeo <- rep("Homeostasis", nrow(df))
+    df$freq <- rep(90, nrow(df))
+    df$kind <- rep("Burst", nrow(df))
+
+    results332 <- rbind(results332, df)
+  }
+}
+
+# ----------------------------------------------------------------------
+# @ 90 Hz, sustained
+#
+# No H
+exp_code <- 335
+osc_codes <- c("0", "0.5", "1", "1.5", "3", "6", "12")
+osc_rates <- c(0, 0.5, 1, 1.5, 3, 6, 12)
+stim_codes <- c(3, 4)
+
+results335 <- NULL
+for(i in 1:length(osc_codes)){
+  for(s_c in stim_codes){
+    o_c <- osc_codes[i]
+    o_r <- osc_rates[i]
+
+    # Load the csv
+    df <- read_csv(paste(data_path, 
+                         "exp", as.character(exp_code), 
+                         "_stim", as.character(s_c), 
+                         "_burst", as.character(o_c),
+                         ".csv", sep=""))
+
+    # Add metadata
+    df$osc_code <- rep(o_c, nrow(df))
+    df$osc_rate <- rep(o_r, nrow(df))
+    df$stim_code <- rep(s_c, nrow(df))
+    df$synapse <- rep("AMPA", nrow(df))
+    df$homeo <- rep("No homeostasis", nrow(df))
+    df$freq <- rep(90, nrow(df))
+    df$kind <- rep("Tonic", nrow(df))
+
+    results335 <- rbind(results335, df)
+  }
+}
+
+# H
+exp_code <- 334
+osc_codes <- c("0", "0.5", "1", "1.5", "3", "6", "12")
+osc_rates <- c(0, 0.5, 1, 1.5, 3, 6, 12)
+stim_codes <- c(3, 4)
+
+results334 <- NULL
+for(i in 1:length(osc_codes)){
+  for(s_c in stim_codes){
+    o_c <- osc_codes[i]
+    o_r <- osc_rates[i]
+
+    # Load the csv
+    df <- read_csv(paste(data_path, 
+                         "exp", as.character(exp_code), 
+                         "_stim", as.character(s_c), 
+                         "_burst", as.character(o_c),
+                         ".csv", sep=""))
+
+    # Add metadata
+    df$osc_code <- rep(o_c, nrow(df))
+    df$osc_rate <- rep(o_r, nrow(df))
+    df$stim_code <- rep(s_c, nrow(df))
+    df$synapse <- rep("AMPA", nrow(df))
+    df$homeo <- rep("Homeostasis", nrow(df))
+    df$freq <- rep(90, nrow(df))
+    df$kind <- rep("Sustained", nrow(df))
+
+    results334 <- rbind(results334, df)
+  }
+}
+
+gamma_results <- rbind(
+  results328, results329, 
+  results330, results331, 
+  results332, results333, 
+  results334, results335
+)
+```
+
+# Figure: Theta results
 ```{r fig.height=2.25, fig.width=6}
@@
     geom_point(size=1.25) +
-    geom_errorbar(mapping=aes(x=osc_rate, ymin=M - SD, ymax=M + SD, color=synapse),
-                  width=.15, size=0.2) +
+    geom_linerange(mapping=aes(x=osc_rate, ymin=M - SD, ymax=M + SD, color=synapse)) +
     scale_color_manual(values=c("black", "grey")) +
@@
     geom_point(size=1.25) +
-    geom_errorbar(mapping=aes(x=osc_rate, ymin=M - SD, ymax=M + SD, color=synapse),
+    geom_linerange(mapping=aes(x=osc_rate, ymin=M - SD, ymax=M + SD, color=synapse),
                   width=.15, size=0.2) +
@@
   geom_point(size=1.25) +
-  geom_errorbar(mapping=aes(x=osc_rate, ymin=M - SD, ymax=M + SD, color=synapse),
+  geom_linerange(mapping=aes(x=osc_rate, ymin=M - SD, ymax=M + SD, color=synapse),
                 width=.15, size=0.2) +
@@
   geom_point(size=1.25) +
-  geom_errorbar(mapping=aes(x=osc_rate, ymin=M - SD, ymax=M + SD, color=synapse), 
+  geom_linerange(mapping=aes(x=osc_rate, ymin=M - SD, ymax=M + SD, color=synapse), 
                 width=.15, size=0.2) +
@@
     geom_point(size=1.25) +
-    geom_errorbar(mapping=aes(x=osc_rate, ymin=M - SD, ymax=M + SD, color=synapse), 
+    geom_linerange(mapping=aes(x=osc_rate, ymin=M - SD, ymax=M + SD, color=synapse), 
                 width=.15, size=0.2) +
@@
 
+# Figure: Gamma (AMPA)
+```{r, fig.height=2.1, fig.width=2.6}
+freq_labels <- as_labeller(c('60' = "60 Hz", '90' = "90 Hz"))
+gamma_results %>% 
+  filter(osc_rate < 1.5, freq < 150, freq > 8) %>% 
+  filter(homeo == "Homeostasis") %>% 
+  group_by(freq, osc_rate, kind) %>% 
+  mutate(M=mean(rate_k), SD=sd(rate_k)) %>% 
+  ggplot(aes(x=osc_rate, y=M, group=interaction(osc_rate, kind), color=kind)) +
+  geom_linerange(mapping=aes(x=osc_rate, ymin=M - SD, ymax=M + SD, color=kind), size=.4) +
+  geom_point() +
+  theme_classic() +
+  scale_color_manual(values=c("darkgoldenrod3", "black"), name="Oscillation") +
+  labs(y="Pop. rate", x="Osc. rate", tag="a.") +
+  lims(y=c(0, 100)) +
+  theme(legend.position = "right",
+        plot.tag = element_text(size=16, face="bold"),
+        legend.background = element_rect(colour ="black"),
+        panel.spacing = unit(1, "lines"),
+        panel.grid.major = element_blank(),
+        panel.grid.minor = element_blank(),
+        strip.background = element_blank()) +
+  facet_grid(.~freq, scales = "free", labeller=freq_labels) -> p1
+
+gamma_results %>% 
+  filter(osc_rate < 1.5, freq < 150, freq > 8) %>% 
+  filter(homeo == "Homeostasis") %>% 
+  group_by(freq, osc_rate, kind) %>% 
+  mutate(M=mean(kappa_coord), SD=sd(kappa_coord)) %>% 
+  ggplot(aes(x=osc_rate, y=M, group=interaction(osc_rate, kind), color=kind)) +
+  geom_point() +
+  geom_linerange(mapping=aes(x=osc_rate, ymin=M - SD, ymax=M + SD, color=kind), size=.4) +
+  theme_classic() +
+  facet_grid(.~freq, scales = "free", labeller = freq_labels) +
+  scale_color_manual(values=c("darkgoldenrod3", "black"), name="Oscillation") +
+  lims(y=c(0.0, .12)) +
+  theme(legend.position = "none",
+        plot.tag = element_text(size=16, face="bold"),
+        panel.spacing = unit(1, "lines"),
+        panel.grid.major = element_blank(),
+        panel.grid.minor = element_blank(),
+        strip.background = element_blank()) +
+  labs(y="Kappa", x="Osc. rate", tag="b.") -> p2
+
+layout_matrix <- rbind(
+  c(1, 1, 1, 1, 1),
+  c(2, 2, 2, 2, NA)
+)
+grid.arrange(p1, p2, layout_matrix=layout_matrix)
+```
+
 # Figure: Control
@@
   geom_point(size=1.5) +
-  geom_errorbar(aes(ymin=M - SD, ymax=M + SD), alpha=0.5, width=.1, size=0.4)  +
+  geom_linerange(aes(ymin=M - SD, ymax=M + SD), alpha=0.5, width=.1, size=0.4)  +
   labs(title="b.", y="Kappa", x="Osc. rate") +
@@
   geom_point(size=1.5) +
-  geom_errorbar(aes(ymin=M - SD, ymax=M + SD), alpha=0.5, width=.1, size=0.4)  +
+  geom_linerange(aes(ymin=M - SD, ymax=M + SD), alpha=0.5, width=.1, size=0.4)  +
   labs(title="a.", y="Pop. rate", x="Osc. rate") +

### 2019-08-19 resistingrhythm/analysis/exp326-327.Rmd
Vis tweaks

---
title: "Analysis : exp326-7 LFP"
output: html_notebook
---

```{r, message=FALSE}
library(ggplot2)
library(dplyr)
library(magrittr)
library(readr)
library(gridExtra)
library(grid)
library(ggpubr)
library(cowplot)

data_path <- "~/Code/resistingrhythm/data/"
```

# Load all data

- Explore gamma=60Hz, gamma=90Hz, ripple=150 Hz

```{r, message=FALSE}
# ----------------------------------------------------------------------
# Load 8 Hz theta AMPA
# 16: Sustained E, with H
exp_code <- 221
osc_codes <- c(100, 105, 110, 115, 120, 125, 130)
osc_rates <- c(0, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0)
stim_codes <- c(3, 4) # 4

results221 <- NULL
for(i in 1:length(osc_codes)){
  for(s_c in stim_codes){
    o_c <- osc_codes[i]
    o_r <- osc_rates[i]

    # Load the csv
    df <- read_csv(paste(data_path, 
                         "exp", as.character(exp_code), 
                         "_stim", as.character(s_c), 
                         "_osc", as.character(o_c),
                         ".csv", sep=""))

    # Add metadata
    df$osc_code <- rep(o_c, nrow(df))
    df$osc_rate <- rep(o_r, nrow(df))
    df$stim_code <- rep(s_c, nrow(df))
    df$synapse <- rep("AMPA", nrow(df))
    df$homeo <- rep("Homeostasis", nrow(df))
    df$freq <- rep(8, nrow(df))
    df$kind <- rep("Sustained", nrow(df))
    results221 <- rbind(results221, df)
  }
}

# 22: Burst E, NO H @ 8 hz
exp_code <- 220
osc_codes <- c(100, 105, 110, 115, 120, 125, 130)
osc_rates <- c(0, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0)
stim_codes <- c(3, 4)

results220 <- NULL
for(i in 1:length(osc_codes)){
  for(s_c in stim_codes){
    o_c <- osc_codes[i]
    o_r <- osc_rates[i]

    # Load the csv
    df <- read_csv(paste(data_path, 
                         "exp", as.character(exp_code), 
                         "_stim", as.character(s_c), 
                         "_osc", as.character(o_c),
                         ".csv", sep=""))

    # Add metadata
    df$osc_code <- rep(o_c, nrow(df))
    df$osc_rate <- rep(o_r, nrow(df))
    df$stim_code <- rep(s_c, nrow(df))
    df$synapse <- rep("AMPA", nrow(df))
    df$homeo <- rep("No homeostasis", nrow(df))
    df$freq <- rep(8, nrow(df))
    df$kind <- rep("Sustained", nrow(df))

    results220 <- rbind(results220, df)
  }
}
ref <- rbind(results220, results221)

# ----------------------------------------------------------------------
# No H
exp_code <- 326
osc_codes <- c(100, 105, 110, 115, 120, 125, 130)
osc_rates <- c(0, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0)
stim_codes <- c(3, 4) # 4

results326 <- NULL
for(i in 1:length(osc_codes)){
  for(s_c in stim_codes){
    o_c <- osc_codes[i]
    o_r <- osc_rates[i]

    # Load the csv
    df <- read_csv(paste(data_path, 
                         "exp", as.character(exp_code), 
                         "_stim", as.character(s_c), 
                         "lfp", as.character(o_c),
                         ".csv", sep=""))

    # Add metadata
    df$osc_code <- rep(o_c, nrow(df))
    df$osc_rate <- rep(o_r, nrow(df))
    df$stim_code <- rep(s_c, nrow(df))
    df$synapse <- rep("AMPA", nrow(df))
    df$homeo <- rep("No homeostasis", nrow(df))
    df$freq <- rep(8, nrow(df))
    results326 <- rbind(results326, df)
  }
}

# H
exp_code <- 327
osc_codes <- c(100, 105, 110, 115, 120, 125, 130)
osc_rates <- c(0, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0)
stim_codes <- c(3, 4)

results327 <- NULL
for(i in 1:length(osc_codes)){
  for(s_c in stim_codes){
    o_c <- osc_codes[i]
    o_r <- osc_rates[i]

    # Load the csv
    df <- read_csv(paste(data_path, 
                         "exp", as.character(exp_code), 
                         "_stim", as.character(s_c), 
                         "_lfp", as.character(o_c),
                         ".csv", sep=""))

    # Add metadata
    df$osc_code <- rep(o_c, nrow(df))
    df$osc_rate <- rep(o_r, nrow(df))
    df$stim_code <- rep(s_c, nrow(df))
    df$synapse <- rep("AMPA", nrow(df))
    df$homeo <- rep("Homeostasis", nrow(df))
    df$freq <- rep(8, nrow(df))
    results327 <- rbind(results327, df)
  }
}

results <- rbind(results326, results327)
rm(results326, results327, df)
```

```{r, fig.width=1.5, fig.height=1.2}
ref %>% 
  ggplot(aes(x=osc_rate, y=kappa_coord-k_ref, group=interaction(osc_rate))) +
  geom_boxplot() +
  geom_hline(aes(yintercept=0), size=.5, color="grey") +
  theme_classic() +
  scale_color_grey() +
  labs(y="Delta kappa") +
  facet_grid(.~homeo, scales = "free")
```

```{r, fig.width=1.5, fig.height=1.2}
results %>% 
  ggplot(aes(x=osc_rate, y=kappa_coord-k_ref, group=interaction(osc_rate))) +
  geom_boxplot() +
  geom_hline(aes(yintercept=0), size=.5, color="grey") +
  theme_classic() +
  scale_color_grey() +
  labs(y="Delta kappa") +
  facet_grid(.~homeo, scales = "free")
```

```{r, fig.width=1.5, fig.height=1.2}
ref %>% 
  ggplot(aes(x=osc_rate, y=rate_k-rate_ref, group=interaction(osc_rate))) +
  geom_boxplot() +
  geom_hline(aes(yintercept=0), size=.5, color="grey") +
  theme_classic() +
  scale_color_grey() +
  labs(y="Delta rate") +
  facet_grid(.~homeo, scales = "free")
```

```{r, fig.width=1.5, fig.height=1.2}
results %>% 
  ggplot(aes(x=osc_rate, y=rate_k-rate_ref, group=interaction(osc_rate))) +
  geom_boxplot() +
  theme_classic() +
  scale_color_grey() +
  labs(y="Delta rate") +
  facet_grid(.~homeo, scales = "free")
```

### 2019-08-19 resistingrhythm/analysis/exp328-339.Rmd
Vis tweaks

@@
 
+# Plot all
 ```{r, fig.height=2.5, fig.width=2.25}
@@
 # H only plots
+## Box
 ```{r, fig.height=1.3, fig.width=2.5}
@@
 ```
+
+## Mean
+```{r, fig.height=1.1, fig.width=2.6}
+freq_labels <- as_labeller(c('60' = "60 Hz", '90' = "90 Hz"))
+
+results %>% 
+  filter(osc_rate < 1.5, freq < 150, freq > 8) %>% 
+  filter(homeo == "Homeostasis") %>% 
+  group_by(freq, osc_rate, kind) %>% 
+  mutate(M=mean(rate_k), SD=sd(rate_k)) %>% 
+  ggplot(aes(x=osc_rate, y=M, group=interaction(osc_rate, kind), color=kind)) +
+  geom_linerange(mapping=aes(x=osc_rate, ymin=M - SD, ymax=M + SD, color=kind), size=.4) +
+  geom_point() +
+  theme_classic() +
+  scale_color_manual(values=c("darkgoldenrod3", "black"), name="Oscillation") +
+  labs(y="Pop. rate", x="Osc. rate", tag="a.") +
+  lims(y=c(0, 100)) +
+  theme(panel.grid.major = element_blank(),
+        panel.grid.minor = element_blank(),
+        strip.background = element_blank()) +
+  facet_grid(.~freq, scales = "free", labeller=freq_labels)
+```
+
+```{r, fig.height=1.1, fig.width=2.6}
+results %>% 
+  filter(osc_rate < 1.5, freq < 150, freq > 8) %>% 
+  filter(homeo == "Homeostasis") %>% 
+  group_by(freq, osc_rate, kind) %>% 
+  mutate(M=mean(kappa_coord), SD=sd(kappa_coord)) %>% 
+  ggplot(aes(x=osc_rate, y=M, group=interaction(osc_rate, kind), color=kind)) +
+  geom_point() +
+  geom_linerange(mapping=aes(x=osc_rate, ymin=M - SD, ymax=M + SD, color=kind), size=.4) +
+  theme_classic() +
+  facet_grid(.~freq, scales = "free", labeller = freq_labels) +
+  scale_color_manual(values=c("darkgoldenrod3", "black"), name="Oscillation") +
+  lims(y=c(0.0, .12)) +
+  theme(panel.grid.major = element_blank(),
+        panel.grid.minor = element_blank(),
+        strip.background = element_blank()) +
+  labs(y="Kappa", x="Osc. rate", tag="b.")
+
+```

### 2019-08-19 resistingrhythm/analysis/paper_figures_v4.Rmd
Fix labels

@@
     df$freq <- rep(90, nrow(df))
-    df$kind <- rep("Sustained", nrow(df))
+    df$kind <- rep("Tonic", nrow(df))
 

### 2019-08-21 resistingrhythm/analysis/exp316_317.Rmd
Add g_K analysis notebook

---
title: "Analysis : exp316-7 g_L analysis"
output: html_notebook
---

# Header
```{r, message=FALSE}
library(ggplot2)
library(dplyr)
library(magrittr)
library(readr)
library(gridExtra)
library(grid)
library(ggpubr)
library(cowplot)

data_path <- "~/Code/resistingrhythm/data/"
```

# Load G_Ca
```{r, message=FALSE}
# Main exp
# -----------------------------------------------------------------------
# 15: Sustained E, with H
exp_code <- 221
osc_codes <- c(100, 115)
osc_rates <- c(0, 1.5)
stim_codes <- c(3, 4)

results221 <- NULL
for(i in 1:length(osc_codes)){
  for(s_c in stim_codes){
    o_c <- osc_codes[i]
    o_r <- osc_rates[i]

    # Load the csv
    df <- read_csv(paste(data_path, 
                         "exp", as.character(exp_code), 
                         "_stim", as.character(s_c), 
                         "_osc", as.character(o_c),
                         ".csv", sep=""))

    # Add metadata
    df$osc_code <- rep(o_c, nrow(df))
    df$osc_rate <- rep(o_r, nrow(df))
    df$synapse <- rep("AMPA", nrow(df))
    df$stim_code <- rep(s_c, nrow(df))
    df$g_L <- rep("1.0e-3", nrow(df))
    df$homeo <- rep("Homeostasis", nrow(df))
    df$freq <- rep(8, nrow(df))
    results221 <- rbind(results221, df)
  }
}

results221 %>%
  filter(rate_k > 0) -> results221

# ----------------------------------------------------------------------
# gL perturb exps
# H
exp_code <- 317
osc_codes <- c(100, 115)
osc_rates <- c(0, 1.5)
stim_codes <- c(3, 4) # 4
g_Ls <- c("0.9e-3", "0.95e-3", "1.05e-3", "1.1e-3")

results317 <- NULL
for(i in 1:length(osc_codes)){
  for(s_c in stim_codes){
    for(g in g_Ls){

      o_c <- osc_codes[i]
      o_r <- osc_rates[i]

      # Load the csv
      # exp316_stim{1}_gl{3}_osc
      df <- read_csv(paste(data_path, 
                           "exp", as.character(exp_code), 
                           "_stim", as.character(s_c), 
                           "_gl", as.character(g), 
                           "_osc", as.character(o_c),
                           ".csv", sep=""))

      # Add metadata
      df$osc_code <- rep(o_c, nrow(df))
      df$osc_rate <- rep(o_r, nrow(df))
      df$stim_code <- rep(s_c, nrow(df))
      df$synapse <- rep("AMPA", nrow(df))
      df$g_L <- rep(g, nrow(df))
      df$homeo <- rep("Homeostasis", nrow(df))
      df$freq <- rep(8, nrow(df))

      results317 <- rbind(results317, df)
    }
  }
}
results317 %>%
  filter(rate_k > 0) -> results317

# no H
exp_code <- 316
osc_codes <- c(100, 115)
osc_rates <- c(0, 1.5)
stim_codes <- c(3, 4) # 4
g_Ls <- c("0.9e-3", "0.95e-3", "1.05e-3", "1.1e-3")

results316 <- NULL
for(i in 1:length(osc_codes)){
  for(s_c in stim_codes){
    for(g in g_Ls){

      o_c <- osc_codes[i]
      o_r <- osc_rates[i]

      # Load the csv
      # exp316_stim{1}_gl{3}_osc
      df <- read_csv(paste(data_path, 
                           "exp", as.character(exp_code), 
                           "_stim", as.character(s_c), 
                           "_gl", as.character(g), 
                           "_osc", as.character(o_c),
                           ".csv", sep=""))

      # Add metadata
      df$osc_code <- rep(o_c, nrow(df))
      df$osc_rate <- rep(o_r, nrow(df))
      df$stim_code <- rep(s_c, nrow(df))
      df$synapse <- rep("AMPA", nrow(df))
      df$g_L <- rep(g, nrow(df))
      df$homeo <- rep("No homeostasis", nrow(df))
      df$freq <- rep(8, nrow(df))

      results316 <- rbind(results316, df)
    }
  }
}
results316 %>%
  filter(rate_k > 0) -> results316

results <- rbind(
  results316,
  results317,
  results221
)

results$g_L <- factor(results$g_L, levels=c("0.9e-3", "0.95e-3", "1.0e-3", "1.05e-3", "1.1e-3"))
```

# Plot
## Individual points
```{r, fig.height=1.2, fig.width=3.5}
results %>% 
  ggplot(aes(x=osc_rate, y=kappa_coord, group=interaction(osc_rate, homeo), color=g_L)) +
  geom_point(size=.5, alpha=0.6) +
  theme_classic() +
  scale_color_viridis_d() +
  facet_grid(homeo~., scales = "free")
```

```{r, fig.height=1.2, fig.width=3.5}
results %>% 
  ggplot(aes(x=osc_rate, y=rate_k, group=interaction(osc_rate, homeo), color=g_L)) +
  geom_point(size=.5, alpha=0.5) +
  theme_classic() +
  scale_color_viridis_d() + 
  facet_grid(homeo~., scales = "free")
```

## Means
```{r, fig.height=1.2, fig.width=1.2}
results %>% 
  filter(homeo=="Homeostasis") %>% 
  group_by(osc_rate, homeo, g_L) %>% 
  mutate(M=mean(kappa_coord), SD=sd(kappa_coord)) %>% 
  ggplot(aes(x=osc_rate, y=M, group=interaction(osc_rate, homeo), color=g_L)) +
  geom_linerange(mapping=aes(x=osc_rate, ymin=M - SD, ymax=M + SD, color=g_L), size=.4) +
  geom_point(size=.5, alpha=0.6) +
  theme_classic() +
  scale_color_viridis_d() +
  labs(tag="a.", y="Kappa", x="Osc. rate") +
  theme(plot.tag = element_text(size=16, face="bold"))
  # facet_grid(homeo~., scales = "free")
```

```{r, fig.height=1.2, fig.width=1.25}
results %>% 
  filter(homeo=="Homeostasis") %>% 
  group_by(osc_rate, homeo, g_L) %>% 
  mutate(M=mean(rate_k), SD=sd(rate_k)) %>% 
  ggplot(aes(x=osc_rate, y=M, group=interaction(osc_rate, homeo), color=g_L)) +
  geom_linerange(mapping=aes(x=osc_rate, ymin=M - SD, ymax=M + SD, color=g_L), size=.4) +
  geom_point(size=.5, alpha=0.6) +
  theme_classic() +
  scale_color_viridis_d() +
  labs(tag="b.", y="Pop. rate", x="Osc. rate") +
  theme(plot.tag = element_text(size=16, face="bold"))
  # facet_grid(homeo~., scales = "free")
```

### 2019-08-21 resistingrhythm/analysis/exp320_321.Rmd
G_KCA analysis

--- 2019-08-21 resistingrhythm/analysis/exp316_317.Rmd
@@
 ---
-title: "Analysis : exp316-7 g_L analysis"
+title: "Analysis : exp320-21 g_KCa analysis"
 output: html_notebook
@@
 
-# Load G_Ca
+# Load G_KCa
 ```{r, message=FALSE}
-# Main exp
-# -----------------------------------------------------------------------
-# 15: Sustained E, with H
-exp_code <- 221
-osc_codes <- c(100, 115)
-osc_rates <- c(0, 1.5)
-stim_codes <- c(3, 4)
-
-results221 <- NULL
-for(i in 1:length(osc_codes)){
-  for(s_c in stim_codes){
-    o_c <- osc_codes[i]
-    o_r <- osc_rates[i]
-
-    # Load the csv
-    df <- read_csv(paste(data_path, 
-                         "exp", as.character(exp_code), 
-                         "_stim", as.character(s_c), 
-                         "_osc", as.character(o_c),
-                         ".csv", sep=""))
-
-    # Add metadata
-    df$osc_code <- rep(o_c, nrow(df))
-    df$osc_rate <- rep(o_r, nrow(df))
-    df$synapse <- rep("AMPA", nrow(df))
-    df$stim_code <- rep(s_c, nrow(df))
-    df$g_L <- rep("1.0e-3", nrow(df))
-    df$homeo <- rep("Homeostasis", nrow(df))
-    df$freq <- rep(8, nrow(df))
-    results221 <- rbind(results221, df)
-  }
-}
-
-results221 %>%
-  filter(rate_k > 0) -> results221
-
 # ----------------------------------------------------------------------
-# gL perturb exps
+# G_KCA perturb exps
 # H
-exp_code <- 317
+exp_code <- 321
 osc_codes <- c(100, 115)
@@
 stim_codes <- c(3, 4) # 4
-g_Ls <- c("0.9e-3", "0.95e-3", "1.05e-3", "1.1e-3")
+g_KCas <- c("0.1e-3", "1e-3", "15e-3", "30e-3", "45e-3", "60e-3")
 
-results317 <- NULL
+results321 <- NULL
 for(i in 1:length(osc_codes)){
   for(s_c in stim_codes){
-    for(g in g_Ls){
+    for(g in g_KCas){
 
@@
                            "_stim", as.character(s_c), 
-                           "_gl", as.character(g), 
+                           "_GKCa", as.character(g), 
                            "_osc", as.character(o_c),
@@
 
-      results317 <- rbind(results317, df)
+      results321 <- rbind(results321, df)
     }
@@
 }
-results317 %>%
-  filter(rate_k > 0) -> results317
+results321 %>%
+  filter(rate_k > 0) -> results321
 
 # no H
-exp_code <- 316
+exp_code <- 320
 osc_codes <- c(100, 115)
@@
 stim_codes <- c(3, 4) # 4
-g_Ls <- c("0.9e-3", "0.95e-3", "1.05e-3", "1.1e-3")
+g_KCas <- c("0.1e-3", "1e-3", "15e-3", "30e-3", "45e-3", "60e-3")
 
-results316 <- NULL
+results320 <- NULL
 for(i in 1:length(osc_codes)){
   for(s_c in stim_codes){
-    for(g in g_Ls){
+    for(g in g_KCas){
 
@@
 
-      results316 <- rbind(results316, df)
+      results320 <- rbind(results320, df)
     }
@@
 }
-results316 %>%
-  filter(rate_k > 0) -> results316
+results320 %>%
+  filter(rate_k > 0) -> results320
 
 results <- rbind(
-  results316,
-  results317,
-  results221
+  results320,
+  results321
 )
 
-results$g_L <- factor(results$g_L, levels=c("0.9e-3", "0.95e-3", "1.0e-3", "1.05e-3", "1.1e-3"))
+results$g_L <- factor(results$g_L, levels=c("0.1e-3", "1e-3", "15e-3", "30e-3", "45e-3", "60e-3"))
 ```
@@
   theme_classic() +
-  scale_color_viridis_d() +
-  facet_grid(homeo~., scales = "free")
+  scale_color_grey() +
+  facet_grid(homeo~g_L, scales = "free")
 ```

### 2019-08-21 resistingrhythm/analysis/paper_figures_v4.Rmd
Added new control panels to (now) Fig 4.

@@
 
-## Main gamma
-```{r}
+## Gamma
+```{r, message=FALSE}
 # ----------------------------------------------------------------------
@@
 )
+```
+
+## Leak
+```{r, message=FALSE}
+# Main exp
+# -----------------------------------------------------------------------
+# 15: Sustained E, with H
+exp_code <- 221
+osc_codes <- c(100, 115)
+osc_rates <- c(0, 1.5)
+stim_codes <- c(3, 4)
+
+results221b <- NULL
+for(i in 1:length(osc_codes)){
+  for(s_c in stim_codes){
+    o_c <- osc_codes[i]
+    o_r <- osc_rates[i]
+
+    # Load the csv
+    df <- read_csv(paste(data_path, 
+                         "exp", as.character(exp_code), 
+                         "_stim", as.character(s_c), 
+                         "_osc", as.character(o_c),
+                         ".csv", sep=""))
+
+    # Add metadata
+    df$osc_code <- rep(o_c, nrow(df))
+    df$osc_rate <- rep(o_r, nrow(df))
+    df$synapse <- rep("AMPA", nrow(df))
+    df$stim_code <- rep(s_c, nrow(df))
+    df$g_L <- rep("1.0e-3", nrow(df))
+    df$homeo <- rep("Homeostasis", nrow(df))
+    df$freq <- rep(8, nrow(df))
+    results221b <- rbind(results221b, df)
+  }
+}
+
+results221b %>%
+  filter(rate_k > 0) -> results221b
+
+# ----------------------------------------------------------------------
+# gL perturb exps
+# H
+exp_code <- 317
+osc_codes <- c(100, 115)
+osc_rates <- c(0, 1.5)
+stim_codes <- c(3, 4) # 4
+g_Ls <- c("0.9e-3", "0.95e-3", "1.05e-3", "1.1e-3")
+
+results317 <- NULL
+for(i in 1:length(osc_codes)){
+  for(s_c in stim_codes){
+    for(g in g_Ls){
+
+      o_c <- osc_codes[i]
+      o_r <- osc_rates[i]
+
+      # Load the csv
+      # exp316_stim{1}_gl{3}_osc
+      df <- read_csv(paste(data_path, 
+                           "exp", as.character(exp_code), 
+                           "_stim", as.character(s_c), 
+                           "_gl", as.character(g), 
+                           "_osc", as.character(o_c),
+                           ".csv", sep=""))
+
+      # Add metadata
+      df$osc_code <- rep(o_c, nrow(df))
+      df$osc_rate <- rep(o_r, nrow(df))
+      df$stim_code <- rep(s_c, nrow(df))
+      df$synapse <- rep("AMPA", nrow(df))
+      df$g_L <- rep(g, nrow(df))
+      df$homeo <- rep("Homeostasis", nrow(df))
+      df$freq <- rep(8, nrow(df))
+
+      results317 <- rbind(results317, df)
+    }
+  }
+}
+results317 %>%
+  filter(rate_k > 0) -> results317
+
+# no H
+exp_code <- 316
+osc_codes <- c(100, 115)
+osc_rates <- c(0, 1.5)
+stim_codes <- c(3, 4) # 4
+g_Ls <- c("0.9e-3", "0.95e-3", "1.05e-3", "1.1e-3")
+
+results316 <- NULL
+for(i in 1:length(osc_codes)){
+  for(s_c in stim_codes){
+    for(g in g_Ls){
+
+      o_c <- osc_codes[i]
+      o_r <- osc_rates[i]
+
+      # Load the csv
+      # exp316_stim{1}_gl{3}_osc
+      df <- read_csv(paste(data_path, 
+                           "exp", as.character(exp_code), 
+                           "_stim", as.character(s_c), 
+                           "_gl", as.character(g), 
+                           "_osc", as.character(o_c),
+                           ".csv", sep=""))
+
+      # Add metadata
+      df$osc_code <- rep(o_c, nrow(df))
+      df$osc_rate <- rep(o_r, nrow(df))
+      df$stim_code <- rep(s_c, nrow(df))
+      df$synapse <- rep("AMPA", nrow(df))
+      df$g_L <- rep(g, nrow(df))
+      df$homeo <- rep("No homeostasis", nrow(df))
+      df$freq <- rep(8, nrow(df))
+
+      results316 <- rbind(results316, df)
+    }
+  }
+}
+results316 %>%
+  filter(rate_k > 0) -> results316
+
+results_control_leak <- rbind(
+  results316,
+  results317,
+  results221b
+)
+
+results_control_leak$g_L <- factor(
+  results_control_leak$g_L, levels=c("0.9e-3", "0.95e-3", "1.0e-3", "1.05e-3", "1.1e-3"))
+```
+
+## Theta drift
+```{r, message=FALSE}
+# ----------------------------------------------------------------------
+# Load 8 Hz theta AMPA
+# 16: Burst E, with H
+exp_code <- 287
+osc_codes <- c(100, 105, 110, 115)
+osc_rates <- c(0, 0.5, 1.0, 1.5)
+stim_codes <- c(3, 4) # 4
+
+results289 <- NULL
+for(i in 1:length(osc_codes)){
+  for(s_c in stim_codes){
+    o_c <- osc_codes[i]
+    o_r <- osc_rates[i]
+
+    # Load the csv
+    df <- read_csv(paste(data_path, 
+                         "exp", as.character(exp_code), 
+                         "_stim", as.character(s_c), 
+                         "_osc", as.character(o_c),
+                         ".csv", sep=""))
+
+    # Add metadata
+    df$osc_code <- rep(o_c, nrow(df))
+    df$osc_rate <- rep(o_r, nrow(df))
+    df$stim_code <- rep(s_c, nrow(df))
+    df$synapse <- rep("AMPA", nrow(df))
+    df$homeo <- rep("Homeostasis", nrow(df))
+    df$freq <- rep(8, nrow(df))
+    results289 <- rbind(results289, df)
+  }
+}
+results289 %>%
+  filter(rate_k > 0) -> results289
+
+# Load 8 Hz theta AMPA
+# 16: Burst E, no H
+exp_code <- 286
+osc_codes <- c(100, 105, 110, 115)
+osc_rates <- c(0, 0.5, 1.0, 1.5)
+stim_codes <- c(3, 4) # 4
+
+results288 <- NULL
+for(i in 1:length(osc_codes)){
+  for(s_c in stim_codes){
+    o_c <- osc_codes[i]
+    o_r <- osc_rates[i]
+
+    # Load the csv
+    df <- read_csv(paste(data_path, 
+                         "exp", as.character(exp_code), 
+                         "_stim", as.character(s_c), 
+                         "_osc", as.character(o_c),
+                         ".csv", sep=""))
+
+    # Add metadata
+    df$osc_code <- rep(o_c, nrow(df))
+    df$osc_rate <- rep(o_r, nrow(df))
+    df$stim_code <- rep(s_c, nrow(df))
+    df$synapse <- rep("AMPA", nrow(df))
+    df$homeo <- rep("No homeostasis", nrow(df))
+    df$freq <- rep(8, nrow(df))
+    results288 <- rbind(results288, df)
+  }
+}
+results288 %>%
+  filter(rate_k > 0) -> results288
+
+# ----------------------------------------------------------------------
+# @ 6 Hz
+#
+# No H
+exp_code <- 298
+osc_codes <- c(100, 105, 110, 115)
+osc_rates <- c(0, 0.5, 1.0, 1.5)
+stim_codes <- c(3, 4)
+
+results298 <- NULL
+for(i in 1:length(osc_codes)){
+  for(s_c in stim_codes){
+    o_c <- osc_codes[i]
+    o_r <- osc_rates[i]
+
+    # Load the csv
+    df <- read_csv(paste(data_path, 
+                         "exp", as.character(exp_code), 
+                         "_stim", as.character(s_c), 
+                         "lfp", as.character(o_c),
+                         ".csv", sep=""))
+
+    # Add metadata
+    df$osc_code <- rep(o_c, nrow(df))
+    df$osc_rate <- rep(o_r, nrow(df))
+    df$stim_code <- rep(s_c, nrow(df))
+    df$synapse <- rep("AMPA", nrow(df))
+    df$homeo <- rep("No homeostasis", nrow(df))
+    df$freq <- rep(6, nrow(df))
+    results298 <- rbind(results298, df)
+  }
+}
+results298 %>%
+  filter(rate_k > 0) -> results298
+
+# H
+exp_code <- 299
+osc_codes <- c(100, 105, 110, 115)
+osc_rates <- c(0, 0.5, 1.0, 1.5)
+stim_codes <- c(3, 4)
+
+results299 <- NULL
+for(i in 1:length(osc_codes)){
+  for(s_c in stim_codes){
+    o_c <- osc_codes[i]
+    o_r <- osc_rates[i]
+
+    # Load the csv
+    df <- read_csv(paste(data_path, 
+                         "exp", as.character(exp_code), 
+                         "_stim", as.character(s_c), 
+                         "_lfp", as.character(o_c),
+                         ".csv", sep=""))
+
+    # Add metadata
+    df$osc_code <- rep(o_c, nrow(df))
+    df$osc_rate <- rep(o_r, nrow(df))
+    df$stim_code <- rep(s_c, nrow(df))
+    df$synapse <- rep("AMPA", nrow(df))
+    df$freq <- rep(6, nrow(df))
+    df$homeo <- rep("Homeostasis", nrow(df))
+
+    results299 <- rbind(results299, df)
+  }
+}
+results299 %>%
+  filter(rate_k > 0) -> results299
+
+# ----------------------------------------------------------------------
+# @ 7 Hz
+#
+# No H
+exp_code <- 302
+osc_codes <- c(100, 105, 110, 115)
+osc_rates <- c(0, 0.5, 1.0, 1.5)
+stim_codes <- c(3, 4)
+
+results302 <- NULL
+for(i in 1:length(osc_codes)){
+  for(s_c in stim_codes){
+    o_c <- osc_codes[i]
+    o_r <- osc_rates[i]
+
+    # Load the csv
+    df <- read_csv(paste(data_path, 
+                         "exp", as.character(exp_code), 
+                         "_stim", as.character(s_c), 
+                         "lfp", as.character(o_c),
+                         ".csv", sep=""))
+
+    # Add metadata
+    df$osc_code <- rep(o_c, nrow(df))
+    df$osc_rate <- rep(o_r, nrow(df))
+    df$stim_code <- rep(s_c, nrow(df))
+    df$synapse <- rep("AMPA", nrow(df))
+    df$homeo <- rep("No homeostasis", nrow(df))
+    df$freq <- rep(7, nrow(df))
+    results302 <- rbind(results302, df)
+  }
+}
+results302 %>%
+  filter(rate_k > 0) -> results302
+
+# H
+exp_code <- 303
+osc_codes <- c(100, 105, 110, 115)
+osc_rates <- c(0, 0.5, 1.0, 1.5)
+stim_codes <- c(3, 4)
+
+results303 <- NULL
+for(i in 1:length(osc_codes)){
+  for(s_c in stim_codes){
+    o_c <- osc_codes[i]
+    o_r <- osc_rates[i]
+
+    # Load the csv
+    df <- read_csv(paste(data_path, 
+                         "exp", as.character(exp_code), 
+                         "_stim", as.character(s_c), 
+                         "_lfp", as.character(o_c),
+                         ".csv", sep=""))
+
+    # Add metadata
+    df$osc_code <- rep(o_c, nrow(df))
+    df$osc_rate <- rep(o_r, nrow(df))
+    df$stim_code <- rep(s_c, nrow(df))
+    df$synapse <- rep("AMPA", nrow(df))
+    df$freq <- rep(7, nrow(df))
+    df$homeo <- rep("Homeostasis", nrow(df))
+    results303 <- rbind(results303, df)
+  }
+}
+results303 %>%
+  filter(rate_k > 0) -> results303
+
+# ----------------------------------------------------------------------
+# @ 9 Hz
+#
+# No H
+exp_code <- 306
+osc_codes <- c(100, 105, 110, 115)
+osc_rates <- c(0, 0.5, 1.0, 1.5)
+stim_codes <- c(3, 4)
+
+results306 <- NULL
+for(i in 1:length(osc_codes)){
+  for(s_c in stim_codes){
+    o_c <- osc_codes[i]
+    o_r <- osc_rates[i]
+
+    # Load the csv
+    df <- read_csv(paste(data_path, 
+                         "exp", as.character(exp_code), 
+                         "_stim", as.character(s_c), 
+                         "lfp", as.character(o_c),
+                         ".csv", sep=""))
+
+    # Add metadata
+    df$osc_code <- rep(o_c, nrow(df))
+    df$osc_rate <- rep(o_r, nrow(df))
+    df$stim_code <- rep(s_c, nrow(df))
+    df$synapse <- rep("AMPA", nrow(df))
+    df$homeo <- rep("No homeostasis", nrow(df))
+    df$freq <- rep(9, nrow(df))
+    results306 <- rbind(results306, df)
+  }
+}
+results306 %>%
+  filter(rate_k > 0) -> results306
+
+# H
+exp_code <- 307
+osc_codes <- c(100, 105, 110, 115)
+osc_rates <- c(0, 0.5, 1.0, 1.5)
+stim_codes <- c(3, 4)
+
+results307 <- NULL
+for(i in 1:length(osc_codes)){
+  for(s_c in stim_codes){
+    o_c <- osc_codes[i]
+    o_r <- osc_rates[i]
+
+    # Load the csv
+    df <- read_csv(paste(data_path, 
+                         "exp", as.character(exp_code), 
+                         "_stim", as.character(s_c), 
+                         "_lfp", as.character(o_c),
+                         ".csv", sep=""))
+
+    # Add metadata
+    df$osc_code <- rep(o_c, nrow(df))
+    df$osc_rate <- rep(o_r, nrow(df))
+    df$stim_code <- rep(s_c, nrow(df))
+    df$synapse <- rep("AMPA", nrow(df))
+    df$freq <- rep(9, nrow(df))
+    df$homeo <- rep("Homeostasis", nrow(df))
+    results307 <- rbind(results307, df)
+  }
+}
+results307 %>%
+  filter(rate_k > 0) -> results307
+
+# ----------------------------------------------------------------------
+# @ 10 Hz
+#
+# No H
+exp_code <- 310
+osc_codes <- c(100, 105, 110, 115)
+osc_rates <- c(0, 0.5, 1.0, 1.5)
+stim_codes <- c(3, 4)
+
+results310 <- NULL
+for(i in 1:length(osc_codes)){
+  for(s_c in stim_codes){
+    o_c <- osc_codes[i]
+    o_r <- osc_rates[i]
+
+    # Load the csv
+    df <- read_csv(paste(data_path, 
+                         "exp", as.character(exp_code), 
+                         "_stim", as.character(s_c), 
+                         "lfp", as.character(o_c),
+                         ".csv", sep=""))
+
+    # Add metadata
+    df$osc_code <- rep(o_c, nrow(df))
+    df$osc_rate <- rep(o_r, nrow(df))
+    df$stim_code <- rep(s_c, nrow(df))
+    df$synapse <- rep("AMPA", nrow(df))
+    df$homeo <- rep("No homeostasis", nrow(df))
+    df$freq <- rep(10, nrow(df))
+    results310 <- rbind(results310, df)
+  }
+}
+results310 %>%
+  filter(rate_k > 0) -> results310
+
+# H
+exp_code <- 311
+osc_codes <- c(100, 105, 110, 115)
+osc_rates <- c(0, 0.5, 1.0, 1.5)
+stim_codes <- c(3, 4)
+
+results311 <- NULL
+for(i in 1:length(osc_codes)){
+  for(s_c in stim_codes){
+    o_c <- osc_codes[i]
+    o_r <- osc_rates[i]
+
+    # Load the csv
+    df <- read_csv(paste(data_path, 
+                         "exp", as.character(exp_code), 
+                         "_stim", as.character(s_c), 
+                         "_lfp", as.character(o_c),
+                         ".csv", sep=""))
+
+    # Add metadata
+    df$osc_code <- rep(o_c, nrow(df))
+    df$osc_rate <- rep(o_r, nrow(df))
+    df$stim_code <- rep(s_c, nrow(df))
+    df$synapse <- rep("AMPA", nrow(df))
+    df$freq <- rep(10, nrow(df))
+    df$homeo <- rep("Homeostasis", nrow(df))
+    results311 <- rbind(results311, df)
+  }
+}
+results311 %>%
+  filter(rate_k > 0) -> results311
+
+# ------------------------------------------------------------------------------------
+# Join results
+results_control_drift <- rbind(
+  results288, 
+  results289, 
+  results298, 
+  results299, 
+  results302, 
+  results303, 
+  results306, 
+  results307, 
+  results310, 
+  results311)
 ```
@@
   mutate(M=mean(rate_k), SD=sd(rate_k)) %>% 
-  ggplot(aes(x=osc_rate, y=M, group=interaction(osc_rate, kind), color=kind)) +
+  ggplot(aes(x=osc_rate, y=M, color=kind)) +
   geom_linerange(mapping=aes(x=osc_rate, ymin=M - SD, ymax=M + SD, color=kind), size=.4) +
-  geom_point() +
+  geom_line(size=0.8) +
+  geom_point(size=1.5) +
   theme_classic() +
@@
   mutate(M=mean(kappa_coord), SD=sd(kappa_coord)) %>% 
-  ggplot(aes(x=osc_rate, y=M, group=interaction(osc_rate, kind), color=kind)) +
-  geom_point() +
+  ggplot(aes(x=osc_rate, y=M, color=kind)) +
+  geom_line(size=0.8) +
+  geom_point(size=1.5) +
   geom_linerange(mapping=aes(x=osc_rate, ymin=M - SD, ymax=M + SD, color=kind), size=.4) +
@@
 # Figure: Control
-```{r, fig.width=2.4, fig.height=2.8}
+```{r, fig.width=5, fig.height=3.6}
 # -
@@
                      label.x=1.3, size=3, show.legend=FALSE) +
-  labs(title="c.", y="Pop. rate", x=TeX("$t_{oscillation} / \\tau_{h}$")) +
+  labs(tag="c.", y="Pop. rate", x=TeX("$t_{oscillation} / \\tau_{h}$")) +
   scale_color_manual(values=c("black", "grey"), name=NA) +
@@
   theme(
-    plot.title = element_text(hjust = -.5, size=18, face="bold"),
+    plot.tag = element_text(size=18, face="bold"),
     legend.background = element_rect(colour ="black"),
@@
 
-# -
+# -----------------------------------------------------------------------------------
+# Freq Theta drift
+results_control_drift %>% 
+  filter(homeo=="Homeostasis") %>% 
+  group_by(osc_rate, freq) %>% 
+  mutate(M=mean(rate_k), SD=sd(rate_k)) %>% 
+  ggplot(aes(x=osc_rate, y=M, color=as.factor(freq))) +
+  geom_linerange(mapping=aes(x=osc_rate, ymin=M - SD, ymax=M + SD, color=as.factor(freq)), size=.4) +
+  geom_line(size=0.8) +
+  geom_point(size=1.5) +
+  theme_classic() +
+  labs(tag="d.", y="Pop. rate", x="Osc. rate") +
+  lims(y=c(0.0, 100.0)) +
+  theme(
+    legend.position = c(1.35, -0.4),
+    legend.key.size = unit(.4, "cm"),
+    legend.background = element_rect(colour ="black"),
+    plot.tag = element_text(size=18, face="bold")) +
+  scale_color_manual(
+    values=c("darkslategray3", "darkslategray4", "black", "darkolivegreen4", "darkolivegreen3"), 
+    name="Freq. (Hz)") -> p10
+
+results_control_drift %>% 
+  filter(homeo=="Homeostasis") %>% 
+  group_by(osc_rate, freq) %>% 
+  mutate(M=mean(kappa_coord), SD=sd(kappa_coord)) %>% 
+  ggplot(aes(x=osc_rate, y=M, color=as.factor(freq))) +
+  geom_linerange(mapping=aes(x=osc_rate, ymin=M - SD, ymax=M + SD, color=as.factor(freq)), size=.4) +
+  geom_line(size=0.8) +
+  geom_point(size=1.5) +
+  theme_classic() +
+  labs(tag="e.", y="Kappa", x="Osc. rate") +
+  lims(y=c(0.0, 0.2)) +
+  theme(legend.position = "none",
+        plot.tag = element_text(size=18, face="bold")) +
+  scale_color_manual(
+    values=c("darkslategray3", "darkslategray4", "black", "darkolivegreen4", "darkolivegreen3"), 
+    name="Freq. (Hz)") -> p11
+
+# -----------------------------------------------------------------------------------
+results_control_leak %>% 
+  filter(homeo=="Homeostasis") %>% 
+  group_by(osc_rate, homeo, g_L) %>% 
+  mutate(M=mean(rate_k), SD=sd(rate_k)) %>% 
+  ggplot(aes(x=osc_rate, y=M, color=g_L)) +
+  geom_linerange(mapping=aes(x=osc_rate, ymin=M - SD, ymax=M + SD, color=g_L), size=.4) +
+  geom_line(size=0.8) +
+  geom_point(size=1.5) +
+  theme_classic() +
+  theme(
+    legend.position = c(1.4, -0.4),
+    legend.key.size = unit(.4, "cm"),
+    legend.background = element_rect(colour ="black"),
+    plot.tag = element_text(size=18, face="bold")) +
+  labs(tag="f.", y="Pop. rate", x="Osc. rate") +
+  scale_color_manual(
+    values=c("darkorange3", "darkorange4", "black", "gold4", "gold3"), 
+    name="g_L (siemens)") -> p14
+
+results_control_leak %>% 
+  filter(homeo=="Homeostasis") %>% 
+  group_by(osc_rate, homeo, g_L) %>% 
+  mutate(M=mean(kappa_coord), SD=sd(kappa_coord)) %>% 
+  ggplot(aes(x=osc_rate, y=M, color=g_L)) +
+  geom_linerange(mapping=aes(x=osc_rate, ymin=M - SD, ymax=M + SD, color=g_L), size=.4) +
+  geom_line(size=0.8) +
+  geom_point(size=1.5) +
+  theme_classic() +
+  theme(legend.position = "none",
+        plot.tag = element_text(size=18, face="bold")) +
+  labs(tag="g.", y="Kappa", x="Osc. rate") +
+  theme(plot.tag = element_text(size=16, face="bold")) + 
+  scale_color_manual(
+    values=c("darkorange3", "darkorange4", "black", "gold4", "gold3"), 
+    name="g_L (siemens)") -> p15
+
+# -----------------------------------------------------------------------------------
 p3 <- textGrob("")
@@
 p9 <- nullGrob()
-
-# -
-# layout_matrix <- rbind(
-#   c(4, 2, 2, 5), 6, 6, 5),
-#   c(4, 2, 2, 5), 6, 6, 5),
-#   c(4, 2, 2, 5), 6, 6, 5),
-#   c(4, 2, 2, 5), 6, 6, 5),
-#   c(3, 1, 1, 5), 7, 7, 5),
-#   c(3, 1, 1, 5), 7, 7, 5),
-#   c(3, 1, 1, 5), 7, 7, 5), 
-#   c(3, 1, 1, 5), 7, 7, 5) 
-# )
+p12 <- textGrob("Theta drift")
+p13 <- textGrob("Conductance\nperturbation")
 
 layout_matrix <- rbind(
-  c(4, 2, 2, 5), 
-  c(4, 2, 2, 5), 
-  c(4, 2, 2, 5), 
-  c(4, 2, 2, 5), 
-  c(3, 1, 1, 5), 
-  c(3, 1, 1, 5), 
-  c(3, 1, 1, 5),  
-  c(3, 1, 1, 9), 
-  c(8, 6, 6, 9),
-  c(8, 6, 6, 9),
-  c(8, 6, 6, 9),
-  c(8, 6, 6, 9)
+  c(4, 2, 2, 5, 12, 10, 10, 9), 
+  c(4, 2, 2, 5, 12, 10, 10, 9), 
+  c(4, 2, 2, 5, 12, 10, 10, 9), 
+  c(4, 2, 2, 5, 12, 10, 10, 9), 
+  c(3, 1, 1, 5, 9,  11, 11, 9), 
+  c(3, 1, 1, 5, 9,  11, 11, 9), 
+  c(3, 1, 1, 5, 9,  11, 11, 9),  
+  c(3, 1, 1, 9, 9,  11, 11, 9), 
+  c(8, 6, 6, 9, 13, 14, 14, 9),
+  c(8, 6, 6, 9, 13, 14, 14, 9),
+  c(8, 6, 6, 9, 13, 14, 14, 9),
+  c(8, 6, 6, 9, 13, 14, 14, 9),
+  c(9, 9, 9, 9, 9,  15, 15, 9),
+  c(9, 9, 9, 9, 9,  15, 15, 9),
+  c(9, 9, 9, 9, 9,  15, 15, 9),
+  c(9, 9, 9, 9, 9,  15, 15, 9)
 )
-grid.arrange(p1, p2, p3, p4, p5, p6, p8, p9, layout_matrix=layout_matrix)
+grid.arrange(p1, p2, p3, p4, p5, p6, p8, p9, p10, p11, p12, p13, p14, p15, layout_matrix=layout_matrix)
 

### 2019-08-21 resistingrhythm/analysis/paper_figures_v4.Rmd
Added lines to Fig 1

@@
   mutate(M=mean(kappa_coord), SD=sd(kappa_coord)) %>% 
-  ggplot(mapping=aes(x=osc_rate, y=M, group=osc_rate, color=synapse)) +
-    geom_point(size=1.25) +
+  ggplot(mapping=aes(x=osc_rate, y=M, color=synapse)) +
+    geom_line(size=0.8) +
+    geom_point(size=1.5) +
     geom_linerange(mapping=aes(x=osc_rate, ymin=M - SD, ymax=M + SD, color=synapse)) +
@@
   mutate(M=mean(kappa_coord), SD=sd(kappa_coord)) %>% 
-  ggplot(mapping=aes(x=osc_rate, y=M, group=osc_rate, color=synapse)) +
-    geom_point(size=1.25) +
+  ggplot(mapping=aes(x=osc_rate, y=M, color=synapse)) +
+    geom_line(size=0.8) +
+    geom_point(size=1.5) +
     geom_linerange(mapping=aes(x=osc_rate, ymin=M - SD, ymax=M + SD, color=synapse),
@@
   mutate(M=mean(rate_k), SD=sd(rate_k)) %>% 
-  ggplot(mapping=aes(x=osc_rate, y=M, group=osc_rate, color=synapse)) +
-  geom_point(size=1.25) +
+  ggplot(mapping=aes(x=osc_rate, y=M,color=synapse)) +
+  geom_line(size=0.8) +
+    geom_point(size=1.5) +
   geom_linerange(mapping=aes(x=osc_rate, ymin=M - SD, ymax=M + SD, color=synapse),
@@
   mutate(M=mean(rate_k), SD=sd(rate_k)) %>% 
-  ggplot(mapping=aes(x=osc_rate, y=M, group=osc_rate, color=synapse)) +
-  geom_point(size=1.25) +
+  ggplot(mapping=aes(x=osc_rate, y=M, color=synapse)) +
+  geom_line(size=0.8) +
+    geom_point(size=1.5) +
   geom_linerange(mapping=aes(x=osc_rate, ymin=M - SD, ymax=M + SD, color=synapse), 
@@
   mutate(M=mean(kappa_coord), SD=sd(kappa_coord)) %>% 
-  ggplot(mapping=aes(x=osc_rate, y=M, group=osc_rate, color=synapse)) +
-    geom_point(size=1.25) +
+  ggplot(mapping=aes(x=osc_rate, y=M, color=synapse)) +
+    geom_line(size=0.8) +
+    geom_point(size=1.5) +
     geom_linerange(mapping=aes(x=osc_rate, ymin=M - SD, ymax=M + SD, color=synapse), 
@@
   mutate(M=mean(rate_k), SD=sd(rate_k)) %>% 
-  ggplot(mapping=aes(x=osc_rate, y=M, group=osc_rate, color=synapse)) +
-    geom_point(size=1.25) +
+  ggplot(mapping=aes(x=osc_rate, y=M, color=synapse)) +
+    geom_line(size=0.8) +
+    geom_point(size=1.5) +
     geom_linerange(mapping=aes(x=osc_rate, ymin=M - SD, ymax=M + SD, color=synapse), 

### 2019-08-21 resistingrhythm/analysis/paper_figures_v4.Rmd
Tweak Fig 2 (gamma)

@@
 # Figure: Gamma (AMPA)
-```{r, fig.height=2.1, fig.width=2.6}
+```{r, fig.height=2.1, fig.width=2.8}
 freq_labels <- as_labeller(c('60' = "60 Hz", '90' = "90 Hz"))
@@
   lims(y=c(0, 100)) +
-  theme(legend.position = "right",
+  theme(legend.position = c(1.17, -0.5),
         plot.tag = element_text(size=16, face="bold"),
@@
 
+pn <- nullGrob()
+
 layout_matrix <- rbind(
-  c(1, 1, 1, 1, 1),
-  c(2, 2, 2, 2, NA)
+  c(1, 1, 1, 1, 3),
+  c(2, 2, 2, 2, 3)
 )
-grid.arrange(p1, p2, layout_matrix=layout_matrix)
+grid.arrange(p1, p2, pn,layout_matrix=layout_matrix)
 ```

### 2019-08-21 resistingrhythm/analysis/paper_figures_v4.Rmd
Tweak control Fig

@@
   theme(
-    legend.position = c(1.4, -0.4),
+    legend.position = c(1.35, -0.4),
     legend.key.size = unit(.4, "cm"),
@@
   c(8, 6, 6, 9, 13, 14, 14, 9),
-  c(9, 9, 9, 9, 9,  15, 15, 9),
-  c(9, 9, 9, 9, 9,  15, 15, 9),
+  c(8, 6, 6, 9, 9,  15, 15, 9),
+  c(8, 6, 6, 9, 9,  15, 15, 9),
   c(9, 9, 9, 9, 9,  15, 15, 9),

### 2019-08-22 resistingrhythm/ipynb/figure_FI.py
Update FI notebook
Add script version (with only generation intact)

@@ -1,0 +1,279 @@
+#!/usr/bin/env python
+# coding: utf-8
+
+# # FI curves
+#
+# Show explicit changes in excitbility with H
+
+# In[8]:
+
+# import matplotlib.pyplot as plt
+# # plt.rcParams.update({'font.size': 50})
+
+# get_ipython().run_line_magic('matplotlib', 'inline')
+
+# import seaborn as sns
+# sns.set(font_scale=3)
+# sns.set_style('ticks', {'axes.edgecolor': '0'})
+
+import numpy as np
+import pandas as pd
+
+from resistingrhythm.util import poisson_impulse
+from resistingrhythm.util import poisson_oscillation
+from resistingrhythm.util import current_pulse
+from resistingrhythm.util import load_spikes
+from resistingrhythm.util import create_times
+from resistingrhythm.neurons import HHH
+
+from fakespikes.rates import square_pulse
+
+# # Simulation
+#
+# Run twice. Once with osc_rate = 0. Once with osc_rate = 1.5
+
+# ## Tune
+
+# # In[ ]:
+
+# # Shared parameters
+# time = 4
+# N = 100
+# tau_h = 1
+
+# V_e = 0
+# tau_e = 5e-3
+# w = (5e-6, 50e-6)
+
+# dt = 1e-5
+
+# # In[ ]:
+
+# # Load some input
+# osc_name = "/Users/qualia/Code/resistingrhythm/data/osc115.csv"
+# stim_name = "/Users/qualia/Code/resistingrhythm/data/stim3.csv"
+
+# # ns_osc, ts_osc = np.asarray([]), np.asarray([])
+# ns_osc, ts_osc = load_spikes(osc_name)
+
+# # -
+# # plt.figure()
+# fig, ax = plt.subplots(1, sharex=True, figsize=(10, 2))
+# _ = ax.plot(ts_osc, ns_osc, markersize=.5, marker='o', linestyle='', color='k')
+# _ = ax.set_xlim(0, 2)
+# sns.despine()
+
+# # In[ ]:
+
+# # Create square wave
+# a = 0.6e-5
+# t_pulse = 3.75
+# w_pulse = .1
+# # t_pulse = 19.5
+# # w_pulse = .1
+
+# times = create_times((0, time), dt=dt)
[…]

### 2019-08-22 resistingrhythm/ipynb/figure_FI.py
Add FNB path

@@ -163,7 +163,8 @@ from fakespikes.rates import square_pulse
 # In[2]:
 
 # Load some input
-osc_name = "/Users/qualia/Code/resistingrhythm/data/osc115.csv"
+# osc_name = "/Users/qualia/Code/resistingrhythm/data/osc115.csv"
+osc_name = "/home/ejp/src/resistingrhythm/data/osc115.csv"
 ns_osc, ts_osc = load_spikes(osc_name)
 
 # In[3]:

### 2019-08-23 resistingrhythm/analysis/paper_figures_v4.Rmd
Add FI figure to Rmd

@@
 
+## FI curve
+```{r, message=FALSE}
+results_fi <- read_csv("../ipynb/FI_curves.csv")
+```
 # Figure: Theta results
@@
 print(wilcox.test(x=tmp3$rate_k, y=tmp4$rate_k))
+```
+# Figure: FI 
+```{r, fig.height=0.9, fig.width=1.9}
+win <- 50e-3
+N <- 100
+us <- 1e6
+results_fi %>% 
+ggplot() +
+  geom_line(aes(x=impulse*us, y=rate_ref/win/N, color="No homeostatis"), size=0.8) +
+  geom_line(aes(x=impulse*us, y=rate_h/win/N, color="Homeostatis"), size=0.8) +
+  labs(tag="a.", y="Avg. rate", x=TeX("Impulse ($\\mu$siemens)")) +
+  lims(x=c(0, 10)) +
+  scale_colour_manual(values=c("black", "grey")) +
+  theme_classic() +
+  theme(
+    legend.title = element_blank(),
+    plot.tag = element_text(size=18, face="bold"),
+    legend.background = element_rect(colour ="black"),
+    legend.key.size = unit(.5, "cm")
+  ) -> p1
+print(p1)
+
+png(file="fig3.png", bg="white", width=3.8, height=1.8, unit="in", res=300)
+print(p1)
+dev.off()
 ```
@@
 grid.arrange(p1, p2, pn,layout_matrix=layout_matrix)
+
+png(file="fig4.png", bg="white", width=5.6, height=4.2, unit="in", res=300)
+grid.arrange(p1, p2, pn,layout_matrix=layout_matrix)
+dev.off()
 ```
@@
 
-png(file="fig4.png", bg="white", width=4.8, height=5.6, unit="in", res=300)
-grid.arrange(p1, p2, p3, p4, p5, p6, p8, p9, layout_matrix=layout_matrix)
+png(file="fig5.png", bg="white", width=10, height=7.2, unit="in", res=300)
+grid.arrange(p1, p2, p3, p4, p5, p6, p8, p9, p10, p11, p12, p13, p14, p15, layout_matrix=layout_matrix)
 dev.off()

### 2020-04-24 resistingrhythm/analysis/paper_figures_v4.Rmd
Renamed 'rate' to 'modulation' in all Figures

@@
     lims(y=c(0.0, 0.2)) +
-    labs(title="b.", y="Kappa", x="Osc. rate") +
+    labs(title="b.", y="Kappa", x="Osc. modulation") +
     theme_classic2() +
@@
     lims(y=c(0.0, 0.2)) +
-    labs(title="d.", y="Kappa", x="Osc. rate") +
+    labs(title="d.", y="Kappa", x="Osc. modulation") +
     theme_classic2() +
@@
   scale_color_manual(values=c("black", "grey")) +
-  labs(title="a.", y="Pop. rate", x="Osc. rate") +
+  labs(title="a.", y="Pop. rate", x="Osc. modulation") +
   lims(y=c(0.0, 180.0)) +
@@
   scale_color_manual(values=c("black", "grey"), name="Tonic") +
-  labs(title="c.", y="Pop. rate", x="Osc. rate") +
+  labs(title="c.", y="Pop. rate", x="Osc. modulation") +
   lims(y=c(0.0, 180.0)) +
@@
     lims(y=c(0.0, 0.2)) +
-    labs(title="f.", y="Kappa", x="Osc. rate") +
+    labs(title="f.", y="Kappa", x="Osc. modulation") +
     theme_classic2() +
@@
     scale_color_manual(values=c("darkgoldenrod3", "goldenrod1"), name="Burst") +
-    labs(title="e.", y="Pop. rate", x="Osc. rate") +
+    labs(title="e.", y="Pop. rate", x="Osc. modulation") +
     lims(y=c(0.0, 180.0)) +
@@
 ```
-# Figure: FI 
-```{r, fig.height=0.9, fig.width=1.9}
-win <- 50e-3
-N <- 100
-us <- 1e6
-results_fi %>% 
-ggplot() +
-  geom_line(aes(x=impulse*us, y=rate_ref/win/N, color="No homeostatis"), size=0.8) +
-  geom_line(aes(x=impulse*us, y=rate_h/win/N, color="Homeostatis"), size=0.8) +
-  labs(tag="a.", y="Avg. rate", x=TeX("Impulse ($\\mu$siemens)")) +
-  lims(x=c(0, 10)) +
-  scale_colour_manual(values=c("black", "grey")) +
-  theme_classic() +
-  theme(
-    legend.title = element_blank(),
-    plot.tag = element_text(size=18, face="bold"),
-    legend.background = element_rect(colour ="black"),
-    legend.key.size = unit(.5, "cm")
-  ) -> p1
-print(p1)
-
-png(file="fig3.png", bg="white", width=3.8, height=1.8, unit="in", res=300)
-print(p1)
-dev.off()
-```
-
 # Figure: Gamma (AMPA)
 ```{r, fig.height=2.1, fig.width=2.8}
-freq_labels <- as_labeller(c('60' = "60 Hz", '90' = "90 Hz"))
+freq_labels <- as_labeller(c('60' = "Gamma, 60 Hz", '90' = "Gamma, 90 Hz"))
 gamma_results %>% 
@@
   scale_color_manual(values=c("darkgoldenrod3", "black"), name="Oscillation") +
-  labs(y="Pop. rate", x="Osc. rate", tag="a.") +
+  labs(y="Pop. rate", x="Osc. modulation", tag="a.") +
   lims(y=c(0, 100)) +
@@
         strip.background = element_blank()) +
-  labs(y="Kappa", x="Osc. rate", tag="b.") -> p2
+  labs(y="Kappa", x="Osc. modulation", tag="b.") -> p2
 
@@
 
-png(file="fig4.png", bg="white", width=5.6, height=4.2, unit="in", res=300)
+png(file="fig3.png", bg="white", width=5.6, height=4.2, unit="in", res=300)
 grid.arrange(p1, p2, pn,layout_matrix=layout_matrix)
+dev.off()
+```
+
+# Figure: FI 
+```{r, fig.height=0.9, fig.width=1.9}
+win <- 50e-3
+N <- 100
+uamp <- 1e6
+results_fi %>% 
+ggplot() +
+  geom_line(aes(x=impulse*uamp, y=rate_ref/win/N, color="No homeostatis"), size=0.8) +
+  geom_line(aes(x=impulse*uamp, y=rate_h/win/N, color="Homeostatis"), size=0.8) +
+  labs(tag="a.", y="Pop. rate", x=TeX("Impulse ($\\mu$amps)")) +
+  lims(x=c(0, 10)) +
+  scale_colour_manual(values=c("black", "grey")) +
+  theme_classic() +
+  theme(
+    legend.title = element_blank(),
+    plot.tag = element_text(size=18, face="bold"),
+    legend.background = element_rect(colour ="black"),
+    legend.key.size = unit(.5, "cm")
+  ) -> p1
+print(p1)
+
+png(file="fig4.png", bg="white", width=3.8, height=1.8, unit="in", res=300)
+print(p1)
 dev.off()
@@
   geom_linerange(aes(ymin=M - SD, ymax=M + SD), alpha=0.5, width=.1, size=0.4)  +
-  labs(title="b.", y="Kappa", x="Osc. rate") +
+  labs(title="b.", y="Kappa", x="Osc. modulation") +
   scale_color_manual(
@@
   geom_linerange(aes(ymin=M - SD, ymax=M + SD), alpha=0.5, width=.1, size=0.4)  +
-  labs(title="a.", y="Pop. rate", x="Osc. rate") +
+  labs(title="a.", y="Pop. rate", x="Osc. modulation") +
   scale_color_manual(
@@
   theme_classic() +
-  labs(tag="d.", y="Pop. rate", x="Osc. rate") +
+  labs(tag="d.", y="Pop. rate", x="Osc. modulation") +
   lims(y=c(0.0, 100.0)) +
@@
   theme_classic() +
-  labs(tag="e.", y="Kappa", x="Osc. rate") +
+  labs(tag="e.", y="Kappa", x="Osc. modulation") +
   lims(y=c(0.0, 0.2)) +
@@
     plot.tag = element_text(size=18, face="bold")) +
-  labs(tag="f.", y="Pop. rate", x="Osc. rate") +
+  labs(tag="f.", y="Pop. rate", x="Osc. modulation") +
   scale_color_manual(
@@
         plot.tag = element_text(size=18, face="bold")) +
-  labs(tag="g.", y="Kappa", x="Osc. rate") +
+  labs(tag="g.", y="Kappa", x="Osc. modulation") +
   theme(plot.tag = element_text(size=16, face="bold")) + 

### 2020-04-24 resistingrhythm/ipynb/figure_FI.py
Update FI script to save SD.
- Also extended equillibration so there is no overlap between I and osc

@@ -167,10 +167,12 @@ from fakespikes.rates import square_pulse
 osc_name = "/home/ejp/src/resistingrhythm/data/osc115.csv"
 ns_osc, ts_osc = load_spikes(osc_name)
 
-# In[3]:
+# Drop anything after 4 seconds
+m = ts_osc > 4
+ns_osc, ts_osc = ns_osc[m], ts_osc[m]
 
 # Shared parameters
-time = 4
+time = 5
 N = 100
 tau_h = 1
 
@@ -181,7 +183,7 @@ w = (5e-6, 50e-6)
 dt = 1e-5
 
 # Impulse desgin
-t_pulse = 3.75
+t_pulse = 4.5
 w_pulse = .1
 a_start = 0.1e-5
 a_stop = 1.0e-5
@@ -243,17 +245,28 @@ for i, a in enumerate(a_range):
         time_step=dt,
         seed_value=42)
 
-    # Extract rates, and save
-    r_1 = (results_1['ts'] > 3.5).sum()
-    r_2 = (results_2['ts'] > 3.5).sum()
+    # Extract rates and SD, and save
+    r_1 = (results_1['ts'] > 4.5).mean()
+    r_2 = (results_2['ts'] > 4.5).mean()
+    s_1 = (results_1['ts'] > 4.5).std()
+    s_2 = (results_2['ts'] > 4.5).std()
     rates_1.append(r_1)
     rates_2.append(r_2)
-
+    vars_1.append(s_1)
+    vars_2.append(s_2)
+    
+    # Progress bar....
     print(f"Rate 1 (no): {r_1}. Rate 2 (yes): {r_2}")
 
 # In[16]:
 
-fi = {'rate_ref': rates_1, 'rate_h': rates_2, 'impulse': a_range}
+fi = {
+    'rate_ref': rates_1, 
+    'rate_h': rates_2, 
+    'var_ref' : vars_1,
+    'var_h' : vars_2,
+    'impulse': a_range}
+
 # to npy
 np.save('FI_curves', fi)
 # to csv

### 2020-04-24 resistingrhythm/ipynb/figure_FI.py
Add stitch path

@@ -164,7 +164,9 @@ from fakespikes.rates import square_pulse
 
 # Load some input
 # osc_name = "/Users/qualia/Code/resistingrhythm/data/osc115.csv"
-osc_name = "/home/ejp/src/resistingrhythm/data/osc115.csv"
+# osc_name = "/home/ejp/src/resistingrhythm/data/osc115.csv"
+osc_name = "/home/stitch/Code/resistingrhythm/data/osc115.csv"
+
 ns_osc, ts_osc = load_spikes(osc_name)
 
 # Drop anything after 4 seconds
@@ -254,18 +256,19 @@ for i, a in enumerate(a_range):
     rates_2.append(r_2)
     vars_1.append(s_1)
     vars_2.append(s_2)
-    
+
     # Progress bar....
     print(f"Rate 1 (no): {r_1}. Rate 2 (yes): {r_2}")
 
 # In[16]:
 
 fi = {
-    'rate_ref': rates_1, 
-    'rate_h': rates_2, 
-    'var_ref' : vars_1,
-    'var_h' : vars_2,
-    'impulse': a_range}
+    'rate_ref': rates_1,
+    'rate_h': rates_2,
+    'var_ref': vars_1,
+    'var_h': vars_2,
+    'impulse': a_range
+}
 
 # to npy
 np.save('FI_curves', fi)
